\chapter{Sentence}

\stc[6.3]{
    The reason why some people addict to something is they use such 
    things to indulge himself and escape from reality.}{
    一些人沉迷于某些事物的原因是他们需要麻痹自己并且逃离现实世界.
    }

\stc[6]{
    They music sound a little sorrow, and the most important thing is 
    I should refrain to masturbate henceforth, but which doesn't mean I can't
    masturbate anymore, which mean I should keep a positive attitude in the remain time
    of the very important exam. Furthermore, I also give myself a good sleep that 
    not only mean the quantity, quality is essential.
}{ommited}

\stc[8]{
    At the time of high school, I can constantly submerge in mathematic world, at that time, my
    brain full up with mathematic, and forget all of annoyance. It's maybe my best time of learning.
    But now I face another challenge that make me very anxious, the most critial thing is I can't let 
    me peace, my brain always full up with something that make me very pain, I worry about the future
    of me. It's a vicious circle, the exam make me anxious because I can't focus into learning and the reason
    is I inevitably need an more convincing degree to find satisfying jobs, and time willn't wait me. 
}{ommited}

\stc[5]{
    In the history, China had invaded a lot of nationality.
    But the offical department and history book always said that isn't an invasion it just
    a domestic war. Well, history always writed by the victor. Whatever, all of the government
    and the offical always make people believe their culture is righteous, and the foes always
    are very vicious, at the end the righteous beat the evil, how a legendary story.
    But I think, at least in that people who hold power and rule people nobody is
    righteous, and no one didn't do something for himself, because human prefer to
    be a selfish animal.
}{}

\stc[5]{
    Sometimes you must endure something that really test your endurance.
}{}

\stc[5]{
    A lot of people who live in china have strong resentment to government, because
    daily life become harder and the PRC always propagandize with time gone the life
    of chinese become better, by contrast people in abroad life become more and more
    hard. It's ridiculous to believe such propaganda, but few people whose brain maybe
    undergo a strong attack by his mother due to his stupid is truely ridiculous.
}{}