\chapter{Vocabulary}

% seperator for pronunciation
\def\sepe{\ifmmode\cdot\else$\cdot$\fi}
\def\twocol#1#2{\hbox{\vbox{#1}\hskip-.65\hsize\relax\vbox{#2}}}
%%%% amazing vscode vim plugin... I don't know when I press "vjkjj...u".
%%% tipa
\let\ca\textscripta%
\let\cd=D%
\let\ce=E%
\let\ci=I%
\let\cn=N%
\let\co=O%
\let\cs=S%
\let\ct=T%
\let\cu=U%
\let\cz=Z%
\let\rse\textrhookschwa%

\let\exx\example
% <vim-code>1,$s/^\([A-z]*\) &/\\index{\1}&/g</vim-code> to index all word
\begin{engvc}[18-8-16]
axis & "\ae ks\ci s& noun. & 轴线;轴\crr
romantic & ro\cu "m\ae nt\ci k& adj. & 浪漫的\crr
\linetab{
    \relative
    \tphrase{romantic poetry}{}
    \tphrase{\ci t's a romantic scheme}{}
    \tphrase{romantic atmosphere}{}
}
supermarket & "sup\textrhookschwa mark@t& noun. & 超市\crr
pronounce& pr@"na\cu nGs& verb. & 发音; 宣告\crr
sympathise & "simp@""\ct a\ci z& verb.& 同情;同感\crr
\linetab{
    \relative
    \tword{sympathetic}{"simp@""\ct \ce t\ci k}{同情的;共鸣的;赞同的;和谐的;合意的}
    \tword{sympathizer}{"simp@\ct a\ci z\textrhookschwa}{同情者;同感者;支持者}
}
extra & "ekstr@&adj.\newline adv.\newline noun.&额外的\newline 额外地\newline 额外的事物\crr
syndrome & "sindro\cu m& noun.&综合征;综合症状;典型表现\crr
decrease & d\ci "kris& verb.\newline noun. & 减少; 降低\newline 减少\crr
away & @"we& adv. & 离开; 远离; 在远处\crr
\linetab{
    \relative
    \tphrase{run away}{跑开}
    \tphrase{far away}{遥远的}
    \tphrase{right away}{立刻}
    \tphrase{far away from}{远离;离...远}
    \tphrase{go away}{走开}
    \tphrase{straight away}{马上; 即刻}
    \tphrase{do away with}{废除; 去掉; 弄死}
    \tphrase{far and away}{无疑地; 显然地}
    \tphrase{away from it all}{远离喧嚣}
    \tphrase{out and away}{大大地; 远远地}
}
variable & "v\ce ri@bl& adj.\newline noun.& 可变的; 易变的; 不稳定的\newline 变量; 易变的东西\crr
\linetab{
    \relative
    \tword{vary}{"veri}{变化; 不同的}
    \tword{variety}{v@"rai@ti}{变化; 多样性; 种种; 品种; 种类}
    \tword{various}{"veri@s"}{各种各样地; 不同的; 各种的;}
    \tword{variation}{""v\ce r\ci "e\cs n}{变化; 变动}
    \tword{invariable}{\ci n"veri@bl}{永无变化地; 始终如一的}
}
barber &"barb\textrhookschwa & noun. &理发师 \crr
hesitate & "h\ce s@tat & verb. & 犹豫; 踌躇\crr
\linetab{
    \example
        \eng \cd on't hesitate at this moment. \chn 在这一瞬间不要犹豫. \newline
        \eng \ci  hesitate before diving into the icy water. \chn 我在跳入冷水的时候犹豫了.\newline 
        \eng \ci  hesitate to get involved in this adventure. }
beer & bi\textrhookschwa&noun. & 啤酒\crr
voluntary & v\ca l@nt@ri & adj. & 自发的; 自愿的\crr
    \linetab{ 
        \relative 
        \tword{volunteer}{""v\ca l@n"t\ci \textrhookschwa}{志愿者(noun.); 自愿做(verb.)} 
}
bulb & b2lb& noun. & 电灯泡; 球茎\crr 
mortal & "m\co rtl& adj.\newline noun. & 致命的; 终有一死的; 极度的\newline 凡人; 普通人\crr 
\linetab{
     \relative \word{moral}{"m\co r@l}{道德的} \word{immortal}{\ci "m\co rtl}{不朽的; 永恒的} 
}
save & sev& verb.\newline prep. \newline conj. & 保存; 拯救; 节省\newline 除...之外; 除了\newline 若不是; 除了\crr 
\linetab{
     \example
     \eng \ci  am wall save that \ci  have a cold. \chn 除了患感冒之外, 我很精神. \newline
     \eng He would have gone, save that he had no means. \chn 要不是没有办法, 他早就走了.\newline 
     \eng Yet only one of his books is now in print, and his vast body of writings music is unknown save to speciallists \chn 他的著作只有一本仍在印行, 他的大量关于音乐的作品 除了专业人士之外, 无人知晓. 
     \relative \phrase{save to }{除了} \phrase{save ... from}{使...免遭} 
     }
comrade& "k\ca mr\ae d& noun. & 同志; 伙伴\crr
materialistic &m@""t\ci ri@"l\ci st\ci k& adj. & 唯物论的; 物质至上主义的\crr
mysterious & m\ci 'st\ci ri@s& adj. & 神秘的\crr
ginger & "d\cz \ci nd\cz \textrhookschwa& noun. & 生姜\crr
pepper & "p\ce p\textrhookschwa & noun.\newline verb. & 胡椒粉\newline 使布满; 向...不断射击\crr
onion & "2nj@n& noun. & 洋葱\crr
shallot & s@"l\ca t&noun.& 青葱； 大葱； 红葱头\crr
leek & lik & noun. & 葱\crr
carrot & "k\ae r@t & noun. & 胡萝卜\crr
skillful & "sk\ci lf@l& adj. & 有技巧的; 熟练的; 灵巧的\crr
\linetab{
    \relative
    \tword{expert}{"eksp\textrhookschwa t}{专家; 老练的; 内行的; 当专家}
    \tword{proficient}{pr@f\ci \cs @nt}{熟练的; 精通的; 专家; 能手; 老手}
    \tword{skilled}{sk\ci ld}{熟练的; 有技能的}
}
grass & gr\ae s&noun.\newline verb. & 草; 草地; 大麻; 告密者\newline 使吃草; 放牧; 告发\crr
\linetab{
    \relative
    \tword{glass}{gl\ae s}{玻璃}
    \tword{gross}{gro\cu s}{总共的; 粗野的}
    \tword{grasp}{gr\ae sp}{抓住; 领会; 理解}
}
brigth & brait& adj. & 明亮的; 鲜艳的; 聪明的\crr
\linetab{
    \remark
    \ct he difference between bright , clever, wise, brilliant\newline
    bright: 口头常用语, 多指年轻人, 尤指小孩思路敏捷, 理解能力强\newline
    clever: 强调头脑灵活, 接受新事物快, 有智有谋, 但不一定暗示全面妥当地考虑问题;\newline
    wise: 侧重不是一般地聪明伶俐, 而是有远见, 有智慧地处理问题\newline
    brilliant: 指人地才华出众, 思路敏捷, 常令人赞叹不已
}
distinguish & d\ci "st\ci \cn gwi\cs & verb. & 区别; 区分\crr
\linetab{
    \defn
    verb. recognize or treat (someone or something) as different
    \example
    \eng \ct he child is perfectly capable of distinguishing reality from fantasy
}
discriminate & d\ci "scr\ci m@n\ce t& verb. & 歧视; 区别; 区分\crr
\linetab{
    \defn
    1. recognize a distinction, differentiate\newline
    2. make an unjust or prejudicial in treatment of different categories of people or
    things, especially on the ground, race, sex or age.
}
difference & "d\ci f@r@ns& noun. &差异; 不同\crr
\linetab{
    \defn
    noun. a point or way in which people or thing are not the same.
}
disparity &d\ci "sp\ae r@ti& noun.& 差距; 差别; 异样\crr
\linetab{
    \defn
    \ca  huge difference.
    \example
    economics is disparity between different regions of the country.
}
capable &"kep@b@l&adj.&有能力的\crr
\linetab{
    \relative
    \vbox{\begin{description}
        \item{able} 褒义词, 着重指多方面地, 经常性地, 或潜在地能力
        \item{capable} 语气弱于 able, 常与 of 连用
        \item{competent} 强调具有胜任某项工作的足够技能或者其他所需要的条件
    \end{description}
    }
}
type &taip&noun.\newline verb. & 类型; 种类; 典型; 字体\newline 打字; 定型; 成为...的典型\crr
\linetab{
    \relative
    \tword{category}{"k\ae t\textrhookschwa g\co ri}{类别\quad 书面用语, 特指有确切定义的群体}
    \tword{classification}{""kl\ae s@f\ci "ke\cs @n}{分类; 分级\quad 根据已经确定的类型对某一实物作鉴别和分类}
    \tword{class}{kl\ae s}{类\quad 正式用语, 指门类,种类或优劣等级}
    \tword{sort}{s\co rt}{类别; 种类}
    \tword{species}{"spi\cs iz}{种类; 物种\quad 生物上的种类}
    \tword{variety}{v@"rai@ti}{品种;种类\quad 强调各自的特点, 形式不同, 品质不同的种}
}
hurt&h\textrhookschwa t&verb.\newline noun.&受伤; 感到疼痛\newline 伤痛\crr
\linetab{
    \relative
    \tword{wound}{wund}{专指对身体的重伤, 尤指在战斗中受的伤}
    \tword{harm}{h\ca rm}{主要用于有生命的东西, 语气略强}
    \tword{injure}{"\ci nd\cz \textrhookschwa}{引起严重的伤痛和损伤}
    \tword{damage}{"d\ae m\ci d\cz }{对无生命的损害}
}
liberty & "lib\textrhookschwa ti&noun.&自由\crr
\linetab{
    \relative
    \tword{liberal}{"l\ci b@r@l}{自由主义的; 自由主义者}
    \tword{liberate}{"l\ci b@""ret}{解放; 释放}
    \tphrase{\ct he \cs tatue of Liberty}{自由女神像}
}
aggravate&"\ae gr@vet&verb.&加剧; 使恶化; 激怒\crr
\linetab{
\example
\eng aggravate the ethical situation in the trade.\chn 恶化了行业的道德状况\newline
\eng \ct hreats will only aggravate her.\chn 恐吓自能激怒他\newline
\eng \cs tress can aggravate the situation.\chn 压力会使情况恶化
}
intensify&\ci n"t\ce ns@""fai&verb.&加强; 强化\crr
orchard&"\co rt\cs \textrhookschwa d&noun.&果园\crr
\end{engvc}

\bigskip

\begin{engvc}[18-8-17]
borrow & "b\ca ro\cu &verb.&借来;借\crr
\linetab{
    \remark
    \eng borrow sth from sb. \chn 从某人那借来某物\newline
    \eng lend sth to sb. / lend sb sth. \chn 把某物借给某人\newline
}
strategic & str@"tid\cz \ci k& adj.&战略上的\crr
\linetab{
    \relative
    \tword{strategy}{"str\ae t@d\cz i}{战略; 策略; 战略学}
    \tword{strategist}{"str\ae t@d\cz \ci st}{战略家}
    \tword{strategical}{str@"tid\cz \ci kl}{张略的}
    \tword{strategically}{str@"tid\cz ikl\ci }{张略上; 战略性地}
}
temperory & "temp@reri& adj.&临时的；短暂的\crr
\linetab{
    \relative
    \tword{contemporary}{k@n"t\ce mp@r\ce ri}{同代人； 现代的； 当代的}
    \tword{temperate}{"temp@r@t}{温和的; 克制的; 有节制的}
    \tword{temperature}{"temp@r@""t\cs \textrhookschwa}{温度; 气温; 体温}
}
population &""p\ca pjule\cs n& noun.&人口\crr
\linetab{
    \relative
    \tword{populate}{"p\ca pjulet}{居住于; 生活于; 移民于}
    \tword{popular}{"p\ca pjel\textrhookschwa}{流行的; 大众的; 受欢迎的}
    \tword{populated}{"p\ca pj\cu let\ci d}{有人居住的; 人口密集的; populate的过去式和过去分词}
    \tword{popularity}{""p\ca pju"l\ae r@ti}{普及; 流行}
}
compliment & "k\ca mpl\ci m@nt& verb. \newline noun. & 称赞; 恭维\newline 称赞; 恭维\crr
complement & "k\ca mpl@ment& verb. \newline noun. & 补足; 补充; 与...相辅相成\newline  补足物; 补语; 余角\crr
sew & so & verb. & 缝制; 缝补\crr
\linetab{
    \example
    \eng    Chains do not hold a marriage together, it is threads, hundreds of tiny threads, which
    sew people together through the years.
}
stool & stul & noun. & 凳子; 大便\crr
wheat & wit& noun.&小麦; 小麦色\crr
dragon & "dr\ae g@n& noun. & 龙; 母夜叉\crr
\linetab{
    \relative
    \tword{frog}{frOg}{青蛙}
    \tword{dragonfly}{"dr\ae g@n""flai}{蜻蜓}
    \tword{tortoise}{"t\co rt@s}{乌龟}
    \tword{phoenix}{"fin\ci ks}{凤凰}
    \tword{tiger}{"taig\textrhookschwa}{老虎}
    \tword{kylin}{kail\ci n}{麒麟}
    \tword{dinosaur}{"dain@s\co r}{恐龙}
}
asymptote& \ae s@mto\cu t& noun. & 渐进\crr
\linetab{
    \defn
    \ca  line that continually approaches a given curve but does not meet it at any finite 
    distance.
}
\end{engvc}

\medskip
\begin{engvc}[18-8-24]
contentious & k@n"t\ce n\cs @s& adj. & 有争议的\crr
\linetab{
    \relative
    \tword{contend}{k@n"t\ce nd}{争斗; 声称}
}
controversial & ""k\ca ntr@"v\textrhookrevepsilon \cs @l& adj. & 有争议的\crr
talkative & "t\co k@tiv& adj. & 贫嘴的; 健谈的\crr
distinctive & d\ci "st\ci \cn kt\ci v & adj. & 独特的; 特别的; 与众不同的\crr
\linetab{
    \exx\eng when Miles Davis died, Jazz was robbed of its most distinctive voice.
}
forehaead & ""f\co rh\ce d& noun. & 前额\crr
\linetab{
    \relative
    \tword{foretime}{"f\co rtai}{以往; 过去}
    \tword{forecast}{"f\co rk\ae st}{预测}
    \tword{forground}{"f\co rgra\cu nd}{前景; 最显著的位置}
    \tword{foreword}{"f\co rw\textrhookschwa d}{序言; 前言}
    \tword{forefather}{"f\co rf\ca \cd \textrhookschwa}{前人; 祖先}
    \tword{foretell}{f\co r"tel}{预言; 预示}
    \tword{forerunner}{"f\co r""r2n\textrhookschwa}{先行者; 先驱; 前兆}
    \tword{foresee}{f\co r"si}{预见; 预知}
    \tword{forearm}{f\co r\ca rm}{前臂}
}
inherit & \ci n"her\ci t& verb.& 继承\crr
\linetab{
    \defn{
        \begin{minipage}{.8\hsize}
        \baselineskip=.4\baselineskip
        \smallskip
        \begin{itemize}
\item        obtain from someone after their death.
\item        receive from a predecessor.
\item        receive by genetic transmission.
        \end{itemize}
        \smallskip
    \end{minipage}
    }
    \relative
    \tword{inheritance}{\ci n"h\ce r\ci t@ns}{继承}
    \tword{heritage}{"h\ce r\ci t\ci d\cz }{遗产}
    \tword{heritable}{"h\ce r\ci t@b@l}{可遗传的}
}
down & da\cu n&adv. & 向下\crr
\linetab{
    \relative
    \tphrase{be down to}{由...负责}
    \tphrase{be down with}{患病}
}
capture & "k\ae pt\cs \textrhookschwa & verb.\newline noun. & 捕获; 占领; 夺取; 吸引; 拍摄\newline 捕获; 战利品\crr
\linetab{
    \relative
    \tword{captive}{"k\ae pt\ci v}{俘虏}
    \tword{caption}{"k\ae p\cs @n}{解释说明}
    \tword{captain}{"k\ae pt@n}{首长; 部长}
    \tword{capital}{"k\ae p\ci tl}{首都; 大写字母}
}
outsider & a\cu t"sa\ci d\textrhookschwa & noun. & 局外人; 圈外人; 无取胜希望者\crr
\linetab{
    \relative
    \tword{foreigner}{"f\co r@n\textrhookschwa}{外国人; 外来人}
    \tword{stranger}{"strend\cz \textrhookschwa}{陌生人}
}
communicate & k@"mjun\ci "ket& verb. & 交流; 沟通\crr
\linetab{
    \relative
    \tword{communist}{"k\ca mj@n\ci st}{共产主义的; 共产主义者}
    \tword{community}{k@"mjun\ci t\ci }{社区; 团体; 群落}
    \tword{communism}{"k\ca mjun\ci z@m}{共产主义}
}
yesterday & "jest\textrhookschwa de& verb. \newline adv. & 昨天\crr
\linetab{
    \relative
    \tword{tomorrow}{t@"m\ca ro\cu }{明天}
    \tphrase{the day after yesterday}{前天}
    \tphrase{the day after tomorrow}{后天}
}
Monday & "m2nde& noun. & 星期一\crr
\ct uesday & "tuzde& noun. & 星期二\crr
Wednesday & "w\ce nzde& noun. & 星期三\crr
\ct hursday & "\ct \textrhookschwa zde& noun. &星期四\crr
Friday & "frai""de& noun. &星期五\crr
\cs aturday & "\ae t\textrhookschwa de& noun. & 星期六\crr
\cs unday & "s2n""de&noun. &星期日\crr
January & "d\cz \ae nju@ri& noun. & 一月\crr
February & "f\ce bju\ce ri& noun. & 二月\crr
March & m\ca rt\cs & noun. & 三月\crr
\ca pril & "epr@l& noun. & 四月\crr
May & me& noun. & 五月\crr
June & d\cz un& noun. & 六月\crr
July & d\cz \cu "lai& noun. & 七月\crr
\ca ugust & \co "g2st& noun. & 八月\crr
\cs eptember & s\ce p"t\ce mb\textrhookschwa& noun. & 九月\crr
\co ctober & \ca k"to\cu b\textrhookschwa& noun. & 十月\crr
\cn ovember & no\cu "vemb\textrhookschwa& noun. & 十一月\crr
\cd ecember & d\ci "s\ce mb\textrhookschwa& noun. & 十二月\crr
inference &"\ci nf@r@ns& noun. & 推断; 推论\crr
\linetab{
    \relative
    \tword{infer}{"\ci nf\textrhookschwa}{推断; 推论(verb.)}
    \tword{refer}{r\ci "f\textrhookrevepsilon}{应用; 提到; 参考}
    \tword{reference}{"r\ce f@r@ns}{提及; 涉及; 应用}
}
often & "\co fn& adv. &常常地\crr
\linetab{
    \relative
    \tword{always}{"\co lwez}{总是; 一直}
    \tword{usually}{"ju:\cz uli}{通常}
    \tword{frequently}{"friw@ntli}{时常; 经常}
    \tword{repeatedly}{r\ci "pit\ci dli}{重复地}
    \tword{regularly}{"regj@l\textrhookschwa li}{有规律地; 定期地}
}
vacant & "vek@nt& adj. &空缺的\crr
hollow & "h\ca lo\cu &adj. & 中空地; 空洞的\crr
meanwhile & "min""hwa\ci l& adv. &与此同时; 其间\crr
\linetab{
    \relative
    \tphrase{at the same time}{同时}
    \tword{likewise}{"la\ci k""waiz}{同样地; 照样地}
}
cautious &"k\co \cs @s& adj. & 小心的; 谨慎的\crr
\linetab{
    \relative
    \dword{careful:} 侧重做事谨慎, 留心, 特别注意一些细节.\newline
    \dword{cautious:} 侧重考虑事情的后果.\newline
    \dword{attentive:} 认真地注意地倾听别人地意见.\newline
    \dword{prudent:} 谨慎思考 计划周密, 不贸然行事.\newline
}
poverty &"p\ca v\textrhookschwa ti& noun. &贫穷; 短缺\crr
secret & "sikr@t& noun. \newline adj.& 秘密 \newline 秘密的\crr
secretary & "s\ce kr@t\ce ri& noun. & 秘书; 书记; 大臣\crr
secretion & s\ci "kri\cs en& noun. &分泌物\crr
secrete & s\ci "krit& verb. &分泌\crr
secure & s@"kj\cu r& adj. & 安全的; 可靠的; 稳定的\crr
obvious & "\ca bv\ci @s& adj. &明显的; 显然的\crr
apparent & @"p\ae r@nt& adj. & 表面上的; 明显的\crr    
evident & "\ce v\ci d@nt& adj. & 明显的\crr
\linetab{
    \relative
    \tword{distinct}{d\ci "sti\cn kt}{明显的; 表示定义或含义的准确, 不会弄错}
    \texx{There's a lot of evidence that oily fish, as distinct from fatty meat has a benefit effect.}
    \tword{definite}{"d\ce f\ci n\ci t}{肯定的; 语气比较重}
    \tword{manifest}{"m\ae n@""f\ce st}{明显的; 语气强, 书面用语, 表示不需要任何推论就一清二楚.}
}
diplomatic & ""d\ci pl@"m\ae t\ci k & adj. & 外交的\crr
addict & @"d\ci kt & noun.\newline verb. & 瘾君子; 入迷的人\newline 使沉迷; 使上瘾\crr
\linetab{
    \relative
    \tphrase{addict oneselft to sth.}{使某人对...上瘾}
    \tword{addictive}{@"d\ci kt\ci v}{使人上瘾的}
    \tword{addiction}{@"d\ci k\cs @n}{成瘾; 沉溺; 嗜好}
    \example
    \eng \ct he man began to addict himself to all sort of vice.
    \chn 这个人开始沉迷于各式各样的陋习.
}
indulge & \ci n"d2ld\cz  & verb. & 放任; 沉迷; 听任\crr
\linetab{
    \example
    \eng \cd on't indulge youself too much.
    \chn 不要过于放纵自己.\newline
    \eng \ct o indulge one's curiosity.
    \chn 满足好奇心.
}
season & "siz@n & noun.\newline verb. & 季节\newline 给...调味; 适应; 风干 \crr
\linetab{{
    \relative
    \tword{spring}{spri\cn }{春天; 泉; 跳跃}
    \tword{summer}{"s2m\textrhookschwa}{夏天; 夏季}
    \tword{autumn}{"\co t@m}{秋天; 秋季}
    \tword{winter}{"w\ci nt@}{冬天}
}}
innate & \ci "net & adj. & 天生的; 生来的\crr
\linetab{
    \relative
    \tword{intrinsic}{\ci n"tr\ci ns\ci k}{固有的; 内在的; 本身的}
    \tword{inherent}{\ci n"h\ci r@nt}{固有的; 内在的; 本身的}
    \tword{inborn}{\ci n"b\co rn}{天生的; 先天的}
    \tword{instinctive}{\ci n"st\ci \cn kt\ci v}{本能的}
}
\end{engvc}

\medskip
\begin{engvc}
drama & "dr\ca m@ & noun. & 戏剧; 话剧\crr
extraordinarily & \ci k"str\co rdn""\ce r\ci li & adj. & 不平凡的\crr
worthwhile & ""w\textrhookrevepsilon \ct "wa\ci l & adj. & 值得做的\crr
institution & ""\ci nst\ci "tj\cu s@n & noun. & 制定; 制度; 机构; 风俗; 习惯\crr
\linetab{
    \example
    \eng Giving presents on Christmas is an institution.
    \chn 在圣诞节送礼物是一种风俗.\newline
    \relative
    \tword{institute}{"\ci nst\ci tut}{学院}
    \tword{constitute}{"k\ca nst@tut}{构成}
    \tword{constitution}{""k\ca nst@"tu\cs n}{宪法}
}
substitute & "s2bst\ci tj\cu t & verb. & 代替\crr
\linetab{
    \relative
    \tword{substitution}{""s2bst\ci "tu\cs @n}{替换(noun.)}
}
hormone & "h\co rmo\cu n & noun. & 荷尔蒙; 激素\crr
\linetab{
    \example
    \eng \cs tudies of both animals and humans have shown that sex hormone somehow 
    affect the stress response.
    \chn 对动物和人类的研究表明, 性激素可能会影响对压力的反应.
}
somehow & "s2m""ha\cu  & adv. & 不知何故; 以某种方式\crr
inhale & \ci n"hel & verb. & 吸入\crr
exhale & \ce ks"hel & verb. & 呼出; 散发\crr
spray & spre & noun.\newline verb. & 喷雾\newline 喷洒\crr
toddlers & "t\ca dl\textrhookschwa & noun. & 学步的儿童\crr
delight & d\ci "la\ci t & noun.\newline verb. & 高兴; 快乐\newline 使高兴\crr
\linetab{
    \exx\eng \cs he clapped her hands in delight.\newline
    \eng \cs he won the game easily, to the delight of all her fans.\newline
    \eng Your visit yesterday delight us.
}
counterpart & "ka\cu nt\textrhookschwa p\ca rt & noun. & 职务相当的人; 对应物; 副本\crr
mock & m\ca k & verb.\newline adj. \newline noun. & 嘲笑; 嘲弄\newline 仿制的; 虚假的\newline 模拟考试; 嘲弄\crr
technology & t\ce k"n\ca l@d\cz i & noun. & 科技; 技术\crr
\linetab{
    \relative
    \tword{technique}{t\ce k"nik}{技术; 工艺; 技巧; 技艺}
    \tword{technician}{t\ce k"n\ci \cs @n}{技术员; 技师}
    \tword{technical}{"t\ce  kn\ci k@l}{技术上的}
}
outlive & a\cu t"l\ci v & verb. & 比...活得长; 度过...而存在; 经受住\crr
\linetab{
    \example
    \eng Millions of families worry about the harsh reality that they may outlive 
    their retirement money.
    \chn 数百万家庭担心的残酷的现实: 退休金用完了人没死.
    \relative
    \tword{outweigh}{a\cu t"we}{大于; 重于; 超过}
    \tword{outrun}{a\cu t"r2n}{跑得比...快}
    \tword{outsize}{"a\cu t""saiz}{更大}
    \tword{outrange}{"a\cu t""red\cz }{愤怒; 发怒}
    \tword{outgrow}{""a\cu t"gro\cu }{长得高}
}
rail & rel & noun.\newline verb. & 铁轨; 横木\newline 咒骂; 责备; 抱怨; 以横木围栏\crr
\linetab{
    \relative
    \tword{railway}{"rel""we}{铁路}
    \tword{subway}{"s2b""we}{地铁; 地下通道}
    \tword{underground}{"2nd\textrhookschwa gra\cu nd}{地下; 地铁; 地下的; 秘密的; 秘密地}
}
pubic & "pjub\ci k & adj. & 阴部地\crr
serise & "s\ci ris & noun. & 系列\crr
quadruple & kw\ca "drupl & adj.\newline noun.\newline adj. & 四倍\crr
\linetab{
    \relative
    \tword{double}{"d\ca b@l}{两倍(noun. verb. adj.)}
    \tword{twofold}{"tufo\cu ld}{两倍(adv. adj.)}
    \tword{triple}{"tr\ci pel}{三倍}
    \tword{quadruple}{kw\ca "drupl}{四倍}
    \tword{quintuple}{kw\ci n"t\ca p@l}{五倍}
    \tword{sextuple}{"sektup@l}{六倍}
}
diverse & da\ci "v\textrhookschwa s & adj. & 不同的; 相异的\crr
righteous & "ra\ci t\cs @s & adj. & 公正的; 正义的\crr
turnaround & "t\textrhookschwa n\textrhookschwa a\cu nd & verb. & 转向; 好装; 周转\crr
\linetab{
    \relative
    \tword{turnover}{"t\textrhookschwa no\cu v\textrhookschwa}{营业额; 流动; 成交量}
    \tword{overturn}{""o\cu v\textrhookschwa "t\textrhookschwa n}{推翻; 倾覆(verb. noun.)}
    \tword{upturn}{"\ca pt\textrhookschwa n}{好转; 转机}
}
intuition & ""\ci ntu"\ci \cs n & noun. & 直觉\crr
\linetab{
    \relative
    \tword{intuitive}{In"tjuItIv}{直觉的}
    \tword{intuit}{In"tuIt}{有直觉知道}
}
tuition & tu"\ci \cs n & noun. & 学费; 指导\crr
instinct & "\ci n""st\ci \cn kt & noun. & 本能; 直觉\crr
confuse & k@n"fjuz & verb. & 迷惑; 混淆\crr
\linetab{
    \relative
    \tword{refuse}{r\ci "fjuz}{拒绝(verb.); 废料; 垃圾(noun.)}
    \tword{infuse}{\ci n"fjuz}{注入; 灌输}
    \tword{diffuse}{d\ci "fjuz}{弥漫; 散射; 弥漫的; 散射的}
    \tword{transfuse}{tr\ae ns"fjuz}{输血; 灌输}
}
hostile & "h\ca stl & adj. & 敌对的; 敌意的\crr
intrigue & "\ci n""trig & noun.\newline verb. & 阴谋诡计; 密谋策划\newline 密谋; 激起...的兴趣\crr
stomach & "st2m@k & noun.\newline verb. & 胃部; 腹部\newline 忍受; 吃得下\crr
\linetab{
\relative
    \tword{brain}{bren}{大脑}
    \tword{heart}{h\ca rt}{心脏}
    \tword{lung}{l2\cn }{肺}
    \tword{liver}{"l\ci v\textrhookschwa}{肝}
    \tword{stomach}{"st2m@k}{胃}
    \tword{kidney}{"k\ci dni}{肾}
    \tword{tooth}{tu\ct }{牙齿}
    \tword{spleen}{splin}{脾脏; 脾气}
    \tword{pancreas}{"p\ae \cn kri@s}{胰腺}
    \tword{buttock}{"b2t@k}{臀部}
    \tword{waist}{west}{腰}
    \tword{wrist}{r\ci st}{手腕}
    \tword{ankle}{"\ae \cn k@l}{踝关节}
    \tword{knee}{ni}{膝盖}
    \tword{skeleton}{"sk\ce l\ci tn}{骨架; 骷髅; 纲要; 骨干的}
    \tword{artery}{"\ca rt@ri}{动脉}
    \tword{vein}{ven}{静脉}
}
ordinarily & ""\co rdn""er@li & adv. & 按说; 通常地\crr
characteristic & "k\ae r@kt@"r\ci st\ci k & adj.\newline noun. & 典型的; 特有的\newline 特点; 特性\crr
\linetab{
    \example
    \eng We ordinary charaterize an action as responsible if it was intended.\newline
\relative
    \tword{characterize}{"k\ae r@kt@""ra\ci z}{表现特色; 刻画性格}
    \tword{characteristically}{"k\ae r@kt@"r\ci st\ci kli}{典型地; 表示特征地}
    \tword{characterization}{""k\ae r@kt\textrhookschwa ra\ci "ze\cs n}{特性描述}
}
pay & pe & verb. & 支付; 付出代价\crr
\linetab{
    \relative
    \tphrase{pay for}{付款; 偿还; 为...付款}
    \tphrase{pay back}{偿还; 报复}
    \tphrase{pay up}{全部付清}
    \tphrase{pay attention to}{注意}
    \tphrase{pay a visit}{访问}
}
product & "pr\ca d2kt & noun. & 产品; 产物; 成果; 数积\crr
\linetab{
    \relative
    \tword{produce}{pr@"dus}{生产; 生育; 引起; 导致}
    \tword{production}{pr@"d2k\cs @n}{生产; 产量}
    \tword{productive}{pr@"d2kt\ci v}{生产的; 多产的; 富有成效的}
    \tword{productivity}{""pr\ca d2k"t\ci v@ti}{生产力; 生产率}
    \tword{invention}{\ci n"v\ce n\cs @n}{发明}
    \tword{reproduce}{""ripr@"dus}{繁殖; 复制}
}
mechanic & m\ci "k\ae n\ci k & noun. & 技工; 机械师\crr
curtain & "k\textrhookschwa tn & noun. & 帷幕; 窗帘\crr
draw & dr\co  & verb. & 拉; 拽; 画; 提取; 吸引\crr
\linetab{
    \relative
    \tphrase{draw up}{起草}
    \tphrase{draw out}{拔出}
    \tphrase{draw from}{源于...}
}
deliver & d\ci "l\ci v\textrhookschwa & verb. & 交付; 递送; 为...接生; 发表; 陈述; 予以\crr
\linetab{
    \example
    \eng For a small city-status, \cs ingapore certainly delivers far more technician
    you might expect with its outstanding learning institution.
    \chn 作为一个小型城市国家, 新加坡拥有的优秀院校超乎想象.
    \relative
    \tword{delivery}{d\ci "l\ci v@ri}{分娩; 交付; 传送(noun.)}
    }
permanent & "p\textrhookschwa m@n@nt & adj. & 永久的; 持久的\crr
diameter & dai"\ae m\ci t\textrhookschwa & noun. & 直径\crr
\linetab{
    \relative
    \tword{radius}{"redi@s}{半径}
    \tword{circumference}{s@r"k2mf@r@ns}{周长}
    \tword{bulk}{b2lk}{体积}
    \tword{density}{"d\ce ns\ci t\ci }{密度}
}
patent & "p\ae tnt & noun.\newline adj. \newline verb. & 专利\crr
average & "\ae vr\ci d\cz  & adj.\newline noun.\newline verb. & 平均的; 平常的\newline 平均数; 平均; 平均水平\newline 计算...的平均值; 平均分配\crr
defendant & d\ci "f\ce nd@nt & noun.\newline adj. & 被告人; 被诉方\newline 被告的; 辩护的\crr
\linetab{
    \relative
    \tword{defend}{d\ci "f\ce nd}{防御; 防卫; 保卫}
    \tword{accuser}{@"kjuz\textrhookschwa}{原告}
    \tword{plaintiff}{"plent\ci f}{原告; 起诉人}
}
grammar & "gr\ae m\textrhookschwa & noun. & 语法\crr
financially & fa\ci "n\ae n\cs @li & adv. & 经济上; 金钱上; 财政方面\crr
finance & "fa\ci n\ae ns & noun.\newline verb. & 金融; 财务\newline 提供资金\crr
flour & fla\cu \textrhookschwa & noun. & 面粉\crr
want & w\ca nt & verb.\newline noun. & 想要\newline 缺乏\crr
\end{engvc}

\medskip
\begin{engvc}
protest & "pro\cu test & verb. & 抗议； 辩驳\newline 抗议；坚决的表示； 申辩\crr
\linetab{
    \exx\eng This has resulted in protests from social scientists.
}
envelop & \ci n"v\ce l@p & verb. & 包围; 包封; 遮盖\crr
\linetab{
    \example
    \eng Gloom and sadness envelop the household.
    \relative
    \tword{envelope}{"env@lo\cu p}{信封}
}
exhibition & ""\ce ks@"b\ci \cs @n & noun. & 展览; 展出\crr
duration & du"re\cs n & noun. & 持续时间; 期间\crr
checkout & "t\cs \ce k""a\cu t & noun. & 检验; 付款处; 结账\crr
\linetab{
    \example
    \eng \ct he idea must undergo the checkout of experiment.\newline
    \relative
    \tphrase{in support of}{支持}
    \tphrase{in favor of}{支持; 赞成}
    \tphrase{with regard to}{关于; 至于}
    \tphrase{in respect of}{就...而言}
    \tphrase{on behalf of}{代表}
    \tphrase{to the benefit of}{为了...的利益}
}
behalf & b\ci "h\ae f & noun. & 代表; 利益; 支持\crr
\linetab{
    \example
    \eng \ci  signed the document on your behalf.
    \chn 我代表你签了那份文件.
    \relative
    \tword{behave}{b\ci "hev}{代表; 举止}
}
substance & "s2bst@ns & noun. & 物质; 物品; 实质; 主旨; 要点\crr
\linetab{
    \example
    \eng \ct he substance of his discussions doesn't really matter(verb.).
    \chn 他讨论地要点根本不重要.
}
latest & "let\ci st & noun.\newline adj. & 最新消息; 最新事物\newline 最新地; 最近地; 最后的\crr
stalemate & "stel""met & noun.\newline verb. & 僵局; 和棋; 僵持状态\newline 使陷入僵局\crr
\linetab{
\tword{stale}{stel}{不新鲜的}
\tword{standoff}{"st\ae nd""\co f}{僵局; 和局}
\tword{impasse}{"\ci mp\ae s}{绝境; 僵局; 死路}
}
negotiation & n\ci ""go\cu \cs i"e\cs n & noun. & 协商; 谈判\crr
nogotiate & n\ci "go\cu \cs iet & verb. & 谈判; 协商\crr
\linetab{
    \relative
    \tword{negotiable}{n\ci "go\cu \cs i@bl}{可协商的}
    \tword{negotiater}{n\ci "go\cu \cs iet\textrhookschwa}{谈判者; 协商者}
}
delicate & "d\ce l\ci k\ci t & adj. & 易损的; 娇嫩的; 纤细的; 微妙的\crr
\linetab{
    \tword{dedicate}{"d\ce d\ci ket}{奉献; 献身; 致力}
    \tword{deliberate}{d\ci "l\ci b@r\ci t}{深思熟虑; 仔细考虑; 深思熟虑的; 故意的}
}
dismiss & d\ci s"m\ci s & verb. & 解雇; 解散; 不理会; 驳回\crr
\linetab{
    \relative
    \tword{eliminate}{\ci "l\ci m\ci net}{消除; 淘汰}
    \texx{Every time you answer a question you eliminate a possibility.}
    \texx{\chn 例行的去掉某人或某物}
    \tword{expel}{\ci ks"p\ce l}{驱逐; 开除; 排出}
    \texx{\chn 强行解除公职或驱出住地}
    \tword{discharge}{d\ci s"t\cs \ca rd\cz }{放出; 排出; 开除(verb. noun.)}
    \texx{\chn 有理由的解雇, 不再雇用}
}
inform & \ci n"f\co rm & verb. & 通知; 告知\crr
\linetab{
    \relative
    \tphrase{inform sb. of sth.}{告知某人某事}
    \tphrase{inform on sb.}{检举某人}
    \tphrase{be informed by}{弥漫着}
}
situation & ""s\ci t\cs u"e\cs @n & noun. & 情况; 形式; 情境\crr
\linetab{
    \relative
    \tword{circumstance}{"s\textrhookrevepsilon k@mst\ae ns}{环境; 情况}
    \texx{\chn 指周围的情况或者某事发生时的情况}
    \tword{condition}{k@n"d\ci \cs @n}{状态; 条件; 环境; 保养; 护理}
    \texx{\chn 强调产生影响的原因或环境}
    \tword{status}{"st\ae t@s}{地位; 身份; 状况; 状态}
    \texx{\chn 指一个人在社会,政治,经济,法律上的地位, 暗含地位显要}
}
employ & \ci m"pl\co i & verb. & 雇佣; 使用\crr
\linetab{
    \relative
    \tword{employee}{\ci mpl\co \ci "i}{雇员}
    \tword{employer}{\ci m"pl\co \ci \textrhookschwa}{雇主}
    \tword{employment}{\ce m"pl\co \ci m@nt}{就业; 雇佣; 职业(noun.)}
    \tword{unemployment}{""2n\ce m"pl\co im@nt}{失业(noun.)}
}
illustrate & "\ci l@""stret & noun. & 说明; 做插图\crr
\linetab{
    \relative
    \tword{illustrative}{\ci "l2str@ t\ci v}{说明的; 解说的; 作例证的}
    \tword{illustration}{""\ci "l@stre \cs @n}{说明; 插图; 例证; 图解}
    \tword{illustator}{"\ci l@stre t\textrhookschwa}{插图作家}
}
survey & "s\textrhookrevepsilon ve & noun.\newline verb. & 调查; 勘测\crr
\linetab{
    \relative
    \tword{survive}{s\textrhookschwa va\ci v}{幸存; 生存}
    \tword{convey}{k@n"ve}{运输}
}
record & "r\ce k\textrhookschwa d & noun.\newline verb. & 记录; 唱片\newline 记录; 录制\crr
preparation & ""pr\ce p@"re\cs @n & noun. & 准备\crr
\linetab{
    \example
    \eng \ci  have two more books in preparation.\newline
    \eng He didn't do any preparation for this exam, so he failed.
}
preliminary & pr\ci "l\ci m\ci neri & adj. & 预备的; 初步的\crr
layout & "le""a\cu t & noun. & 布局; 布置\crr
acknowledge & @k"n\ca l\ci d\cz  & verb. & 承认; 表明已收到; 答谢\crr
economical & ""\ce k@"n\ca m\ci kl & adj. & 节俭的; 经济的\crr
\linetab{
    \example
    \eng We bought a cheap car for economical reason.\newline
    \relative
    \tword{economy}{\ci "k\ca n@mi}{经济; 节约}
    \tword{economic}{""\ce k@"n\ca m\ci k}{经济的}
}
infinite & "\ci nf\ci n@t & adj. & 无穷的; 无限的\crr
\linetab{
    \relative
    \tword{finite}{"fa\ci ""na\ci t}{有限的}
}
legacy & "l\ce g@si & noun. & 遗产; 遗赠\crr
certify & "s\textrhookschwa t\ci fa\ci  & verb. & 保证; 证明; 证实\crr
take & tek & verb. & 拿; 取; 乘坐; 吃; 接受\crr
\linetab{
    \index{phrase of take}
    \relative
    \tphrase{take care of}{照顾}
    \tphrase{take part}{参与; 参加}
    \tphrase{take on}{承担; 呈现; 具有; 流行; 接纳; 雇佣; 穿上}
    \tphrase{take up}{拿起; 开始从事}
    \tphrase{take charge of}{接管; 负责}
    \tphrase{take off}{起飞; 脱下; 离开}
    \tphrase{take apart}{打败; 拆开}
    \tphrase{take out}{取出; 去掉; 出发}
    \tphrase{take into}{考虑到; 说服}
    \tphrase{take in}{接受; 理解; 拘留; 欺骗; 让...进入; 改短}
    \tphrase{take over}{接管; 接受}
    \tphrase{take away}{拿走; 带走; 取走; 夺走}
}
imagination & \ci ""m\ae d\cz @"ne\cs @n & noun. &想象; 想象力\crr
prejudice & "pr\ce d\cz @d\ci s & noun.\newline verb. & 偏见; 成见\newline 使有偏见; 损害\crr
bug & b2g & noun.\newline verb. & 小虫子; 窃听器; 漏洞\newline 装窃听器; 使烦恼\crr
\linetab{
    \relative
    \tword{rug}{r2g}{地毯}
    \tword{drug}{dr2g}{药}
    \tword{hug}{h2g}{拥抱}
    \tword{tug}{t2g}{猛拉}
    \tword{plug}{pl2g}{插头}
    \tword{bacteria}{b\ae k"t\ci r\ci @}{细菌}
    \tword{virus}{"va\ci r@s}{病毒}
    \tword{leak}{lik}{渗漏; 泄露(verb.) 漏洞; 泄露(noun.)}
}
line & la\ci n & noun.\newline verb. & 线; 界线; 绳\newline 排队; 画线\crr
\linetab{
    \relative
    \tword{hardline}{""h\ca rd"la\ci n}{强硬的}
    \tword{underline}{""2nd\textrhookschwa "la\ci n}{强调; 在...下面画线}
    \tword{decline}{d\ci "kla\ci n}{下降; 衰退; 谢绝(verb. noun.)}
    \tword{offline}{"\ca fla\ci n}{离线的; 离线地}
    \tword{deadline}{"d\ce d""la\ci n}{最终期限}
    \tword{incline}{\ci n"kla\ci n}{倾斜; 倾向; 斜坡}
    \tword{inclination}{""\ci nk@l@""ne\cs @n}{倾斜; 倾向; 意向}
    \tword{baseline}{"besla\ci n}{基线; 底线; 基准}
    \tword{outline}{"a\cu t""la\ci n}{轮廓; 纲要; 描画轮廓}
    \tword{pipeline}{"pa\ci p""la\ci n}{管线; 管道}
    \tword{lineage}{"l\ci ni\ci d\cz }{血统; 世系}
    \tphrase{in line with}{与...一致}
    \tphrase{line up}{排成一排; 组织; 安排}
}
verbal & "v\textrhookschwa bl & adj. & 口头的; 语言的; 用词地; 动词地\crr
\linetab{
    \relative
    \tword{verbalize}{"v\textrhookschwa b@la\ci z}{用语言表达}
    \tword{verbalization}{"v\textrhookschwa b@la\ci ze \cs @n}{用语言表现; 冗长}
    \tword{verbalism}{"v\textrhookschwa b@liz@m}{咬文嚼字; 语言表达}
    \tword{verbify}{"v\textrhookschwa b\ci fa\ci }{使动词化}
}
accurate & "\ae kj\cu r@t & adj. & 精确的; 无误地\crr
\linetab{
    \example
    \eng an accurate description
}
inquire & \ci n"kwa\ci \textrhookschwa & verb. & 询问; 调查\crr
\linetab{
    \relative
    \tword{require}{r\ci "kwa\ci \textrhookschwa}{需要; 要求}
    \tword{acquire}{@"kwa\ci \textrhookschwa}{获得; 得到; 学会}
    \tword{acquisition}{""\ae kwI"zIS@n}{获得; 得到的东西; 收购}
    \tword{acquaintance}{@"kwent@ns}{相识; 熟悉的人; 知识; 心得}
}
contribution & ""k\ca ntr\ci "bju\cs n & noun. & 贡献; 捐助物; 投稿; 稿件\crr
\linetab{
    \relative
    \tword{contribute}{k@n"tr\ci bjut}{捐献; 投稿; 贡献; 促成}
    \tword{contributing}{k@n"tr\ci bjuti\cn }{贡献的; 起作用的(adj.) 捐献; 投稿(现在分词)}
    \tword{distribute}{d\ci "str\ci bjut}{分发; 分配; 散步; 配给}
    \tword{attribute}{@"tr\ci bjut}{由...引起; 把...归因于; 认为是...创作的(verb.) 属性; 品质; 特性; 定语}
    \tphrase{pay tribute to}{赞美; 认同}
}
redundancy & r\ci "d2nd@nsi & noun. & 冗余; 裁员; 多余\crr
\linetab{
    \relative
    \tword{abundant}{@"b2nd@nt}{富裕的; 充足的}
    \tword{redundant}{r\ci "d2nd@nt}{多余的; 富余的}
    \tword{surplus}{"s\textrhookschwa pl@s}{过剩(noun.); 过剩的; 多余的}
    \tword{superfluous}{su"p\textrhookschwa flu@s}{多余的; 过剩的}
    \tword{remnant}{"r\ce mn@nt}{剩余的}
}
attention & @"t\ce n\cs @n & noun. & 注意; 关注\crr
\linetab{
    \relative
    \tword{attend}{@"t\ce nd}{出席; 上学; 照顾; 处理}
    \tword{attendance}{@"t\ce nd@ns}{出席; 出席人数}
    \tword{attendant}{@"t\ce nd@nt}{服务员}
    \tword{attentive}{@"t\ce nt\ci v}{专心的; 留心的; 注意的}
    \tword{attentively}{@"t\ce nt\ci vli}{专心地; 注意地}
}
valid & "v\ae l\ci d & adj. & 有效的; 正当地; 有根据地\crr
simulation & ""s\ci mj@"le\cs & noun. & 模拟; 仿真\crr
\linetab{
    \relative
    \tword{assimilate}{@"s\ci m@""let}{吸收; 消化; 使同化}
    \tword{emulate}{"\ce mje""let}{竞争; 努力赶上; 仿真; 模拟}
    \tword{accumulate}{@"kjumjulet}{积累}
    \tword{stimulate}{"st\ci mjulet}{刺激; 激励}
    \tword{imitate}{"\ci m\ci tet}{模仿; 效仿}
    \tword{intimate}{"\ci nt@m\ci t}{\vbox{暗示; 提示; 宣布(verb.) 亲密地; 熟悉地; 私人地; 性关系地(adj.) 密友(noun.)}}
    \tword{intimidate}{In"tImI""det}{胁迫; 威胁; 恐吓}
    \tword{timid}{"tImId}{胆小的}
}
scandal & "sk\ae ndl & noun. & 丑闻; 丑行\crr
skim & sk\ci m & verb. & 略读; 掠过\crr
gloomy & "glumi & adj. & 忧郁的; 沮丧的; 黑暗的\crr
melancholy & "mel@nk\ca li & 忧愁; 忧郁的\crr
definite & "d\ce f\ci n\ci t & adj. & 肯定的; 确定的\crr
\linetab{
    \relative
    \tword{define}{d\ci "fa\ci n}{下定义}
    \tword{defined}{d\ci "fa\ci nd}{有定义的; 确定的; 清晰的}
    \tword{definitive}{d\ci "f\ci n\ci t\ci v}{决定性的; 最后的; 限定的(adj.) 限定词(noun.)}
    \tword{defining}{d\ci "fa\ci ni\cn }{最典型的; 起决定作用的}
    \tword{definable}{d\ci "fa\ci n@bl}{可定义的; 可确定的; 可限定的}
    \tword{definitely}{"d\ce f\ci n@t@li}{清楚地; 当然; 明确地; 肯定地}
    \tword{definition}{""d\ce f@"n\ci \cs @n}{定义; 清晰度; 解说}
    \tword{definiteness}{""d\ce "f@n\ci tn\ci s}{确定性; 明确; 特性}
}
critical & "kr\ci t\ci k@l & adj. & 批判的; 临界的; 危机的; 关键的; 至关重要的\crr
\linetab{
    \relative
    \tword{critic}{"kr\ci t\ci k}{批评家}
    \tword{criticism}{"kr\ci t\ci ""s\ci z@m}{批评(noun.)}
    \tword{criticise}{"kr\ci t\ci ""sa\ci z}{批评(verb.)}
}
operator & "\ca p@ret\textrhookschwa & noun. & 接线员; 操作员\crr
aware & @"wer & adj. & 意识到的; 知道的\crr
\linetab{
    \defn
    Have knowledge or perception of a situation or fact.
    \example
    \eng He pretended not to be aware of my presence.\newline
    \eng Were you aware that something was wrong.
}
thumb & \ct 2m & noun.\newline verb. & 大拇指\newline 以拇指拨弄\crr
\linetab{
    \relative
    \tword{dumb}{d2m}{哑巴的; 无发言权的}
    \tword{bump}{b2mp}{碰撞; 冲突(noun. verb.)}
    \tword{lumb}{l2mp}{小块(noun.) 结成块(verb.)}
    \tphrase{index finger / fore finger}{食指}
    \tphrase{middle finger}{中指}
    \tphrase{ring finger / third finger}{无名指}
    \tphrase{little finger}{小指}
}
terminal & "t3rm\ci nl & adj.\newline noun. & 终端的; 晚期的\newline 终端; 终点站; 航空站\crr
project & pr\ca d\cz ekt & noun.\newline verb. & 项目; 计划; 工程; 课题\newline 计划; 投影; 射出; 凸出\crr
\linetab{
    \example
    \eng to project a corporate image to the outside world.
    \chn 对外突出企业形象.
}
doctrine & "d\ca ktr\ci n & noun. & 教条; 教义; 学说\crr
concrete & "k\ca \cn krit & adj.\newline noun.\newline verb. & 有形的; 混凝土的\newline 混凝土; 具体物\newline 用混凝土覆盖\crr
\linetab{
    \example
    \eng \cs ome instead suggest there are concrete measures that can be taken to ensure more finish strongly 
    enough to go onto college.
    \chn 然而, 有专家建议可采取具体措施来确保更多的来自劣势群体的孩子完成学业.
}
discrete & d\ci "skrit & adj. & 离散的; 个别的; 不相关的\crr
college & "k\ca l\ci d\cz  & noun. & 学院; 大学\crr
colleague & "k\ca lig & noun. & 同事\crr
unfocused & 2n"fok@st & adj. & 不集中的; 漫不经心的\crr
\linetab{
    \example
    \eng \ca  study show a lack of sleep can easily make a child cranky, irritable or unfocused.
}
fiction & "f\ci k\cs @n & noun. & 小说; 虚构\crr
elementary & ""\ce l@"m\ce nt@ri & adj. & 基本的; 初级的\crr
skirt & sk3rt & noun.\newline verb. & 裙子; 下摆; 边缘\newline 位于...边缘; 避开\crr
peer & p\ci \rse & verb.\newline noun. & 凝视; 盯着看; 与...对等\newline 同等的人; 同辈; 贵族\crr
\linetab{
    \relative
    \tphrase{gaze at}{凝视; 注视(惊讶地)}
    \tphrase{stare at}{盯着看(无礼地)}
    \tphrase{glare at}{怒视}
    \tphrase{peer at}{盯着}
}
subsequent & "s2bs\ci kw@nt & adj. & 随后的; 后来的\crr
infrastructure & "\ci nfr@str2kt\cs \rse & noun. & 基础设施\crr
temperature & "t\ce mp@r@""t\cs \rse & noun. & 温度; 气温; 体温\crr
tendency & "t\ce nd@nsi & noun. & 趋势; 倾向\crr
\linetab{
    \example
    \eng \ct he findings do not simply explain peoples tendency to be friend those of similar
    ethnic backgrounds.
}
simply & "s\ci mpli & adv. & 简单地; 仅仅; 简直\crr
ethnic & "\ce \ct n\ci k & adj. & 人种的; 种族的\crr
make & mek & verb. & 做; 制作; 使得\crr
\linetab{
    \relative
    \tphrase{make sure}{确信; 证实}
    \tphrase{make up}{弥补; 组成; 化妆; 整理}
    \tphrase{make full use of}{充分利用}
    \tphrase{make friends with}{与...交友}
    \tphrase{make a difference}{有影响; 有关系}
    \tphrase{make out}{理解}
    \tphrase{make a decision}{作决定}
    \tphrase{make for}{导致; 有助于; 走向}
    \tphrase{make of}{了解; 用...制造}
    \tphrase{make in}{加入; 进入; 干涉别人}
    \tphrase{make a living}{谋生}
}
foul & fa\cu l & adj.\newline verb.\newline noun. & 很坏的; 肮脏恶臭的; 很令人不快的\newline 使污秽; 对...犯规; 纠缠难解\newline 犯规\crr
necessary & "n\ce s@s\ce ri & adj. & 必需的; 必要的; 必然的\crr
\linetab{
    \relative
    \tword{indispensable}{""\ci nd\ci "sp\ce ns@b@l}{不可缺少的(语气强)}
    \tword{essential}{\ci "s\ce n\cs @l}{必需的; 基本的; 本质的; 提炼的; 精华的(暗含不可缺少, 否则无法存在)}
    \tword{requisite}{"r\ce kw\ci z\ci t}{必需的; 必备的; 必需品(强调不可避免, 但并非绝不可以缺少)}
}
\end{engvc}

\medskip
\begin{engvc}[18-8-27]
parallel & "p\ae r@""l\ce l & adj.\newline verb.\newline noun. & 平行的; 相似的; 相同的\newline 平行; 类似\newline 类似的事物; 相似之处\crr
\linetab{
    \example
    \eng Your experience are parallel with mine.\newline
    \eng \ct here are upsetting parallel today.\newline
    \eng \ca  big concrete gutter that parallel the road.
}
combine & k@m"ba\ci n & verb. & 组合; 结合\crr
\linetab{
    \example
    \eng combine theory with practice\newline
    \eng combine all the ingredient in a bowl.
}
ingredient & \ci n"grid\ci @nt & noun. & 配料\crr
\end{engvc}

\medskip
\begin{engvc}[18-8-28]
satisfiction & ""s\ae t\ci s"f\ae k\cs @n & noun. & 满意； 满足\crr
\linetab{
    \relative
    \tword{satisfy}{""s\ae t\ci s""fa\ci }{满足； 使满足}
    \tword{satisfactory}{""s\ae t\ci s"f\ae kt@ri}{满意的; 满足的}
    \tword{satisfied}{"s\ae t\ci s""fa\ci d}{满意的; 满足的(形容感觉)}
    \tword{satisfying}{"s\ae t\ci sfa\ci \ci \cn }{令人满意的}
}
gossip & "g\ca s\ci p & verb.\newline noun. & 散播\newline 流言蜚语\crr
\linetab{
    \relative
    \tphrase{hot gossip}{热门八卦}
}
ignorant & "\ci gn@r@nt & adj. & 无知的; 缺乏知识的\crr
\linetab{
    \relative
    \tword{ignorance}{"Ign@r@ns}{无知; 愚昧; 不知; 不懂}
    \tword{ignoramus}{""Ign@"rem@s}{无知的人; 笨蛋}
}
formidable & "f\co rm\ci d@b@l & adj. & 令人敬畏的; 可怕的\crr
reveal & r\ci "vil & verb. & 显露; 泄露; 透露\crr
\linetab{
    \exx\eng \cd etails of the murder were revealed by the local paper.\newline
    \eng \cs he crouched in dark, too frighten to reveal herself.\chn\word{crouch}{kra\cu t\cs }{卷缩; 伏缩(verb.) 顿看的姿势(noun.)}
}
infancy & "\ci nf@nsi & noun. & 婴儿期; 幼年; 初期\crr
cineme & "s\ci n@m@ & noun. & 电影\crr
subsidy & "s2bs\ci di & noun. & 补贴\crr
\linetab{
\relative
\tword{allowance}{@"la\cu @ns}{津贴}
\tword{bonus}{"bon@s}{奖金}
\tword{tuition}{tu"\ci \cs @n}{学费}
\tword{scholarship}{"sk\ca l\rse \cs ip}{奖学金}
\tword{toll}{to\cu l}{过路费}
\tword{fare}{f\ce \rse}{车票费}
\tword{revenue}{"rev@nu}{税收}
\tword{welfare}{"w@lfe@r}{福利}
\tword{pension}{"p\ce n\cs @n}{养老金}
}
tunnel & "t2n@l & noun.\newline verb. & 隧道; 地道\newline 开凿隧道\crr
channel & "t\cs \ae n@l & noun.\newline iverb. & 河床; 海峡; 渠道; 频道\newline 引导; 开导; 形成河道\crr
considerate & k@n"s\ci d@r\ci t & adj. & 考虑周到的; 体贴的\crr
\linetab{
    \tword{considerable}{k@n"s\ci d@r@b@l}{重要的; 可观的; 相当大的}
    \tword{consider}{k@n"sId\rse}{考虑; 仔细考虑; 认为; 以为}
    \tword{considering}{k@n"sId@rIN}{鉴于; 考虑到; 就...而言(preposition.)}
}
scarce & skers & adj. & 缺乏的; 不足的; 稀有的\crr
everlasting & ""ev\rse "l\ae sti\cn  & adj. & 永久的; 永恒的; 经久不变的\crr
\linetab{
    \relative
    \tword{perpetual}{p\rse "pet\cs u@l}{持续的; 长久的}
    \texx{My life has been a perpetual nightmare.}
    \tword{perpetuate}{p\rse"petSuet}{使永存; 使不朽}
    \tword{perpetuity}{""p3rp@"tu@ti}{永恒; 永远(noun.)}
    \tword{eternal}{\ci "t\rse nl}{不朽的; 永久的}
    \tword{eternity}{\ci "t\rse n@ti}{永恒; 永生; 不朽}
    \tword{permanent}{"p\rse m@n@nt}{永久的; 持久的}
}
embodiment & \ci m"b\ca dim@nt & noun. & 体现; 具体化; 化身\crr
orbiter & "\co rb\ci t\rse & noun. &航天飞行器\crr
orbit & "OrbIt & noun.\newline verb. & 轨道; 轨迹\newline 绕...轨道而行\crr
petition & p@"t\ci \cs @n & noun.\newline verb. & 请愿书; 祈求\newline 请愿; 祈求\crr
entreat & \ci n"trit & verb. & 恳求; 祈求\crr
plead & plid & verb. & 请求; 辩护\crr
archaeological & ""\ca k\ci r"l\ca d\cz \ci kl & adj. &考古学的\crr
\linetab{
    \relative
    \tword{ecology}{i"k\ca l@d\cz i}{生态学; 生态}
    \tword{biology}{ba\ci "\ca l@d\cz i}{生物学}
    \tword{microbiology}{""ma\ci kro\cu ba\ci "\ca l@d\cz i}{微生物学}
    \tword{psycology}{sa\ci "k\ca l@d\cz i}{心理学}
    \tword{geology}{d\cz i\ca l@d\cz i}{地质学}
    \tword{geography}{d\cz \ci "\ca gr@fi}{地理学}
    \tword{astronomy}{@"str\ca n@mi}{天文学}
    \tword{physics}{"f\ci z\ci ks}{物理学}
    \tword{chemistry}{"k\ce mistr\ci }{化学}
    \tword{history}{"h\ci stri}{历史}
    \tword{politics}{"p\ca l@t\ci ks}{政治}
    \tword{oceanography}{""o\cu \cs @"n\ca gr@fi}{海洋学}
    \tword{archaeology}{""\ca ki"\ca l@d\cz i}{考古学}
    \tword{architecture}{"\ca rk\ci tekt\cs @}{建筑学}
    \tword{philosophy}{f@"l\ca s@fi}{哲学}
    \tword{anthropology}{""\ae n\ct r@"p\ca l@d\cz i}{人类学}
    \tword{statistics}{st@"t\ci st\ci ks}{统计学}
}
inexpressible & ""\ci n\ci ks"pr\ce s@b@l & adj. & 难以表达的; 无法形容的\crr
thoroughly & "\ct \textrhookrevepsilon r@li & adv. & 彻底地; 完全地\crr
thorough & "\ct\rse r@U & adv. & 彻底的; 完全的\crr
contest & "k\ca ntest & noun.\newline verb. & 比赛; 竞赛\newline 竞争; 争夺; 争辩; 辩驳\crr
\linetab{
    \relative
    \tword{concert}{"k\ca ns@t}{音乐会}
    \tword{content}{"k\ca t\ce nt}{内容}
    \tword{context}{"k\ca ntekst}{上下文; 环境}
}
preside & pr\ci "za\ci d & verb. & 主持; 指挥; 担任会议主席\crr
gorgeous & "g\co rd\cz @s & adj. & 华丽的; 绚丽的; 极好的\crr
striking & "stra\ci ki\cn  & adj. & 引人注目的; 显著的\crr
cement & s@"m\ce nt & noun.\newline verb. & 水泥; 胶合剂\newline 用水泥涂; 粘牢\crr
reliable & r\ci "la\ci @b@l & adj. &  可靠的; 可信的\crr
\linetab{
    \relative
    \tword{reliance}{r\ci "la\ci @ns}{信赖; 依赖}
    \tword{reliant}{r\ci "la\ci @nt}{信赖的; 依赖的}
    \tword{reliability}{r\ci ""la\ci @"b\ci l@ti}{可靠性}
}
poem & "po\cu @m & noun. & 诗; 诗篇\crr
\linetab{
    \relative
    \tword{poetry}{"po\cu @tr\ci }{诗集; 诗歌}
    \tword{poet}{"po\cu @t}{诗人}
    \tword{poetic}{po\cu "et\ci k}{诗歌的}
}
slack & sl\ae k & adj.\newline noun.\newline verb. & 松弛的; 懈怠的; 萧条的\newline 松弛的部分; 松散; 淡季\newline 使松懈; 懈怠\crr
\linetab{
    \example
    \eng \ct he economic slack. \chn 经济萧条\newline
    \eng \ca s usual, \cs ingapore \ca irlines will reduce trans-pacific capacity in slack seasons.\newline
    \eng to slack one's duty.
}
mining & "ma\ci ni\cn  & noun. & 采矿; 采矿业\crr
dependency & d\ci "pend@nsi & noun. & 依赖; 附属国; 附属地\crr
constrict & k@n"str\ci kt & verb. & 紧缩; 束紧; 使紧缩\crr
\linetab{
    \relative
    \tword{district}{"d\ci str\ci kt}{地区; 区域}
    \tword{distract}{d\ci "str\ae kt}{使分心; 使混乱}
    \tword{destruct}{d\ci "str2kt}{破坏}
}
accommodate & @"k\ca nm@det & verb. & 容纳; 为...提供住宿; 适应\crr
complaint & k@mplent & noun. & 抱怨; 投诉\crr
\linetab{
\relative
\tword{complain}{k@m"plen}{抱怨(verb.)}
\tword{compliance}{k@m"pla\ci @ns}{遵守; 服从; 顺从}
}
column & "k\ca l@m & noun. & 圆柱; 专栏; 纵; 列\crr
columnist & "k\ca l@mn\ci st & noun. & 专栏作家\crr
bond & b\ca nd & verb.\newline noun. & 使结合; 使粘合\newline 结合; 债券\crr
\linetab{
    \example
    \eng \ct he bond market \chn 证券市场\newline
    \eng enter into a bond with sb.\newline
    \eng \ct hese two materials won't bond together\newline
    \relative
    \tword{bind}{ba\ci nd}{捆绑; 约束(verb.) 困境; 结合处(noun.)}
    \tword{bound}{ba\cu nd}{限制; 弹跳}
}
opportunity & ""\ca p\rse "tun@ti & noun. & 机会; 时机\crr
\linetab{
    \relative
    \tword{occasion}{@"ke\cz @n}{特殊场合; 时机; 机会(noun.) 导致; 使发生(verb.)}
    \tword{chance}{tr\ae ns}{机会}
}
campus & "k\ae mp@s & noun. & 校园\crr
conviction & k@n"v\ci k\cs @n & noun. & 坚信; 判罪; 信服\crr
\linetab{
    \relative
    \tword{convict}{k@n"v\ci kt}{宣判有罪(verb.) 罪犯(noun.)}
    \tword{convince}{k@n"v\ci ns}{说服; 使确信}
    \example
    \eng He will appeal against his conviction.\newline
    \eng \ci f you have conviction about something, stick with it.\newline
    \eng \ci  have the conviction that he is right.
}
chubby & "t\cs 2bi & adj. & 丰满的; 圆胖的\crr
\linetab{
    \example
    \eng \ca  pretty child with chubby cheek. \chn 胖嘟嘟小脸的漂亮小孩.
}
analogy & @"n\ca l@d\cz i & noun. & 类比; 类推; 类似\crr
\linetab{
    \example
    \eng \cn o analogy exists between them.\newline
    \eng He expained the subject by analogy.
    \relative
    \tword{analogue}{"\ae n@""l\co g}{类似物(noun.) 模拟的; 指针式的(adj.)}
}
tug & t2g & verb.\newline noun. & 用力拉; 拽\crr
bucket & "b2k\ci t & noun. & 水桶; 吊桶\crr
judicial & d\cz u"di\cs @l & adj. & 司法的; 法庭的; 审判的\crr
\linetab{
    \relative
    \tword{judge}{d\cz 2d\cz }{法官; 裁判(noun.) 判断; 评判(verb.)}
    \tword{judicious}{d\cz u"d\ci \cs @s}{明智的; 判断正确的}
    \tword{judiciary}{d\cz \cu "d\ci s\ci @ri}{司法部}
    \tword{jury}{"d\cz \cu ri}{陪审团}
}
authoritative & @"\ct \co r@tet\ci v & adj. & 权威性的; 命令式的\crr
autograph & "\co t@gr\ae f & noun.\newline verb. & 亲笔签名\crr
slice & sla\ci s & noun.\newline verb. & 切片; 薄片; 部分; 片段\newline 切成片\crr
notorious & no\cu "t\co r\ci @s & adj. & 声名狼藉的; 臭名昭著的\crr
invaluable & \ci n"v\ae lj\cu @b@l & adj. & 无价的; 非常宝贵的\crr
\linetab{
    \relative
    \tword{valuable}{"v\ae lj\cu @bl}{有价值的; 贵重的; 值钱的}
    \tword{priceless}{"pra\ci sl\ci s}{无价的; 极贵重的; 极有趣的}
    \tword{inestimable}{\ci n"\ce st@m@b@l}{无价的; 无法估计的}
    \tword{impayable}{\ci m"p\ca @b@l}{无价的}
    \tword{unworthy}{2n"w\rse \ct i}{不值得的}
    \tword{worthless}{w\rse \ct l\ci s}{无用的}
    \tword{vauleless}{"v\ae ljul\ci s}{不值钱的}
}
excessively & \ci k"s\ce s\ci vli & adv. & 太; 过分地; 过度地\crr
monetary & "m\ca n\ci t\ce ri & adj. & 货币的; 金钱地\crr
evolutionary & ""\ce v@"lu\cs @n@ri & adj. & 进化的; 发展地; 演变的\crr
\linetab{
    \relative
    \eng \ci  hope this information serves each who draw on it well in your personal
    evolutionary pathway.\quad \phrase{draw on it well}{好好吸取它}
}
educate & "\ce d\cz @""ket & verb. & 教育\crr
conscientious & ""k\ca n\cs i"\ce n\cs @s & adj. & 本着良心的; 尽责的\crr
\linetab{
    \example
    \eng \ca  conscientious decision to speak out about injustice.
}
stockpile & st\ca kpa\ci l & noun.\newline verb & 大量储备; 囤积\crr
loyalty & l\co \ci @lti & noun. & 忠诚; 诚实\crr
manoeuvre & m@"nuv\rse & noun.\newline verb. & 移动; 演习; 操纵\newline 操纵; 控制; 刷花招\crr
manipulate & m@"n\ci pj\cu let & verb. &操纵; 使用\crr
primitive & "pr\ci m\ci t\ci v & adj. & 原始的; 简陋的\crr
primary & "pra\ci m@ri & adj. & 最初的; 首要的; 小学的; 原来的\crr
celebrity & s@"l\ce br\ci ti & noun. & 名人; 名声\crr
citizenry & "s\ci t\ci z@nri & noun. & 全体市民; 公民\crr
\linetab{
    \relative
    \tword{citizen}{"sItIz@n}{市民; 公民}
    \tword{civic}{"sIvIk}{市民的; 公民的; 城市的}
    \tword{civilise}{"sIv@""laIz}{使开化; 使文明; 教化}
    \texx{Rather than wipe slums(贫民窟) from the map, the authorities looked to civilise
    them and integrate them into the urban fabric(版图).}
    \tword{civilisation}{sIvIlI"zeS@n}{文明; 文化}
    \eng Both China and Africa are cradles of human civilisation and 
    lands of great promise.
}
intellectualism & ""\ci nt@"lekt\cs \cu @l\ci z@m & noun. & 理智主义; 知性主义\crr
assault & @"s\co lt  & noun.\newline verb. & 攻击; 袭击\crr
breeze & briz & noun. & 微风; 和风\crr
prolong & pr@"l\co \cn  & verb. & 延长; 拉长; 拖长\crr
\linetab{
    \example
    \eng For whom modern medicine has prolonged the physical agony of dying.\newline
    \eng We must prolong the runway of the airfield.\newline 
    \eng \ci  don't know how to prolong the life of my battery. 
}
modern & "m\ca d@rn & adj.\newline noun. & 现代的\newline 现代\crr
agony & "\ae g@ni & noun. & 痛苦\crr
controversy & "k\ca ntr@v@si & noun. & 争论; 论战\crr
convention & k@n"v\ce n\cs @n & noun. & 习俗; 大会; 协定\crr
\linetab{
    \relative
    \tword{conventional}{k@n"v\ce n\cs @nl}{常规的; 惯例的; 习俗的}
    \tword{conventionally}{k@n"v\ce n\cs @n@li}{照例地}
    \tword{conventionality}{k@n"v\ce n\cs @n@l\ci ty}{惯例; 习俗; 老套}
    \tword{conventionalization}{k@n"v\ce n\cs @n@la\ci ze\cs @n}{惯例化; 习俗化; 象征手法化}
    \tword{conventionalize}{k@n"v\ce n\cs @n@l"a\ci z}{使习俗化; 使样式化}
}
mischief & "m\ci st\cs \ci f & noun. & 恶作剧; 淘气; 伤害\crr
asset & "\ae s\ce t & noun. & 财富; 有价值地人或物\crr
stationary & "ste\cs @neri & adj. & 固定的; 不动的; 静止的\crr
collaborative & k@"l\ae b@ret\ci v & adj. & 合作的; 协力的\crr
\linetab{
    \example
    \eng Few of use inherently use our innovative and collaborative modes of thought.
}
critique & kr\ci "t\ci k & noun.\newline verb. & 批评; 评论文\newline 批判; 发表评论\crr
innumerable & \ci "num@r@bl & adj. & 无数的; 数不清的\crr
\linetab{
    \example
    \eng Human beings once created innumerable miracles.\quad \phrase{miracle}{奇迹}
}
precede & pr\ci "sid & verb. & 领先; 优于\crr
\linetab{
    \example
    \eng He preceded his speech with a few words of welcome to the special guests.
}
familiar & f@"m\ci l\ci \rse & adj. & 熟悉的\crr
\linetab{
    \relative
    \tphrase{be proficient in}{熟练; 精通}
    \tphrase{beadept at}{擅长; 精于}
    \tword{efficient}{\ci "f\ci \cs @nt}{效率高的}
    \tword{sufficient}{s@"f\ci \cs @nt}{足够的; 充足的}
    \tword{deficient}{d\ci "f\ci \cs @nt}{缺乏的}
}
integer & "\ci nt\ci d\cz \rse & noun. & 整数\crr
destination & ""d\ce st\ci "ne\cs @n & noun. & 目的地; 终点\crr
destiny & "d\ce st@ni & noun. & 命运; 天命; 天数\crr
destine & "d\ce st\ci n & verb. & 注定; 指定; 预定\crr
density & "d\ce ns\ci ti & noun. & 浓度; 密度\crr
introductory &  ""\ci ntr@"d2kt@ri & adj. & 引导的; 介绍的; 开端的\crr
\linetab{
    \example
    \eng \ca fter you have clearly and adequately developed the body of your paper, pay particular
    attention to the introductory and concluding paragraphs.
}
adequately & "\ae d\ci kw@tli & adj. & 充分的; 足够的; 恰当的\crr
modestly & "mm\ca d\ci stli & adv. & 谦虚地; 谨慎地; 适度地\crr
\linetab{
    \example
    \eng \ce ven the modestly educated sought an elevated tone when they put pen to paper
    before the 1960s.\chn 1960年以前, 甚至那些受过普通教育地人在下笔前都会寻求一种高雅地腔调.
}
volume & "v\ca ljum & noun. & 卷; 册; 体积; 音量\crr
\linetab{
    \example
    \eng \ct he \cn ational \ca cademy of \cs cience(\cn \ca \cs ) released a two-volumne report, 
    \ca pproaching \cd eath: \ci mproving Care at the \ce nd of Life.
}
exploit & \ci k"spl\co \ci t & verb.\newline noun. & 开拓; 利用; 开采; 剥削\newline 功绩\crr
\linetab{
    \example
    \eng \ct he capitalists exploit the workers in order to maximize profits.
}
alternative & \co l"t\rse n@t\ci v & adj.\newline noun. & 两者选一的; 供选择的\newline 两者选一的事物; 供替代的选择\crr
pipe & pa\ci p & noun.\newline verb. & 管子; 管道; 烟斗\newline 吹笛; 以管运输\crr
\linetab{
    \example
    \eng pipe dream \chn 白日梦\newline
    \eng He did pipe so that we can dance.
}
amplifier & "\ae mpl@""fa\ci \rse & noun. & 放大器; 扩音器; 扬声器\crr
opinion & @"p\ci nj@n & noun. & 意见; 看法; 观点\crr
sorrow & "s\ca ro\cu  & noun. & 悲哀; 悲痛\crr
ecdysis & "\ce kd\ci s\ci s & noun. & 蜕皮; 蜕化\crr
regulate & r\ce "gj\cu let & verb. & 管制; 调整\crr
\linetab{
    \example
    \eng Hormones regulate many insect functions, including ecdysis and metamorphosis.
    \chn 激素调节昆虫的许多功能, 包括蜕皮和变态.
}
desolate & "d\ce s@l\ci t & adj.\newline verb. & 荒凉的; 孤寂凄凉的\newline 使荒无人烟的\crr
\linetab{
    \example
    \eng \ca  big fire will desolate the whole land.\newline
    \eng Your leaving will desolate me.\newline
    \eng \ca  bleak and desolate landscape.
}
bully & "b\cu li & verb.\newline noun. & 恐吓; 胁迫; 欺负\newline 仗势欺人者; 横行霸道者\crr
\linetab{
    \example
    \eng \cs chool bullying is a type of bullying that occurs at any education setting.
}
coward & "ka\cu \rse d & noun. & 懦夫\crr
county & "ka\cu nti & noun. & 郡; 县\crr
coil & k\co il & verb.\newline noun. & 盘绕; 卷成圈\newline 卷; 盘卷之物; 线圈\crr
\linetab{
    \example
    \eng \ca  coil of rope.\newline
    \eng \ca  snake can coil around a branch.\newline
    \eng \ci  coil my hair at the back of my head.
}
scorn & sk\co rn & noun.\newline verb. & 轻蔑; 不屑\newline 蔑视; 看不起\crr
\linetab{
    \example
    \eng \ca n expression of scorn.\newline
    \eng \ct he \ce conomist piece exemplified this socially sanctioned scorn.\newline
    \eng Homework has never been popular with students and even many parents, but
    in recent years it has been particularly scorned.
    \relative
    \tword{scoff}{skOf}{笑柄; 嘲笑; 食物(noun.) 嘲笑; 嘲弄; 掠夺(verb.)}
    \tword{sneer}{snIr}{讥笑; 冷笑(verb. noun.)}
    \tword{jeer}{dZIr}{讥笑; 戏弄(verb. noun.)}
    \tword{scold}{skoUld}{责骂; 斥责(verb.) 常责骂人的人(noun.)}
    \tword{scout}{skaUt}{搜索; 侦察; 跟踪; 监视(verb. noun.) 童子军(noun.)}
    \tword{despise}{dI"spaIz}{看不起; 鄙视}
    \tword{contempt}{k@n"tEmpt}{蔑视; 轻视}
}
exemplify & \ci g"z\ce mpl@""fa\ci  & verb. & 举例说明; 例证\crr
sanction & "s\ae \cn k\cs @n & noun.\newline verb. & 批准; 允许; 认可; 制裁\crr
detective & d\ci "t\ce kt\ci v & noun.\newline adj. & 侦探\newline 侦探的\crr
geneticist & d\cz @"n\ce t\ci s\ci st & noun. & 遗传学家; 遗传学工作者\crr
quality & "kw\ca l@ti & noun. & 质量; 素质; 品质\crr
\linetab{
    \relative
    \tword{qualify}{"kw\ca l@fa\ci }{使合格; 资格}
    \tword{qualitative}{"kw\ca l@tet\ci v}{性质}
    \tword{qualification}{""kw\ca l\ci f\ci "ke\cs n}{资格; 条件; 合格证书}
    \tword{quantity}{"kw\ca nt@ti}{数量}
    \tword{quantify}{"kw\ca nt\ci fa\ci }{量度; 确定...数量; 量化(verb.)}
    \tword{quantitative}{"kwAnetetIv}{数量的; 定量的}
    \eng Quatitative accumulation leads to qualitative transformation.
}
enthusiastically & \ci n""\ct juz\ci "\ae st\ci kli & adv. & 热情地; 热心地\crr
\linetab{
    \relative
    \tword{enthuse}{\ci n"\ct juz}{兴奋地说; 使热情}
    \tword{enthusiast}{\ci n"\ct juzi\ae st}{热心者}
    \tword{enthusiastic}{\ci n""\ct juzi"\ae st\ci k}{热心的; 热情的}
}
tentative & "t\ce nt@t\ci v & adj.\newline noun. & 实验性的; 暂时的\newline 假设; 实验\crr
\linetab{
    \example
    \eng \cs o rar it has worked out a tentative plan with \cu \cs  officials to make amends with 
    \ca merican buyers of its diesel cars. \quad\word{amend}{@"m\ce nd}{修正; 改进(verb.) 补偿(noun.)}
}
megalith & "m\ce g@"l\ci \ct  & noun. & 巨石\crr
fulfill & f\cu l"f\ci l & verb. & 履行; 实现; 完成\crr
\linetab{
    \relative
    \tword{complete}{k@m"plit}{完成}
    \tword{completeness}{k@m"plitn@s}{完整性; 完备性}
    \tword{fulfillment}{f\cu l"f\ci lm@nt}{实现; 履行; 满足}
}
receptor & r\ci "sept\rse & noun. & 感受器; 受体\crr
superstitious & ""sup\rse "st\ci \cs @s & adj. & 迷信的\crr
deduct & d\ci "d2kt & verb. & 扣除\crr
\linetab{
    \example
    \eng \cd on't deduct the commission from the value of the consignment.
    \chn 不要从货物的价值中扣除佣金.
    \relative
    \tword{deduce}{d\ci "dus}{推断}
}
mythical & "m\ci \ct \ci k@l & adj. & 神话的; 虚构的\crr
\linetab{
    \relative
    \tword{myth}{m\ci \ct }{神话}
    \tword{mysterious}{m\ci "st\ci ri@s}{神秘的}
    \tword{mystic}{"m\ci st\ci k}{神秘的}
    \tword{mystery}{"m\ci st@ri}{谜; 难以理解的事物; 神秘感}
}
dusk & d2sk & noun. & 黄昏; 薄暮\crr
\linetab{
    \relative
    \tword{dawn}{d\co n}{黎明; 破晓(verb. noun.)}
    \tword{deck}{d\ce k}{甲板; 舱面}
}
abroad & @"br\co d & adv. & 在国外地; 出国\crr
\linetab{
    \relative
    \tword{aboard}{@"b\co d}{在船上}
    \tword{overseas}{""\co uv\rse "s\ci z}{国外的(adj.); 在国外(adv.)}
    \tword{domestic}{d@"m\ce st\ci k}{国内的; 家庭的}
}
vague & veg & adj. & 含糊的; 不明确的\crr
ascribe & @"skra\ci b & verb. & 把...归因于\crr
\linetab{
    \example
    \eng \ct hey ascribe his success to good luck.
}
humiliate & hju"m\ci li""et & verb. & 使屈辱; 使丢脸; 使蒙羞\crr
\linetab{
    \relative
    \tword{humidity}{hju"m\ci d\ci ti}{湿度; 潮湿}
    \tword{humble}{"h2mb@l}{卑下的; 谦逊的; 地位低下的}
    \tword{humility}{hju"m\ci l\ci ti}{谦逊}
    \tword{humiliation}{hju""m\ci li"e\cs @n}{羞辱; 耻辱; 丢脸}
}
simplify & "s\ci mpl@"fa\ci  & verb. & 简化\crr
magnitude & "m\ae gn\ci tud & noun. & 大小; 重要; 巨大; 震级\crr
\linetab{
    \relative
    \tword{magnificent}{m\ae g"n\ci f\ci s@nt}{宏观的; 壮观的}
    \tword{magnification}{""m\ae gn@f\ci "ke\cs @n}{夸大; 放大(noun.)}
    \tword{magnify}{"m\ae g@n\ci fa\ci }{夸大; 赞美(verb.)}
    \tword{magnific}{"m\ae g@n\ci f\ci k}{庄严的; 崇高的}
}
casual & "k\ae \cz u@l & adj. & 偶然的; 随意的; 非正式的; 临时的\crr
\linetab{
    \relative
    \tword{casualty}{"k\ae Zu@lti}{伤亡; 受伤的人; 事故; 临时救治所; 急诊室}
    \exx\eng The driver was rushed to casualty after the car accident.
}
nutrient & "nutri@nt & adj.\newline noun. & 营养的\newline 营养物\crr
\linetab{
    \relative
    \tword{nutrition}{nu"tr\ci \cs @n}{营养; 滋养(noun.)}
    \tword{nurture}{"n\rse t\cs \rse}{教育; 培养; 给与营养(noun. verb.)}
}
presuppose & ""pris@"po\cu z & verb. & 预先假定; 预料; 以...为先决条件\crr
\linetab{
    \example
    \eng \cd on't presuppose my guilt.
}
shipload & "sipl\co d & noun. & 一船的载货\crr
journalist & "d\cz \rse n@l\ci st & noun. & 新闻记者\crr
\ct hanksgiving & \ct \ae \cn ks"g\ci vi\cn  & noun. & 感恩节\crr
\linetab{
    \relative
    \tphrase{\cn ew Year's \cd ay}{元旦}
    \tphrase{Valentine"s \cd ay}{情人节}
    \tphrase{\ca pril Fool's \cd ay}{愚人节}
    \tphrase{Hallowmas}{万圣节}
    \tphrase{Christmas \cd ay}{圣诞节}
    \tphrase{\cs pring Festival}{春节}
    \tphrase{Lantern Festival}{元宵节}
}

acquire & @"kwa\ci \rse & verb. & 获得； 取得； 树立\crr
\linetab{
    \defn
    buy or obtain (an object or asset) for oneself.
    \exx
    \eng \ci nstead, tax will become payable automatically 30 days after the date that 
    the purchaser acquires the property or land.

}
spiritual & "sp\ci r\ci t\cs u@l & adj. & 精神上的; 心灵上的\crr
\linetab{
    \defn
    1. of, relating to, or affecting the human spirit or soul as opposed to material or physical things.\newline
    2. of or relating to religion or religious belief.
}
silver & "s\ci lv\rse & noun.\newline adj.\newline verb. & 银; 银色; 银器\newline 银的\newline 镀银\crr
\linetab{
    \relative
    \twocol{
    \tword{gold}{goUld}{金}
    \tword{copper}{"kAp@}{铜}
    \tword{iron}{"aI@rn}{铁}
    \tword{steel}{stil}{钢}
    }{%
    \tword{brass}{br\ae s}{黄铜}
    \tword{alloy}{"\ae l""OI}{合金}
    \tword{bronze}{brAnz}{青铜}
    \tword{metal}{"mEtl}{金属}
    }
}
expense & \ci k"sp\ce ns & noun. & 费用; 开支\crr
announcement & @"na\cu nsm@nt & noun. & 宣告; 通告\crr
assertion & @"s\textrhookrevepsilon \cs n & noun. & 断言; 主张; 声明\crr
\linetab{
    \tword{assert}{@"s\textrhookrevepsilon t}{断言; 宣称; 坚持}
}
settle & "s\ce tl & noun. & 定居; 安顿; 解决\crr
\linetab{
    \relative
    \tphrase{settle up}{解决; 还清欠款}
    \tphrase{settle for}{勉强接受; 愿意}
    \tphrase{settle in}{定居在; 坐在...里}
    \tphrase{settle into}{稳定成为}
    \tphrase{settle on}{停在; 决定}
    \tphrase{settle to}{安心于}
    \tphrase{settle with}{和...取得谅解}
}
collision  & k@"l\ci \cz @n & noun. & 碰撞; 冲突\crr
constantly & "k\ca nst@ntli & adv. & 不断地; 时常地\crr
curiosity & ""kj\cu ri"\ca s@ti & noun. & 好奇心\crr
horror & "h\co r\textrhookrevepsilon & noun. & 恐惧\crr
mechanism & "m\ce k@""n\ci z@m & noun. & 机械; 机械装置\crr
\linetab{
    \relative
    \tword{machine}{m@"\cs in}{机器; 机械(noun.)}
    \tword{machinery}{m@"\cs \ci n@li}{机械(noun.)}
    \tword{machinist}{m@"\cs \ci n\ci st}{机械师; 机械工}
    \tword{mechanic}{m\ci "k\ae n\ci k}{技工; 机修工}
    \tword{mechanical}{m\ci "k\ae n\ci k@l}{机械的; 呆板地}
    \tword{mechanically}{m\ci "k\ae n\ci k@li}{机械地}
}
parameter & p@"r\ae m\ci t\rse & noun. & 参数; 参量; 决定因素; 界限\crr
\linetab{
    \exx
    \eng \ct his is a parameter that determines the taste of a wine.\newline
    \eng We have to work within the parameter of budget.
}
aspect & "\ae sp\ce kt & noun. & 模样; 面貌; 方面; 朝向\crr
\linetab{
    \exx
    \eng \ct he house has a southern aspect.\newline
    \eng His brother is a man with a serious aspect.\newline
    \eng \ci n this aspect. \chn 从这一方面
}
intricate & "\ci ntr\ci k\ci t & adj. & 错综复杂的\crr
\linetab{
    \exx
    \eng \ci  have a novel with an intricate plot.\newline
    \eng \ct he intricate machine requires a skilled operator.
    }
\end{engvc}

\medskip
\begin{engvc}[18-8-29]
fortnightly & "f\co rtna\ci tli & adj.\newline adv.\newline noun. & 两星期一次的\newline 两星期一次地\newline 双周刊\crr
subsidize & "s2bs\ci da\ci z & verb. & 资助; 以津贴补助\crr
\linetab{
    \exx
    \eng \ci t is a great economic burden for a government with tight budget to subsidize artists and drama companies.\newline
    \eng subsidize laziness.
}
inevitable & \ci n"\ce v\ci t@b@l & adj. & 不可避免的; 必定的\crr
\linetab{
    \relative
    \tword{evade}{\ci "ved}{逃避; 回避; 躲避}
    \tword{evasion}{\ci "ve\cz @n}{逃避; 回避(noun.)}
    \tword{unavoidable}{""2n@"v\co \ci d@b@l}{不可避免的}
}
invest & \ci n"v\ce st & verb. & 投资\crr
verge & v\rse \cz  & noun.\newline verb. & 边缘; 边界\newline 濒临; 接近\crr
\linetab{
    \exx
    \eng \ct he economy is on the verge of collapse.\newline 
    \eng \ct hey verge towards a quarrel.
}
consent & k@n"s\ce nt & noun.\newline verb. & 同意; 允许\crr
\linetab{
    \relative
    \tphrase{with the consent of sb.}{经某人同意}
}
vicious & "v\ci \cs @s & adj. & 邪恶的; 恶性的; 堕落的\crr
hitherto & "h\ci \cd \rse tu & adv. & 迄今; 到目前为止\crr
patronize & "petr@na\ci z & verb. & 惠顾; 资助\crr
\linetab{
    \exx
    \eng \ct he \co ct.28 issue of \cn ewsweek reported that 2 million gamblers patronize 1800 virtual casinos every week.
}
insulate & "\ci ns@let & verb. & 隔离; 使隔热; 使隔音\crr
petroleum & p@"tro\cu li@m & noun. & 石油\crr
\linetab{
    \tword{gasoline}{g\ae s@"lin}{汽油}
    \tword{gasolene}{"g\ae s@lin}{汽油}
    \tword{diesel}{"d\ci z@l}{柴油; 柴油车}
    \tword{petrol}{"p\ce tr@l}{汽油}
}
condemn & k@n"d\ce m & verb. & 谴责; 判刑\crr
prone & pro\cu n & adj. & 俯卧的; 易于...的; 有...倾向的\crr
\linetab{
    \exx
    \eng be prone to snap overreactions.\newline
    \eng He was prone to anger.
}
outfit & "a\cu t""f\ci t & noun.\newline verb. & 全套装备; 配备; 机构\newline 装备; 配置设备\crr
tempt & t\ce mpt & verb. & 诱惑; 引诱; 怂恿\crr
contempt & k@n"t\ce mpt & noun. & 蔑视; 轻蔑\crr
criterion & kra\ci "t\ci ri@n & noun. & 标准; 准则; 规范\crr
\linetab{
    \exx\eng Practice is the sole criterion for testing truth.
}
summon & "s2m@n & verb. & 召唤; 召集; 鼓起\crr
\linetab{
    \exx
    \eng \ct o summon the courage to tell the truth.\newline
    \eng \ct hey summon men to defend their country.
}
envision & \ci n"v\ci \cz @n & verb. & 想象; 设想\crr
\linetab{
    \exx
    \eng \ct hat is because Congress has always envisioned joint federal-state immigration enforcement.\newline
    \eng \ci Q tests ask you to compete verbal and visual analogies, to envision paper
    after it has been folded an cut ...
    \relative
    \tword{revision}{r\ci "v\ci \cz @n}{修订}
    \tword{prevision}{pr\ci "v\ci d\cz @n}{预见; 预测}
    \tword{provision}{pr@"v\ci d\cz @n}{规定; 预备; 供应}
    \tword{precision}{pr\ci "s\ci d\cz @n}{精确度}
}
nasty & "n\ae sti & adj. & 丑陋的; 令人不愉快的; 下流的; 肮脏的\crr
foe & fo\cu  & noun. & 敌人; 仇敌\crr
\linetab{
    \relative
    \tword{toe}{toU}{脚趾; 脚尖(noun.) 用脚尖触; 动脚尖}
}
grease & gris & noun.\newline verb. & 油脂; 润滑油; 贿赂\newline 给...加润滑油; 贿赂\crr
\linetab{
    \relative
    \tword{lubricate}{"lubr\ci ""ket}{润滑(verb.)}
    \tword{lubricant}{"lubrIk@nt}{润滑的}
    \tword{bribe}{bra\ci b}{贿赂(verb.) 贿赂物(noun.)}
}
sustainability & s@"sten@"b\ci l@ti & noun. & 可持续性; 耐久性\crr
\linetab{
    \relative
    \tword{sustain}{s@"sten}{承受; 支撑; 维持}
    \tword{sustainable}{s@"sten@bl}{可支撑的; 可以忍受的; 可持续的}
    \tword{substance}{"s2bst@ns}{物质; 实质; 主旨; 要点}
    \tword{substantial}{s@b"s\ae nS@l}{大量的; 实质的; 坚固的}
}
exclusionary & \ci k"sklu:\cz @nri & adj. & 排斥的; 排除在外的\crr
\linetab{
    \exx
    \eng \ct he earlier exclusionary culture.
}
transaction & tr\ae n"z\ae k\cs @n & noun. & 交易; 业务\crr
fossil & "f\ca sl & noun. & 化石; 守旧的事物\crr
reel & ril & noun.\newline verb. & 卷筒; 卷轴; 卷盘\newline 卷; 绕; 踉跄; 蹒跚\crr
\linetab{
    \eng My head reeled with the facts and figures.
    \relative
    \tword{reed}{rid}{芦苇; 舍簧}
}
entitlement & \ce n"ta\ci tlm@nt & noun. & 权益; 应得的权利; 权力资格\crr
\linetab{
    \exx
    \eng \ci nstead, the claimant receives a time-limited allowance, conditional on actively seeking a job; 
    no entitlement and no insurance.
}
rein & ren & noun.\newline verb. & 缰绳; 驾驭; 控制\newline 控制; 驾驭\crr
\linetab{
    \exx
    \eng You must learn to rein your temper.
}
inn & \ci n & noun. & 客栈; 小旅馆\crr
confer & k@n"f\rse & verb. & 授予; 赋予; 商讨\crr
\linetab{
    \exx\eng \ct he science of confering the human capabilities on machine.
}
impart & \ci m"p\ca rt & verb. & 传授; 给予; 告知\crr
\linetab{
    \exx\eng \ct o impart some advice.
    \relative
    \tword{impact}{"Im""p\ae kt}{影响; 冲击}
    \tword{impair}{Im"per}{损害}
    \tword{compart}{k@m"pAt}{分隔}
    \tword{repair}{rI"per}{修理}
    \tword{impartial}{Im"pArSl}{公平的; 无偏见的}
}
dolidarity & ""s\ca l@"d\ae r@ti & noun. & 团结; 一致; 休戚相关\crr
avail & @"vel & verb.\newline noun. & 有用; 有益\crr
intangible & \ci \cn "t\ae nd\cz @b@l & adj.\newline noun. & 不可捉摸的; 无形的\newline 无形的东西\crr
\linetab{
    \exx\eng \ca nd perhaps faintly, they hint that people should look to intangible quialities like 
    character and intellect rather that dieting.
}
uproar & "2p""p\co r & noun. & 喧嚣; 骚动; 吵闹\crr
asteroid & "\ae st@""r\co id & noun. & 小行星\crr
migrate & "ma\ci gret & verb. & 迁移; 迁居; 迁徙\crr
\linetab{
    \relative
    \tword{migrant}{"ma\ci gr@nt}{候鸟}
    \tword{emigrate}{"\ce m\ci ""gret}{迁出}
    \tword{emigrant}{"\ce m\ci gr@nt}{移民}
    \tword{immigrate}{"\ci m\ci ""gret}{移入}
    \tword{immigrant}{"\ci m\ci gr@nt}{移民; 移民de}
}
allot & @"l\ca t & verb. & 分配; 分派\crr
ritual & "r\ci t\cs u@l & noun.\newline adj. & 仪式; 典礼; 例行习惯\newline 仪式的; 惯常的\crr
doom & dum & noun.\newline verb. & 厄运; 毁灭; 死亡\newline 注定; 判决\crr
\linetab{
    \exx\eng \ct he arguments doom their marriage to failure.
}
tiresome & "ta\ci \rse s\rse m & adj. & 令人厌烦的\crr
\linetab{
    \relative
    \tword{fearsome}{"f\ci rs@m}{可怕的; 吓人的}
    \tphrase{wholesome}{健康的; 有益身心的}
    \tphrase{troublesome}{令人讨厌的; 引起烦恼的}
    \tphrase{handsome}{英俊的; 健美的; 美观的; 大方的}
    \tphrase{awesome}{可怕的; 令人敬畏的; 极好的}
    \tphrase{bothersome}{麻烦的; 令人讨厌的}
    \tphrase{winsome}{迷人的; 可爱的; 引人注目的}
    \tphrase{chromosome}{染色体}
}
refrigerator & r\ci "fr\ci d\cz @""ret\rse & noun. & 冰箱\crr
promising & "pr\ca m\ci s\ci \cn  & adj. & 有希望的; 有前途的\crr
peculiar & p\ci "kjulj\rse & adj. & 古怪的; 不寻常的; 特有的; 独特的\crr
\linetab{
    \exx\eng \ct he force of geographic conditions peculiar to \ca merica.
    \chn 美洲特有的地理条件.
    \exx\eng He has his own peculiar style which you'll soon get used to.
    \relative
    \tphrase{be peculiar to sb./sth.}{某人/某物特有的}
}
vaunt & v\co rnt & noun.\newline verb. & 吹嘘; 自夸\crr
authentic & \co "\ct \ce nt\ci k & adj. & 真正的; 真实的; 真迹的\crr
premise & "pr\ce m\ci s & noun.\newline verb. & 前提; 假定\newline 作出前提\crr
estimate & "\ce st@""met & verb.\newline noun. & 估算; 估价\newline 估价; 估算\crr
\linetab{
    \exx\eng My estimate of his abilities was wrong.
    \relative
    \tword{appraise}{@"prez}{评价; 估价; 鉴定}
    \tword{assess}{@"s\ce s}{评定; 评估; 估算}
    \tword{evaluate}{i"v\ae lj\cu et}{估价; 评价}
}
misery & "m\ci z@ri & noun. & 痛苦; 悲惨\crr
\linetab{
    \exx\eng Fame brought her nothing but misery.
    \chn 名声只给他带来痛苦.
    \relative
    \tword{miserable}{"mIz\rse r@b@l}{痛苦的; 悲惨的; 卑鄙的}
    \tword{commiserate}{k@"mIz@""ret}{同情; 怜悯(verb.)}
}
surpass & s\rse "p\ae s & verb. & 超过; 胜过; 优于\crr
dominant & "darm@n@nt & adj. & 支配的; 占优势的; 显性的\crr
\linetab{
    \relative
    \tword{dominate}{"d\ca minet}{统治}
    \tword{domain}{do\cu"men}{领土; 领域}
    \tword{predominant}{pr\ci "d\ca m\ci n@nt}{主导的; 支配的; 占有优势的; 主要的}
    \tword{predominate}{pr\ci "d\ca m\ci net}{占主导地位; 占支配地位}
}
attain & @"ten & verb. & 达到; 获得\crr
\linetab{
    \relative
    \tword{detain}{d\ci "ten}{拘留}
    \tword{sustain}{s@"sten}{支撑}
    \tword{obtain}{@b"tein}{获得; 得到}
    \tword{contain}{k@n"ten}{包含}
    \tword{maintain}{men"ten}{维持}
    \tword{retain}{ri"ten}{保留}
    \tword{entertain}{""ent\rse ten}{娱乐}
}
meticulous & m@"t\ci kj\cu l@s & adj. & 一丝不苟的; 谨慎的\crr
devise & d\ci "va\ci z & verb.\newline noun. & 设计; 发明; 想出; 策划; 遗赠\newline 遗赠\crr
\linetab{
    \exx\eng divise a solution and implement it.\newline
    \eng he isn't going to devise his property to his son.\newline
    \eng they devise a machine.\newline
    \eng \ca  new system has been devised to control traffic in the city.
}
covenant & "k2v@n@nt & noun.\newline verb. & 契约; 协约\newline 订立契约\crr
interminable & \ci n"t@m@n@b@l & adj. & 没完没了的\crr
sacrifice & "s\ae kr@""fa\ci s & noun.\newline verb. & 牺牲; 献出\newline 供奉; 祭品; 牺牲\crr
\linetab{
    \exx\eng He gave his life as a sacrifice for his country.
}
novelty & "n\ca vlti & noun. & 新奇的事物; 小玩意\crr
\linetab{
    \relative
    \tword{innovate}{"\ci n@""vet}{创新}
    \tword{innovatioin}{"\ci n@""veS@n}{创新}
    \tword{renovate}{"r\ce n@vet}{翻新}
    \tword{renovation}{""r\ce n@"ve\cs n}{翻新}
}
liquor & "l\ci k\rse & noun. & 酒; 烈酒\crr
presume & pr\ci"zum & verb. & 假设; 设想; 认定; 冒昧\crr
\linetab{
    \relative
    \tphrase{presume}{侧重从过去经验或根据某些感觉把某事认定为事实}
    \tphrase{assume}{指毫无根据的武断推测}
    \tphrase{suppose}{缺乏确切事实, 根据一些现象进行的推测; 有时仅仅表示自己的观点}
    \tphrase{guess}{个人的主观臆断或碰运气的猜测}
}
tumble & "t2mb@l & verb.\newline noun. & 跌倒; 摔倒; 暴跌\crr
excursion & Iks"k\textrhookrevepsilon\cz n & noun. & 远足; 短途旅行\crr
incursion & In"k\rse\cz n & noun. & 侵犯; 入侵\crr
catastrophe & k@"t\ae str@fi & noun. & 灾难\crr
\linetab{
    \relative
    \tword{cataclysm}{"k\ae t@ ""kl\ci z@m}{大灾难; 洪水; 剧变}
    \tword{cataract}{"k\ae t@""r\ae kt}{瀑布; 洪流; 白内障}
}
submerge & s@b"m\rse dZ & verb. & 潜水; 浸没\crr
\linetab{
    \exx\eng all his life was submerged in the liberation of the people.\newline
    \eng I watchecd the submarine submerge.\newline
    \eng I often submerge myself in study.
}
defy & d\ci "fa\ci  & verb. & 不服从; 蔑视; 挑衅\crr
\linetab{
    \exx\eng if you defy the law, you will be sent to prison.\newline
    \eng gdp as the measure of success is widely defied in the uk.
}
fierce & f\ci rs & adj. & 凶猛的; 凶狠的\crr
cherish & "t\cs\ce r\ci s & verb. & 珍爱; 爱惜; 怀念; 怀有; 抱有\crr
\linetab{
    \exx\eng I cherish the hope of seeing him again.
}
amateur & "\ae m@t\rse & noun.\newline adj. & 业余爱好者\newline 业余的\crr
indignation & ""\ci nd\ci g"ne\cs @n & noun. & 愤怒; 愤慨; 义愤\crr
\linetab{
    \exx\eng feelings of righteous indignation, it seems, are not the preserve of people alone.
    \relative
    \tword{indignant}{\ci n"d\ci gn@nt}{愤怒的; 义愤的}
    \tword{indignity}{\ci n"d\ci gniti}{侮辱; 轻蔑}
    \tword{dignity}{"d\ci gn@ti}{尊严; 高贵}
    \tword{dignitary}{"d\ci gn\ci teri}{达官贵人}
}
stride & stra\ci d & noun.\newline verb. & 大步行走; 跨一大步\newline 大步; 步伐\crr
conspicuous & k@n"sp\ci kj\cu @s & adj. & 显著的; 显眼的; 显而易见的\crr
\linetab{
    \exx\eng a traffic sign should be conspicuous.\newline
    \eng The most conspicuous way in which the old politics is changing 
    is in the growing use of referendums.
}
sham & \cs\ae m & noun.\newline adj.\newline verb. & 假象; 虚假; 枕头套\newline 虚假的;假装的\newline 假装; 佯装\crr
breach & brits & noun.\newline verb. & 缺口; 破裂; 违背\newline 在...上打开缺口; 违反; 突破\crr
\linetab{
    \exx\eng the company argued the breack of the advertising code was a misunderstanding.
}
verdict & "v\rse d\ci kt & noun. & 裁决; 判决; 定论\crr
appall & @"p\co l & verb. & 使胆寒; 使惊骇\crr
\linetab{
    \exx\eng their terrible crime appal everyone.\newline 
    \eng the prospect of another war appalled us.
}
merchandise & "m\rse\cs @nda\ci s & noun.\newline verb. & 商品; 货物\newline 推销; 销售\crr
adornment & @"d\co rnm@nt & noun. & 装饰; 装饰品\crr
\linetab{
    \exx\eng cosmetics are used for adornment.\newline
    \eng it was a building without any adornment.
}
witch & w\ci t\cs & noun.\newline verb. & 巫婆; 女巫; 魔女\newline 施巫术\crr
mindset & "ma\ci ndset & noun. & 思维模式; 心态\crr
\linetab{
    \defn 
    the established set of attitudes held by someone.
}
territory & "t\ce r@t\co ri & noun. & 领土; 领域\crr
insatialble & \ci n"se\cs @b@l & adj. & 无法满足的; 贪得无厌的\crr
\linetab{
    \exx\eng PetroChina is seeking to tap into overseas reserves to 
    feed China's insatiable demand for oil.
    \relative
    \tword{satiable}{"se\cs @b@l}{可满足的}
    \tword{satiation}{""se\cs \ci e\cs @n}{满足; 饱食; 饱满; 厌腻}
    \tword{satiated}{"se\cs \ci et\ci d}{对...厌倦; 充分满足}
}
signify & "s\ci gn\ci fa\ci & verb. & 表示; 预示; 象征; 要紧\crr
\linetab{
    \exx\eng doesn't it signify to go or to say?\newline
    \eng i signify my approval.
}
wardrobe & "w\co rdro\cu b & noun. & 衣柜; 衣橱\crr
scout & ska\cu t & verb.\newline noun. & 侦察; 巡视; 搜寻; 物色\newline 侦察; 侦察兵; 童子军\crr
apparatus & ""\ae p@"r\ae t@s & noun. & 装置; 仪器; 器械; 器官\crr
contemplate & "k\ca nt@mplet & verb. & 注视; 凝视; 沉思; 思忖; 期望\crr
endeavor & \ci n"d@v\rse & verb.\newline noun. & 尽力; 竭力\crr
masturbate & "m\ae st\rse bet & verb. & 自慰; 手淫\crr
parade & p@"red & noun.\newline verb. & 游行; 阅兵\crr
warehouse & "we\rse ha\cu s & noun.\newline verb. & 仓库; 货栈\newline 把...放入仓库\crr
\linetab{
    \exx\eng please warehouse the goods.\newline
    \eng they store the goods in a warehouse.
}
correlate & "k\co r@let & verb. & 使相互关联\crr
\linetab{
    \exx\eng negatively / positively correlate with ... \chn 与 ... 负相关 / 正相关.\newline
    \eng these figures seem to correlate.
}
aviation & ""ev\ci"e\cs @n & noun. & 飞行; 航空; 航空术\crr
shilling & "s\ci l\ci\cn & noun. & 先令\crr
hostility & h\ca"st\ci l@ti & noun. & 敌意; 敌对; 对抗\crr
investigate & \ci n"v\ce st\ci""get & verb. & 调查; 研究\crr
rut & r2t & noun. & 车辙; 发情期; 老一套\crr
\linetab{
    \exx\eng once those ruts of procedure are worn into the brain, they are there to stay.
}
depart & d\ci"part & verb. & 离开; 背离; 去世; 离职\crr
\linetab{
    \relative
    \tword{departure}{d\ci"p\ca t\cs\rse}{离开}
    \tword{department}{d\ci"p\ca tm@nt}{系; 部门}
}
agenda & @"d\cz\ce nd@ & noun. & 议事日程; 议程\crr
\linetab{
    \relative
    \tword{agency}{"ed\cz @nsi}{代理; 中介}
    \tword{agent}{"ed\cz @nt}{特工; 代理人}
}
accord & @"k\co rd & verb.\newline noun. & 符合; 一致; 给予\newline 协议; 条约; 协调\crr
\linetab{
    \exx\eng his actions accord with his words.\newline 
    \eng the queen accorded him the greatest honor.
}
peninsula & p@"n\ci ns@l@ & noun. & 半岛\crr
shove & \cs2v & verb. & 挤; 推; 撞\crr
corrode & k@"ro\cu d & verb. & 侵蚀; 腐蚀\crr
tramp & tr\ae mp & noun.\newline verb. &: 流浪汉; 流浪乞丐; 徒步旅行\newline 步行; 踩; 塌\crr
solitary & "s\ca l@t\ce ri & adj. & 独自的; 单独的; 孤寂的\crr
\linetab{
    \relative
    \tword{solitude}{"s\ca l@tud@}{孤独}
    \tword{solidarity}{""s\ca l\ci"d\ae r@ti}{团结}
}
cultivation & ""k2lt@"ve\cs@n & noun. & 栽培; 种植; 培养\crr
\linetab{
    \exx\eng the cultivation of friendship.\newline 
    \eng moral self-cultivation.\newline
    \eng the cultivation of an attitude.
    \relative
    \tword{cultivate}{"k2lt@vet}{培养; 栽培}
}
revitalize & ri"va\ci tl""a\ci z & verb. & 使新生; 使复兴\crr
\linetab{
    \exx\eng revitalize a sluggish global economy
}
plow & pla\cu & noun.\newline verb. & 犁\crr
screw & skru & noun.\newline verb. & 螺丝钉\newline 拧紧\crr
cereal & "s\ci ri@l & noun. & 谷类; 谷类食品\crr
comb & ko\cu m & noun.\newline verb. & 梳子\newline 梳理; 搜寻\crr
storey & "st\co ri & noun. & 楼层\crr
awe & \co & noun.\newline verb. & 敬畏\newline 使敬畏\crr
\linetab{
    \exx\eng we listended to the scholar with awe.\newline
    \eng she filled me with a sense of awe.\newline
    \eng these wonders awe people.
}
mildly & "ma\ci ldli & adv. & 和善地; 轻微地\crr
corrupt & k@"r2pt & adj.\newline verb. & 腐败的; 贪污的; 受贿地\newline 使腐败; 使堕落\crr
intermittent & ""\ci nt\rse"m\ci t@nt & adj. & 间断的; 断断续续的\crr
amendment & "@m\ce ndm@nt & noun. & 修改; 修正\crr
repertoire & "rep\rse tw\ca r & noun. & 全部节目; 全部才能\crr
marvelous & "m\ca rv@l@s & adj. & 令人惊异的; 好极的\crr
obedient & o"bidi@nt & adj. & 顺从的\crr
dispose & d\ci"spo\cu z & verb. & 安排; 安置; 处理\crr
\linetab{
    \relative
    \tword{disposable}{dI"spoUz@bl}{用后即丢弃的; 一次性的; 可自由支配的}
}
seldom & "s\ce ld@m & adv.\newline adj. & 很少; 难得\newline 不常的; 稀少的\crr
inedible & \ci n"\ce d@b@l & adj. & 不能吃的; 不宜食用的\crr
elaborate & \ci"l\ae b@ret & verb.\newline adj. & 精心制作; 详尽阐述\newline 精心制作的; 详尽的\crr
\linetab{
    \exx\eng she went on to elaborate her argument.
    \relative
    \tword{labor}{"leb\rse}{劳动; 劳工; 分娩(noun.) 干苦力活; 努力; 分娩(verb.)}
}
fertile & "f\textrhookrevepsilon t@l & adj. & 富饶的; 多产的\crr
courtesy & "k\rse t@si & noun. & 礼貌; 谦恭\crr
apparasial & @"pr\ce z@l & noun. & 评价; 评定\crr
deplore & d\ci"pl\co r & verb. & 谴责; 强烈反对\crr
refrain & r\ci"fren & verb.\newline noun. & 克制; 节制\newline 副歌\crr
\end{engvc}

\medskip
\begin{engvc}[18-8-30]
constrain & k@n"stren & verb. & 迫使; 约束\crr
\linetab{
    \exx\eng every country has laws that contrain political freedom.
}
constraint & k@n"strent & noun. & 约束; 限制; 拘束\crr
\linetab{
    \exx\eng in china's network world, there are many constraint that prevent people knowing 
    the damage of communism. and the polices of china just are son of bitch.
}
process & "prases & noun.\newline verb. & 进程; 过程; 工序\newline 处理; 加工\crr
\linetab{
    \exx\eng the light weight process(lwp) contain independent context and stack is thread that 
    be designed for multitask in linux.
}
rescue & "reskju & noun.\newline verb. & 救援; 营救\crr
\linetab{
    \exx\eng he dived from the bridge to rescue the drowning child.
}
overturn & "ouv\rse"t\rse n & verb.\newline noun. & 推翻; 倾覆; 打倒\crr
\linetab{
    \exx\eng i overturn a glass of water.
}
assumption & @"s2mps@n & noun. & 假设; 设想\crr
\linetab{
    \tphrase{on the assumption of}{在...的前提下}
}
assassinate & @"s\ae s@net & verb. & 暗杀; 行刺\crr
\linetab{
    \tword{assassin}{@"s\ae sn}{暗杀者}
    \tword{saber}{"se b\rse}{剑士}
    \tword{lancer}{"l\ae ns\rse}{枪兵}
    \tword{caster}{"k\ae st\rse}{魔法师}
    \tword{archer}{"arts\rse}{弓箭手}
    \tword{rider}{"raid\rse}{骑兵}
    \tword{berserker}{b@r"z@rk\rse}{狂战士}
}
tide & taid & noun. & 潮汐; 潮流\crr
\linetab{
    \exx\eng tide is unlikely to turn back.
}
statistics & st@"tistiks & noun. & 统计学; 统计数字\crr
\linetab{
    \tword{statistic}{st@"tistik}{统计数字}
    \tword{statistical}{st@"tistikl}{统计的}
    \tword{statistician}{""st\ae ti"stis@n}{统计员}
}
originate & @"r\ci d\cz@""net & verb. & 起源; 发源; 发生\crr
\linetab{
    \tword{origin}{@"r\ci d\cz @n}{起源}
    \tword{original}{@"r\ci d\cz @n@l}{起初的}
    \tword{originality}{@"r\ci d\cz @""n\ae l@ti}{独创性; 新颖性}
    \tword{initiate}{\ci "n\ci \cs iet}{开创; 传授(verb.) 被传授初步知识的人(noun.) 被传授初步知识的(adj.)}
    \tword{initial}{\ci "n\ci \cs @l}{最初的; 开始的(adj.) 首字母(noun.) 用名字的首字母签名于(verb.)}
    \tword{initiation}{\ci ""n\ci \cs i"es@n}{开始; 创始; 入会仪式}
    \tword{initialize}{\ci "n\ci \cs @""la\ci z}{初始化}
    \tword{initiative}{\ci "n\ci \cs @t\ci v}{主动性; 首创精神}
}
succession & s@k"ses@n & noun. & 连任; 继任\crr
\linetab{
    \exx\eng there was a dispute about the rightful succession to the throne.
}
dispute & dI"spjUt & noun.\newline verb. & 争议; 争端\newline 争吵; 争议\crr
\linetab
{
    \relative
    \tphrase{argument}{辩论双方均以事实或者理由来说服对方的辩论}
    \tphrase{conflict}{双方坚持己见, 怀有敌意的争论, 分歧严重. 有时无法用言语解决, 自得诉诸武力.}
    \tphrase{debate}{经过仔细组织和计划的个人或团体之间的辩论}
    \tphrase{dispute}{时间长, 言辞激烈, 争锋相对的争辩}
    \tphrase{quarrel}{言辞的激烈的争吵}
    \tphrase{strife}{不可缓和的矛盾引起的争吵和斗殴}
}
revitalize & rI"vaItl""aIz & verb. & 使新生; 使复兴\crr
exclude & Ik"sklud & verb. & 拒绝; 排斥; 排除\crr
\linetab{
    \exx\eng be excluded from\newline
    \eng the price will exclude accommodation.\newline
    \eng they exclude me from attending their club.
}
despair & dI"sper & noun.\newline verb. & 绝望\newline 绝望\crr
\linetab{
    \tword{desperate}{"dEsp@rIt}{绝望的; 不顾一切的; 拼死的; 极度渴望的}
}
violation & ""vaI@"les@n & noun. & 违反; 妨碍; 侵犯; 违背\crr
\linetab{
    \tword{violate}{"vaI@""let}{违反; 侵犯}
    \tword{violent}{"vaI@l@nt}{暴力的; 凶猛的}
}
epidemic & ""\ce p\ci "d\ce m\ci k & noun.\newline adj. & 流行病\newline 流行性的\crr
\linetab{
    \exx\eng \ct he outbreak of swine flu that was first detected in Mexico was
    declared a global epidemic on June 11, 2009.
}
stern & st\rse n & adj.\newline noun. & 严厉的; 苛刻的\newline 船尾\crr
rival & "raIvl & noun.\newline verb. & 竞争者; 敌手\newline 竞争\crr
certainty & "s\rse tnti & noun. & 确定; 无疑\crr
zoom & zum & verb.\newline noun. & 作嗡嗡声; 飞驰; 陡升\newline 直线上升; 激增; 嗡嗡声\crr
calculate & "k\ae lkj@"let & verb. & 计算\crr
fascinate & "f\ae s@""net & verb. & 强烈吸引住; 使着迷\crr
\linetab{
    \exx\eng his ideas fascinate the students.\newline
    \eng her beauty fascinate me.\newline
    \eng the exotic atmosphere will fascinate you.
}
imaginary & \ci"m\ae d\cz ineri & adj. & 虚构的; 想象的\crr
legitimate & l@"d\cz \ci t@m\ci t & adj.\newline verb. & 合法的; 合理的; 法律认可的\newline 使合法; 认为正当\crr
\linetab{
    \exx\eng 
    \ct he French government has comdemned the coup in Haiti and has demanded 
    the restoration of legitimate government.\chn \word{coup}{ku}{政变; 棒击; 机敏的策略}
    \relative
    \tword{legitimacy}{l@"d\cz \ci t@m@si}{合法性; 正统性; 合理性}
    \eng \cs ome of the clergy refused to acknowledge the new king's legetimacy.\chn \word{clergy}{"kl\textrhookrevepsilon rd\cz i}{牧师; 教士}
    \tword{legislate}{"l\ce d\cz \ci ""slet}{立法(verb.)}
    \eng Most member countries have already legislated against excessive overtime.\newline
    \tword{legislation}{""l\ce d\cz \ci "sle\cs @n}{立法; 法规(noun.)}
    \eng \ct he new industrial relations legislatioin curbed the power of unions.\chn \word{curbe}{k\textrhookrevepsilon rb}{限制; 抑制}
    \tword{legislature}{"l\ce d\cz \ci slet\cs \rse}{立法机关; 立法机构}
    \eng \ct here rules may have the same effect as the law passed by legislature.\newline
    \tword{legal}{"lig@l}{法律的; 合法的(adj.) 法定权利(noun.)}
    \tword{legality}{li"g\ae l\ci ti}{合法性}
    \eng \ct he legal character of the jail determines that the administration of jails
    must insist the principle of legality.\newline
    \tword{delegate}{"d\ce l\ci ""get}{代表(verb. noun.)}
    \eng How many of their activities can be safely and effectively delegate to the less trained staff.\newline
    \tword{relegate}{"r\ce l\ci ""get}{放逐; 贬职}
    \eng \ct hrough the image of these studies can be seen that the word relegate people in the 
    inner world and the period of ideal personality.
}
paralyze & "p\ae r@""laIz & verb. & 使麻痹; 使瘫痪; 使无效; 使停止活动\crr
\linetab{
    \relative
    \tword{paralysis}{p@"r\ae lIsIs}{瘫痪; 麻痹(noun.)}
}
paradise & "p\ae r@""daIs & noun. & 天堂; 伊甸园; 乐园\crr
participate & p\ca r"tIsIpet & verb. & 参与; 参加\crr
\linetab{
    \relative
    \tword{participant}{pAr"tIsIp@nt}{参与者; 参加者}
}
questionnaire & ""kwestS@"ner & noun. & 调查问卷; 调查表\crr
\linetab{
    \exx\eng three years after joining the study, the women filled out a questionnaire about their happiness.
}
accept & \relax\ae k"sEpt & verb. & 接受; 认可; 同意\crr
\linetab{
    \relative
    \tword{receive}{rI"siv}{接收}
    \tword{reception}{rI"sEps@n}{接待}
    \tword{conceive}{k@n"siv}{设想}
    \tword{concept}{"kAnsept}{概念}
    \tword{deceive}{dI"siv}{欺骗}
    \tword{deception}{dI"sEps@n}{骗局}
    \tword{perceive}{p\rse "siv}{察觉(verb.)}
    \tword{perception}{p\rse "seps@n}{观念}
}

thrill & trIl & noun.\newline verb. & 兴奋; 震颤感\newline 激动; 震颤; 兴奋\crr
\linetab{
    \exx\eng \ct he most thrilling explanation, unfortunately, a little defective.
}
throughtout & Tru"aUt & preposition.\newline adv. & 遍及; 各处; 自始自终\newline 自始自终; 到处\crr
\linetab{
    \exx\eng the experiences will be unforgetable throughtout my life.\newline
    \eng it rained throughtout the night.\newline
    \eng he is famous throughtout the world.
}
perpetual & p\rse"petSu@l & adj. & 持续的; 长久的\crr
\linetab{
    \relative
    \tword{perpetuity}{""p\rse p@"tu@ti}{永远; 永存; 不灭; 不朽}
    \texx{Family life in the desire to gratify appetites and secure family perpetuity.}
}
realistic & ""ri@"lIsItIk & adj. & 现实的; 现实主义的\crr
sequence & "sikw@ns & noun. & 顺序; 次序; 序列\crr
vessel & "vEs@l & noun. & 器皿; 容器; 船; 血管\crr
deposit & dI"pAzIt & noun.\newline verb. & 存款; 押金; 沉淀\newline 储蓄; 堆积\crr
graduate & "gr\ae dZuet & noun.\newline verb. & 大学毕业生; 研究生\newline 毕业\crr
despite & dI"spaIt & preposition.\newline noun. & 尽管; 不管\newline 憎恨; 侮辱; 轻蔑\crr
\linetab{
    \exx\eng \ct heir music only earns my despite.
}
despise & dI"spaIz & verb. & 鄙视; 看不起\crr
pursuit & p\rse "sut & noun. & 追求; 追赶; 追捕\crr
\linetab{
    \exx\eng ericsson, and his colleagues have thus taken to studying expert performers in
    a wide range of pursuits, including soccer.
    \relative
    \tword{pursue}{p\rse"su}{追求; 追赶; 追逐(verb.)}
    \eng \ce veryone has the freedom to pursue their dreams.
}
formidable & "fOrmId@bl & adj. & 可怕的; 令人敬畏的; 难以对付的\crr
opponent & @"poUn@nt & noun. & 对手; 反对者; 敌手\crr
anecdote & "\ae nIkdoUt & noun. & 趣事; 轶事\crr
\linetab{
    \exx\eng i still remembered an anecdote of my childhood.
}
guarantee & ""g\ae r@n"ti & noun.\newline verb. & 确保; 保证\newline 保证; 保证书\crr
\linetab{
    \exx\eng i guarantee that he will come.
}
precious & "prES@s & adj. & 珍贵的; 宝贵的\crr
\linetab{
    \exx\eng \ct ime is so precious that you must make full use of it.
}
disgrace & dIs"gres & noun.\newline verb. & 耻辱; 丢脸; 不光彩\newline 使丢脸; 使蒙受耻辱\crr
\linetab{
    \tword{grace}{gres}{优雅}
}
immun & I"mjun & adj. & 免疫的; 有免疫力的; 不受影响的\crr
\linetab{
\tword{immunize}{"Imj@""naIz}{使免疫}
\tword{immunity}{I"mjunIti}{免疫力}
\tword{immunization}{""Imjun@zeS@n}{免疫}
}
immense & I"mEns & adj. & 极大的; 巨大的\crr
\linetab{
    \tphrase{enormous}{体积, 数量或程度上的巨大}
    \tphrase{immense}{空间的广阔}
    \tphrase{giant}{非正式用语, 指巨人般庞大的体积}
}
commodity & k@"mAd@ti & noun. & 商品; 货物; 日用品\crr
modernisation & ""mAd@n@"zes@n & noun. & 现代化\crr
triumph & "traI@mf & verb.\newline noun. & 战胜; 成功\newline 胜利; 凯旋\crr
\linetab{
    \exx\eng justice will triumph over evil.\newline
    \eng  It was a personal triumph over her old rival.
}
vice & vaIs & noun.\newline adj. & 恶习; 罪恶; 缺点; 缺陷\newline 副的; 替代的\crr
\linetab{
    \tword{versa}{"v@rs\rse}{反之亦然}
    \tphrase{vice versa}{反之亦然}
}
pressure & "prEs\rse & noun. & 压力; 压强; 压迫\crr
anonymous & @"nAn@m@s & adj. & 匿名的; 无名的; 不知名的\crr
engineering & ""endZI"nIrIn & noun. & 工程; 工程学\crr
flavor & "flev\rse & noun.\newline verb. & 风味; 滋味; 味道\newline 给...添加风味; 调味\crr
collar & "kAl\rse & noun.\newline verb. & 衣领; 领子\newline 抓住; 给...上领子\crr
enthusiasm & In"Tuzi\ae z@m & noun. & 热情; 热心; 热诚\crr
wherever & we\rse ev\rse & conjunction.\newline adv. & 处处; 在任何地方; 无论哪里\newline 究竟在哪里\crr
\linetab{
    \tword{whenever}{wEn"Ev\rse}{无论何时}
    \tword{whatever}{w@t"ev\rse}{无论什么}
    \tword{whoever}{fu"Ev\rse}{无论谁}
    \tword{however}{haU"ev\rse}{无论怎样}
}
whip & wIp & noun.\newline verb. & 鞭子\newline 鞭打; 抽打; 突然移动\crr
solemn & "sAl@m & adj. & 严肃的; 庄严的; 隆重的\crr
insight "In""saIt & noun. & 洞察力; 见识\crr
inspect & In"spEkt & verb. & 检查; 视察\crr
\linetab{
    \exx\eng customs officers inspect our baggage.\newline
    \eng the government sent him to inspect school.
}
mercury & "m\textrhookrevepsilon kj@ri & noun. & 水银; 汞; 精神; 元气; 水星(Mercury)\crr
renaissance & "ren@sAns & noun. & 文艺复兴; 再生\crr
\linetab{
    \exx\eng florence is the shrine of the renaissance.\newline
    \eng the news media is expriencing a renaissance.
}
bleak & blIk & adj. & 荒凉的; 阴冷的; 凄凉的; 无望的; 沮丧的\crr
pot & pAt & noun.\newline verb. & 壶; 锅; 罐; 瓢\newline 罐装; 栽入盆中; 射杀\crr
reproach & rI"proUtS & verb.\newline  noun. & 责备; 指责\newline 责备; 指责\crr
\linetab{
    \exx\eng don't reproach youself, it was not you fault.
    \relative
    \tword{rebuke}{r\ci "bjuk@}{责备; 责怪(verb. noun.)}
    \tword{reproachable}{r\ci "pro\cu t\cs @b@l}{应受责备的}
    \tword{blame}{blem}{责备; 责怪(verb. noun.)}
}
instantaneous & ""Inst@n"teni@s & adj. & 瞬间的\crr
limp & lImp & verb.\newline adj. & 跛行; 蹒跚\newline 无力的; 无生气的\crr
\linetab{
    \relative
    \tword{limb}{lIm}{肢体; 枝条}
    \tword{lamb}{l\ae m}{羊羔}
    \tword{lamp}{l\ae mp}{灯}
    \tword{lump}{l2mp}{小块; 肿块}
    \tword{lame}{lem}{跛足的}
    \tword{tame}{tem}{养训的}
}
ministry & "mInIstri & noun. & 部长; 公职; 牧师\crr
minority & maI"nOr@ti & noun. & 少数; 少数民族; 未成年\crr
resolute & "rEz@""lut & adj. & 坚决的; 毅然的; 有决心的\crr
\linetab{
    \relative
    \tword{resolve}{rI"zAlv}{决心; 决定; 使分解; 溶解(verb.) 决心(noun.)}
    \tword{resolution}{""rEz@"luS@n}{定义; 决议; 分辨率}
}
spin & spIn & verb.\newline noun. & 纺纱; 旋转; 疾驰\newline 旋转\crr
\linetab{
    \exx\eng to spin at full speed.\newline
    \eng to spin a coin.
}
toxic & "tAksIk & adj.\newline noun. & 有毒的; 中毒的\newline 毒药; 毒剂\crr
\linetab{
    \relative
    \tword{tonic}{"tAnIk}{滋补品(noun.) 滋补的(adj.)}
}
conquest & "kANkwest & noun. & 攻克; 征服\crr
erroneous & I"roUni@s & adj. & 错误的; 不正确的\crr
instruction & In"str2S@n & noun. & 指示; 教授; 指令; 说明\crr
instrument & "Instr@m@nt & noun. & 仪器; 乐器; 工具; 手段; 法律文件\crr
shampoo & s\ae m"pu & noun.\newline verb. & 洗发水; 洗发精; 洗发香波\newline 洗头发\crr
shed & sed & verb.\newline noun. & 流涌; 脱落; 抛弃; 摆脱\newline 棚屋; 小屋\crr
\linetab{
    \exx\eng He completely shed the older ways.\newline
    \eng \ci f you shed tears when you miss the sun, you will miss the starts.\newline
    \eng Some of the tree were already beginning to shed their leaves.
}
terrific & t@rIfIk & adj. & 极好的; 非常的; 惊人的\crr
aisle & aIl & noun. & 过道; 通道; 走廊\crr
eligible & "ElIdZ@b@l & adj. & 有资格的; 合格的; 合意的\crr
\linetab{
    \exx\eng you could be eligible for a scholarship.\newline
    \eng Make suitors called on eligible women under the watchful eyes of concerned adults.
}
\end{engvc}

\medskip
\begin{engvc}[18-8-31]
workout & "w\rse kaUt & noun. & 健身; 练习; 测验\crr
\linetab{
    \exx\eng he has made a workout plan and strictly followed it.\newline
    \eng the right metal workouts can significantly improve your basic cognitive function.
}
pronunciation & pr@""n2nsi"es@n & noun. & 发音; 读音\crr
municipality & mju""nIs@"p\ae lIti & noun. & 自治市; 市当局\crr
supper & "s2p\rse & noun. & 晚饭; 晚餐\crr
\linetab{
    \relative
    \tword{breakfast}{"brIkfest}{早餐}
    \tword{lunch}{l2ntS}{午餐}
    \tword{dinner}{"dIn\rse}{晚餐}
}
underrate & ""2nd\rse "ret & verb. & 低估; 看轻\crr
\linetab{
    \exx\eng we can't underrate population pressures.\newline
    \eng i underrate the difficulty of the task.
    \relative
    \tword{overrate}{""oUv\rse "ret}{高估}
    \tword{underestimate}{""2nd\rse "Est@met}{低估}
}
interviewee & ""Int\rse vju"i & noun. & 被面试者; 被采访者\crr
\linetab{
    \relative
    \tword{interview}{""Int\rse vju}{面试}
    \tword{interviewer}{"Int\rse vju\rse}{采访者; 面试时的考官}
}
upstart & "2pstArt & noun. & 自命不凡的新上任者; 狂妄自大的新手\crr
downstairs & daUn"stE\rse z & adv.\newline adj. & 住楼下; 在楼下\newline 楼下的; 底楼的\crr
\linetab{
    \relative
    \tword{upstairs}{""2p"stE\rse z}{在楼上(adv.) 楼上的(adj.) 楼上(noun.)}
}
submission & s@b"mIS@n & noun. & 屈从; 降服; 归顺; 提交\crr
\linetab{
    \exx\eng no enemy can frighten us into submission.\newline
    \eng they tried to strave him into submission.
    \relative
    \tword{commission}{k@"mIS@n}{委员会; 佣金(noun.) 委托; 委任(verb.)}
    \tword{remission}{rI"mIS@n}{减轻; 免除}
    \tword{demission}{dI"mIS@n}{辞职(noun.)}
}
valley & "v\ae li & noun. & 山谷; 溪谷; 流域\crr
compose & k@m"pouz & verb. & 创作; 组成; 使镇定\crr
\linetab{
    \relative
    \tword{composure}{k@m"poUZ\rse}{镇定; 沉着}
    \tword{composition}{"kAmp@"zISn}{作文; 成分}
}
discipline & "dIs@plIn & noun.\newline verb. & 纪律; 训练; 惩戒; 学科; 科目\newline 训练; 自制; 惩罚\crr
pyramid & "pIr@mId & noun.\newline verb. & 金字塔\newline 使...成塔尖形\crr
\linetab{
    \exx\eng population pyramid \chn 人口急速增加\newline
    \eng Pyramid sale is illegal in our country.\chn 传销在我国是犯法的.
}
banana & b@"n\ae n@ & noun. & 香蕉\crr
\linetab{
    \relative
    \tword{apple}{"\ae p@l}{苹果}
    \tword{pear}{pe@}{梨}
    \tword{apricot}{"\ae prIkAt}{杏}
    \tword{peach}{pItS}{桃子}
    \tword{grape}{grep}{葡萄}
    \tword{pineapple}{"paIn""\ae p@l}{菠萝}
    \tword{plum}{pl2m}{李子}
    \tword{watermelon}{"wOt\rse mel@n}{西瓜}
    \tword{orange}{"OrIndZ}{橙子}
    \tword{lemon}{"lEm@n}{柠檬}
    \tword{mango}{"m\ae ngoU}{芒果}
    \tword{strawberry}{"strOb@ri}{草莓}
}
burglar & "b\rse gl\rse & noun. & 窃贼; 夜盗\crr
handkerchief & "h\ae Nk\rse tSIf & noun. & 手帕; 方巾\crr
encyclopaedia & In""saIkl\rse"pIdI@ & noun. & 百科全书\crr
acrobat & "\ae kr@""b\ae t & noun. & 杂技演员; 立场观点善变的人\crr
suspect & s@"spEkt & verb. & 怀疑; 猜想(verb.) 嫌疑犯(noun.) 令人怀疑的; 不可信(adj.)\crr
\linetab{
    \relative
    \tword{suspiciously}{s@"spIS@sli}{怀疑地; 猜疑地}
    \tword{suspicious}{s@"spIS@s}{怀疑的; 猜疑的}
    \tword{suspicion}{s@"spIS@n}{怀疑; 猜疑(noun.)}
}
landlady & "l\ae nd""ledi & noun. & 女房东\crr
landlord & "l\ae ndlOrd & noun. & 房东; 地主\crr
eloquent & "El@kw@nt & adj. & 有口才的; 有说服力的\crr
\linetab{
    \exx\eng facts are more eloquent than words.
}
clerk & kl\rse k & noun. & 职员; 店员\crr
emit & i"mit & verb. & 发出; 发射\crr
signtseeing & "sait"sin & noun. & 观光; 游览\crr
thrust & tr2st & verb.\newline noun. & 刺; 戳\newline 推力; 刺; 戳\crr
\linetab{
    \exx\eng the whole thrust of the project was to make money.\newline
    \eng provide enough thrust to make the car move.
}
stamina & "st\ae m@n@ & noun. & 精力; 体力; 耐力\crr
\linetab{
    \exx\eng winter-born babies tend to have higher oxygen capcity, which increase soccer stamina.
    \relative
    \tword{vigor}{"v\ci g\rse}{精力}
    \tword{vigorous}{"v\ci g@r@s}{精力充沛的}
}
curriculum & k@"r\ci kj@l@m & noun. & 课程\crr
curricula & k@"rIkj@l@ & noun. & 课程(plural curriculuml)\crr
unpretentious & ""2npri"tens@s & adj. & 谦逊的; 不夸耀的\crr
\linetab{
    \exx\eng She had advocated his appointment in the Times, calls him
    an unpretentious musician with no air of the formidable conductor about.
}
shutter & "s2t\rse & noun. & 百叶窗; 快门\crr
feudal & "fjudl & adj. & 封建的; 封建制度的\crr
\linetab{
    \exx\eng he lost faith in feudal traditions.\newline
    \eng the feudal barons were cruel to the people.
}
plateau & pl\ae"tO & noun. & 高原; 高地; 稳定的状态\crr
\linetab{
    \relative
    \tword{basin}{"bes\ci n}{盆地}
    \tword{plain}{plen}{平原}
    \tword{desert}{"dez@rt}{沙漠}
}
trolly & "trOli & noun. & 手推车; 有轨电车\crr
chamber & "t\cs emb\rse & noun. & 房间; 大会议室; 议院\crr
\linetab{
    \exx\eng We are goning to make sure we are in the council chamber every time he speak.
}
deed & did & noun. & 行为; 事迹\crr
\linetab{
    \exx\eng your deed must anserw to your words.
}
glue & glu & noun.\newline verb. & 胶水; 胶合; 粘合\crr
bullet & "bulit & noun. & 子弹; 枪弹\crr
smuggle & "sm2g@l & verb. & 走私; 偷运\crr
\linetab{
    \exx\eng he smuggled his notes into the exam.\newline
    \eng she managed to smuggle in illegal drugs.
}
infectious & In"fEkS@s & adj. & 传染性的; 有感染力的\crr
\linetab{
    \relative
    \tword{infect}{In"fEkt}{传染; 感染}
    \tword{infection}{In"fEks@n}{感染; 传染; 影响}
}
morphine & "mOrfin & noun. & 吗啡\crr
\linetab{
    \relative
    \tword{marijuana}{""m\ae r@"wAn@}{大麻}
    \tword{cocaine}{koU"ken}{可卡因}
    \tword{caffeine}{k\ae "fIn}{咖啡因}
}
inflation & In"fles@n & noun. & 充气; 膨胀; 通货膨胀\crr
\linetab{
    \exx\eng inflation is caused by excessive money stock.
}
eclipse & IklIps & noun.\newline verb. & 日或月食; 丧失; 没落\newline 遮避; 使黯然失色\crr
slam & sl\ae m & verb. & 砰地关上; 猛动; 抨击\crr
\linetab{
    \exx\eng to slam into one's work.\newline
    \eng Local media slammed the plan to build a prison in the area.\newline
    \eng \ci  heard someone slam the door.
}
cloak & kloUk & noun.\newline verb. & 斗篷; 遮盖物; 掩护物\newline 遮掩; 隐匿\crr
\linetab{
    \exx\eng he cloaked his evil purpose under sweet words.
}
inhibit & In"hIbIt & verb. & 抑制; 阻止; 约束\crr
\linetab{
    \exx\eng \cd on't let fear inhibit you.\newline
    \eng You should inhibit wrong desires.
}
\end{engvc}

\medskip
\begin{engvc}
isomorphism & ""aIs@mOr"fIz@m & noun. & 同构\crr
equivalent & I"kwIv@l@nt & adj.\newline noun. & 相等的; 等价的\newline 等价物\crr
\end{engvc}

\medskip
\begin{engvc}
sole & sOl & noun.\newline adj. & 鞋底; 脚掌\newline 仅有的; 唯一的\crr
cardinality & ""kArd@"n\ae l@ti & noun. & 基数\crr
\linetab{
    \defn
    the number elements in a set or other grouping, as a property of that grouping.
}
transitive & "tr\ae nsItIv & adj.\newline noun. & 及物的; 过渡的; 可递的\newline 及物动词\crr
\linetab{
    \defn
    (of relation) such that if it applies between successive members of a
    sequence, it must also aplly between any two members taken in order.
    for instance, if a is larger than b, b is larger than c, then a is larger then c.
}
polynomial & ""pAlI"noUmIl & adj.\newline noun. & 多项式的\newline 多项式\crr
appropriate & @"proUpri@t & adj.\newline verb. & 适当的; 恰当的\newline 拔出; 盗用; 侵吞\crr
\linetab{
    \exx\eng the city will appropriate funds for new airport.
    \eng tell him the truth at an appropriate time.
}
approximate & @"prAksIm@t & verb.\newline adj. & 估计; 接近于\newline 近似的; 大约的\crr
appreciate & @"priSi""et & verb. & 欣赏; 感激; 赏识; 察觉; 意识到\crr
spectacular & spEk"t\ae kj@l\rse & adj. & 壮观的\crr
\linetab{
    \exx\eng a spectacular improvement over our exponential first attempt.
}
occasionally & @"keZn@li & adv. & 偶尔; 有时\crr
\linetab{
    \exx\eng occasionally i try to write poems.
}
specification & ""spEs@fI"kes@n & noun. & 规格; 规范\crr
heir & e\rse & noun. & 继承人; 后嗣\crr
vulnerable & "v2ln@r@b@l & adj. & 脆弱的; 易受伤的\crr
slipper & "slIp\rse & noun. & 拖鞋\crr
streamline & "strim"laIn & verb.\newline adj. & 使成流线型; 使合理化; 使简化\newline 流线型的\crr
\linetab{
    \defn
    design or provide with a form that presents very little resistance to a flow
    or air or water, increasing speed and ease of movement.
}
premium & "primi@m & noun.\newline adj. & 保险费; 奖金; 额外费用; 溢价\newline 高价的; 优质的\crr
conspiracy & k@n"spIr@si & noun. & 阴谋; 共谋\crr
\linetab{
    \relative
    \tword{conspire}{k@n"spaI\rse}{阴谋策划; 协力促成}
}
overpass & "oUv\rse p\ae s & noun. & 立交桥; 天桥\crr
sigh & saI & verb.\newline noun. & 叹气\newline 叹气\crr
palace & "p\ae lIs & noun. & 宫殿; 王宫\crr
escort & ""eskOrt & verb.\newline noun. & 护送; 护卫\newline 护送者; 护卫队\crr
\linetab{
    \exx\eng Because of the fantastic driving of Valtteri Bottas, 
    some people in reddit joke that Valtteri Bottas had to accept 
    esocrted by armed guard to leave Italy Monza Circuit.
}
resemble & rI"zEmb@l & verb. & 相似; 类似\crr
\linetab{
    \exx\eng his nails resemble the ivory keys of the spinet.\newline
    \eng he resembles his father in character.
}
reconstruct & ""rik@n"str2kt & verb. & 重建; 重构; 修复\crr
\linetab{
    i am fond to reconstruct some messy code.
}
messy & "mEsi & adj. & 杂乱的; 肮脏的\crr
sheer & SI\rse & adj.\newline verb. & 及轻薄的; 陡峭的; 纯粹的; 完全的;\newline 避开; 转向\crr
patash & "pSt\ae S & noun. & 钾碱; 碳酸钾\crr
manure & m@"nUr & noun.\newline verb. & 肥料\newline 给...施肥\crr
fertilizer & "f\rse t@laIz\rse & noun. & 肥料\crr
polish & "pAlIS & verb. & 擦亮; 磨光; 润色\crr
appraise & @"prez & verb. & 评价; 估价; 鉴定\crr
enrol & \ci n"ro\cu l & verb. & 登记; 注册; 招收; 录取\crr
kidnap & "k\ci d""n\ae p & verb.\newline noun. & 绑架; 劫持; 诱拐\newline 绑架罪\crr
\linetab{
    \exx\eng He was charged with the kidnap of a woman.
    \relative
    \tword{ransom}{"r\ae ns@m}{赎金(noun.) 赎回(verb.)}
    \tword{blackmail}{"bl\ae k""mel}{勒索; 敲诈(noun. verb.)}
    \tword{kidney}{"k\ci dni}{肾; 肾脏; 腰子; 脾气}
}
enviable & "\ce nvi@b@l & adj. & 令人羡慕的; 引起嫉妒的\crr
\linetab{
    \relative
    \tword{envy}{"\ce nvi}{嫉妒;羡慕(noun. verb.)}
}
ornate & \co r"net & adj. & 装饰华丽的; 华美的\crr
\linetab{
    \relative
    \tword{ornament}{\co r"n@m@nt}{装饰品}
    \tword{decorate}{d\ce "k@""re t}{装饰; 装修}
    \tword{decoration}{d\ce "k@""re\cs @n}{装饰品}
    \tword{decorative}{"dek@""ret\ci v}{装饰性的}
}
auction & "\co k\cs n & noun.\newline verb. & 拍卖\crr
ward & w\co rd & noun.\newline verb. & 病房; 选区\newline 监护; 守护; 挡住\crr
moartality & m\co r"t\ae l@ti & noun. & 死亡人数; 死亡率; 必死性\crr
\linetab{
    \exx\eng \ct hese deaths are reminders of our own mortality.
}
summit & "s2m\ci t & noun.\newline adj. & 顶峰; 顶点; 顶尖\newline 最高级的; 政府首脑的\crr
jolly & "d\cz \ca li & adj.\newline verb.\newline adv. & 愉快的; 快乐的\newline 开玩笑; 作乐\newline 非常; 很\crr
beware & b\ci "wer & verb. & 注意; 当心\crr
\linetab{
    \exx\eng \ct hey should beware of making hasty decisions.
}
stall & st\co l & noun.\newline verb. & 小隔间; 摊位; 牲畜棚\newline 停顿; 使熄火; 故意拖延\crr
\linetab{
    \exx\eng Never buy food from a market stall.\newline
    \eng Don't panic, I can stall him off.
}
confinement & k@n"fa\ci nm@nt & noun. & 拘禁; 限制; 分娩\crr
inedible & \ci n"\ce d@b@l & adj. & 不能吃的; 不宜食用的\crr
\linetab{
    \exx\eng \ci t'll be appropriate for you to make a passing remark about the indeible canteen food 
    of the chairman's notorious bad taste in.
}
\end{engvc}

\medskip
\begin{engvc}
provincialism & pr@"v\ci n\cs @""l\ci z@m & noun. & 地方主义； 方言； 偏狭性\crr
\linetab{
    \relative
    \tword{province}{"pr\ca v\ci ns}{省}
    \tword{provincial}{pr@"v\ci n\cs @l}{地方的; 狭隘的}
}
resent & r\ci "z\ce nt & verb. & 怨恨; 憎恨\crr
\linetab{
    \relative
    \tword{resentment}{r\ci "z\ce ntm@nt}{怨恨; 愤恨}
    \texx{The mere presence of a grape in the other chamber was enought to %
    induce resentment in a female capuchin.}
    \tword{resentful}{r\ci "z\ce ntf@l}{愤慨的}
}
rubble & "r2b@l & noun. & 碎石; 瓦砾\crr
cosmic & "k\ca zm\ci k & adj. & 宇宙的; 极广阔的\crr
\linetab{
    \relative
    \tword{comic}{"k\ca m\ci k}{漫画}
    \tword{cosmos}{"k\ca zm\co s}{宇宙}
    \tword{cosmetic}{k\ca z"met\ci k}{化妆品}
}
molecule & "m\ca l\ci kjul & noun. & 分子\crr
\linetab{
    \relative
    \tword{atom}{@"t@m}{原子}
    \tword{proton}{pr\co "t@n}{质子}
    \tword{molecular}{m@"lEkj@l\rse}{分子的; 分子构成的}
    \texx{Avoid new restrictions on research that involves the cloning human DNA or cells - routine in molecular biology.}
}
\end{engvc}

\medskip
\begin{engvc}
tactics & "t\ae kt\ci ks & noun. & 策略; 战术\crr
\linetab{
\relative
\tword{tactic}{"t\ae kt\ci k}{按顺序的; 依次排列的}
\tword{tactical}{"t\ae kt\ci k@l}{战术的; 策略的}
\tword{tactician}{t\ae k"t\ci \cs @n}{战术家}
}
confidential & k\ca n"f@d\ce n\cs @l & adj. & 机密的; 秘密的; 视为心腹的\crr
friction & "fr\ci k\cs @n & noun. & 摩擦; 不和; 争执\crr
\linetab{
    \relative
    \tword{faction}{"f\ae k\cs @n}{集团; 党派}
    \tword{fiction}{"f\ci k\cs @n}{小说}
    \tword{fabrication}{""f\ae br@"ke\cs @n}{制备; 加工; 虚构}
}
obsolete & ""\ca bs@"lit & adj.\newline verb. & 过时的; 废弃的; 淘汰的\newline 抛弃\crr
\linetab{
    \defn 
    {\tt adj.\qquad} no longer produced or used; out of date.\newline
    {\tt verb.\qquad}\vtop{cause (a product or a idea) to be or become obsolete by replacing it with something new.}
}
retrospect & "r\ce tr@""sp\ce kt & verb.\newline noun. & 回顾; 回想\crr
\linetab{
    \exx\eng happiness in retrospect\newline
    \eng to retrospect the development\newline
    \eng \ci n retrospect, \ci  think that \ci  was wrong.
}
climate & "kla\ci m\ci t & noun. & 气候; 风气; 一般趋势\crr
rebel & r\ci "b\ce l & verb.\newline noun. & 反抗; 造反\newline 叛逆者\crr
\linetab{
    \tword{rebellious}{r\ci "b\ce lj@s}{叛逆的}
    \tword{rebellion}{r\ci "b\ce lj@n}{反叛}
}
flexibility & ""fl\ce s@"b\ci l@ti & noun. & 弹性; 灵活性; 柔韧性\crr
\linetab{
    \exx\eng \cd istance learning has an advantage of flexibility.
}
magistrate & "m\ae d\cz \ci ""stret & noun. & 地方法官; 治安官; 行政官\crr
\linetab{
    \relative
    \tword{magister}{m@"d\cz \ci st@}{教师; 总督}
}
thirst & \ct \textrhookrevepsilon st & noun. & 口渴; 渴求\crr
\linetab{
    \relative
    \tword{thirsty}{\ct \textrhookrevepsilon sti}{口渴的; 渴望的}
}
reconcile & "r\ce k@nsa\ci l & verb. & 使和解; 使和好; 调和\crr
\linetab{
    \exx\eng He refusedc to reconcile himself with his brother.\newline
    \eng Must they reconcile themselfves to their fates?\newline 
    \eng \ca n attempt to reconcile the need for industrial development with concern 
    for the environment.
}
cattle & "k\ae tl & noun. & 牛; 家畜\crr
pregnant & "pr\ce gi@nt & adj. & 怀孕的; 重要的; 含有深意的; 有创造力的\crr
\linetab{
    \exx\eng 
    \tphrase{pregnant artists}{有创造力的艺术家}
    \eng\phrase{a pregnant decision}{成果显著的决定}
    \eng \ct here was a long, pregnant silence...
}
signtseeing & "sa\ci t""si\cn  & noun. & 观光; 游览\crr
\linetab{
    \exx\eng 
    do some sightseeing.\newline
    \eng go signtseeing.\newline
}
robe & ro\cu b &noun.\newline verb. & 长袍; 使穿上长袍\crr
\linetab{
    \relative
    \twocol{
    \tword{cape}{kep}{披风; 海角}
    \tword{veil}{vel}{面纱; 覆盖; 遮挡; 隐匿}
    \tword{gown}{gaUn}{长袍; 礼服; 长外衣}
    }{%
    \tword{toga}{"toUg@}{宽长袍; 参议院的职位}
    \tword{cloak}{klOuk}{斗篷; 披风; 遮挡}
    }
}
appreciative & @"pri\cs @t\ci v & adj. & 感激的; 欣赏的\crr
\linetab{
    \relative
    \tword{appreciate}{@"pri\cs i""et}{欣赏}
}
overcharge & ""o\cu v\rse "t\cs \ca d\cz  & verb.\newline noun. & 对...要价过高; 装填过量\newline 要价过高; 装填过量\crr
arrestee & \relax\rse r\ce s"ti & noun. & 被捕者\crr
\linetab{
    \exx\eng
    Breaking: \ca  man arrest in Minneapolis due to sexual assualt, according 
    reliable source, this arrestee is LiuQiangdong.
}
reckless & "r\ce kl\ci s & adj. & 鲁莽的; 不计后果的\crr
\linetab{
    \relative
    \tword{reck}{rek}{顾忌}
}
revival & r\ci "va\ci v@l & noun. & 复兴; 复苏; 再生\crr
\linetab{
    \relative
    \tword{revive}{r\ci "va\ci v}{复活}
    \tword{survival}{s\rse "va\ci v@l}{幸存}
    \tword{survive}{s\rse"va\ci v}{幸存}
    \tword{revitalization}{""ri""va\ci t@la\ci "ze\cs @n}{复苏; 复兴}
    \tword{revitalise}{ri"va\ci t@la\ci z}{使复兴}
    \tword{revitalize}{ri"va\ci t@la\ci z}{使复兴}
}
gratitude & "gr\ae t\ci tud & noun. & 感激之情; 感谢\crr
\linetab{
    \relative
    \tword{grateful}{"gre t@f@l}{感激的}
    \tword{graceful}{"gre sf@l}{优雅的}
    \tword{attitude}{"\ae t\ci tud}{态度}
    \tword{altitude}{"\ae ltitud}{海拔; 高度}
    \tword{latitude}{"l\ae t\ci tud}{纬度; 行动或言论的程度}
    \eng \ci t gives freedom of thought and expression the widest possible latitude.\newline
    \tword{fortitude}{"f\co rt\ci tud}{刚毅; 坚忍}
}
symposium & s\ci m"po\cu zi@m & noun. & 研讨会; 专题讨论会\crr
\linetab{
    \exx\eng \ct hen it sponsors lots of symposiums and a credibility project
    dedicated to wondering why customers are annoyed and fleeing in large numbers.
}
flee & fli & verb. & 逃跑; 逃离\crr
nonconformist & ""n\ca nk@n"f\co rm\ci st & adj.\newline noun. & 不信奉国教的; 不墨守成规的\newline 不墨守成规者; 新教徒\crr
plunge & pl2nd\cz  & verb. \newline noun. & 投入; 跳进; 猛跌\newline 投入; 跳进; 骤降\crr
\linetab{
    \exx\eng take the plunge\chn 冒险尝试; 果断行事; 投身于\newline
    \eng Prices started a downward plunge.\newline 
    \eng \ct he whale took a plunge into the deep water.
}
profound & pr@"fo\cu nd & adj.\newline noun. & 深刻的; 高深的; 深切的\newline 海洋\crr
\linetab{
    \defn
    {\tt adj.\quad}\vtop{
        1. (of state, quality, or emotion) very great or intense.\newline
        2. (of person, or statement) having show great knowledge or insight.}
    {\tt noun.\quad}\vtop{
        \ct he vast depth of the ocean or of the mind.
    }
}
reluctant & r\ci "l2kt@nt & adj. & 不情愿的; 勉强的\crr
\linetab{
    \exx\eng \cd espite these factors, many social scientists seem 
    reluctant to tackle such problems.
}
treason & "triz@n & noun. & 叛国罪; 卖国\crr
\linetab{
    \relative
    \tword{traitor}{"tret\rse}{叛徒; 背叛者; 卖国贼}
    \tword{betray}{b\ci "tre}{背叛}
    \exx\eng He was executed for treason.\newline
    \eng \ci  hate those person who always take treason toward their friends.
}
tremendous & tr\ci "m\ce nd@s & adj. & 巨大的; 极大的\crr
hall & h\co l & noun. & 大厅; 礼堂; 门厅\crr
dubious & "dubi@s & adj. & 可疑的; 怀疑的; 拿不准的\crr
\linetab{
    \exx\eng \ci  feel dubious about what to do next.\newline
    \eng He identity was dubious.\newline
    \eng Navy has the dubious honour of being the first athlete to be banned in this way.
}
strip & str\ci p & verb.\newline noun. & 剥去; 剥夺; 脱衣\newline 长条; 条状\crr
\linetab{
    \exx\eng \ci  strip myself for a shower.\newline
    \eng He shouldn't strip his daughter of the right to be educated.
}
naked & "nekid & adj. & 裸体的; 裸漏的\crr
balllon & b@"lun & verb.\newline noun. & 气球; 热气球; 玩具气球\newline 乘热气球飞行; 膨胀\crr
magnet & "m\ae gn\ci t & noun. & 磁体; 磁铁\crr
sacred & "sekr\ci d & adj. & 宗教的; 神圣的; 庄严的\crr
umbrella & 2m"br\ce l@ & noun. & 伞; 雨伞\crr
quarrel & "kw\co r@l & verb.\newline noun. & 争吵; 吵架\newline 争吵; 口角; 拌嘴\crr
subtitle & "s2b""ta\ci tl & noun.\newline verb. & 副标题; 说明或对白的字幕\newline 给...加副标题; 给...加字幕\crr
pupil & "pjup@l & noun. & 小学生; 瞳孔\crr
mutton & "m2tn & noun. & 羊肉\crr
terrain & t@"ren & noun. & 地形; 地势; 地带\crr
\linetab{
    \exx\eng \ct ypically, the survey and sample large areas of terrain to determine 
    where excavatioin will yield useful information.\newline
    \eng \ct he terrain changed from forest to desert.
}
excavate & "\ce ksk@"vet & verb. & 挖掘; 发掘\crr
accordance & @"k\co rdns & noun. & 一致; 符合\crr
\linetab{
    \relative
    \tphrase{in accordance with}{与...一致}
}
bankrupt & "b\ae \cn k""r2pt & adj.\newline noun. & 破产的\newline 破产; 破产者\crr
\linetab{
    \exx\eng He seemed to be bankrupt of hope and confidence.\newline
    \eng \ct he company went bankrupt and he lost his job.
}
barren & "b\ae r@n & adj. & 贫瘠的; 不孕的; 无价值的\crr
\linetab{
    \exx\eng He prayed that his barren wife would one day have a child.
}
cape & kep & 披风; 斗篷; 海角\crr
genuine & "d\cz \ce njun & adj. & 真正的; 真诚的\crr
\linetab{
    \exx\eng \ca ll genuine knowledge originates in direct experience.
    \relative
    \tword{ingenuous}{\ci n"d\cz \ce nju@s}{坦率的; 天真无邪的; 朴实的}
    \tword{unsophisticated}{""2ns@f\ci s"t\ci ""k2t\ci d}{朴实的; 不复杂的; 简单的}
    \tword{ingenious}{\ci n"d\cz inj@s}{精巧的; 聪明的; 设计独特的}
    \tword{generic}{d\cz @"n\ce r\ci k}{通用的; 普通的}
}
vanity & "v\ae n\ci ti & noun. & 虚荣; 自负\crr
utterance & "2t@r@ns & noun. & 言辞; 言语; 言论\crr
\linetab{
    \exx\eng Her unusual utterance revealed her emotions.\newline
    \eng \ci  have a native utterance in \ce nglish.\newline
    \eng He gave utterance to his thoughts.
}
vegetation & ""v\ce d\cz \ci "te\cs @n & noun. & 草木; 植物\crr
\linetab{
    \relative
    \tword{vegetarian}{""v\ce d\cz @ter\ci @n}{素食主义者}
    \tword{vegetable}{"v\ce d\cz t@b@l}{蔬菜}
    \tword{botany}{"b\ca t@ni}{植物}
    \tword{botanic}{b@"t\ae n\ci k}{植物的; 植物学的}
}
sophomore & "s\ca f@m\co r & noun. & 大学二年级学生\crr
boil & b\co \ci l & verb.\newline noun. & 沸腾; 煮; 煮沸\newline 煮沸; 沸点; 疥疮\crr
recipient & r\ci "s\ci pi@nt & noun.\newline adj. & 接收者; 容纳者; 容器\newline 容易接受的; 感受性强的\crr
\linetab{
    \relative
    \tword{receive}{r\ci "siv}{接受}
    \tword{receipt}{r\ci "sit}{收据}
    \tword{reception}{r\ci "s\ce p\cs @n}{接受(noun.)}
    \tword{receptionist}{r\ci "sa\ci p\cs @n\ci st}{接待员}
}
veil & vel & noun.\newline verb. & 面纱; 遮盖物\crr
\linetab{
    \exx\eng veil the face.\newline
    \eng \ce verything was wrapped in a veil of evening.\newline
    \eng \ci nside information is helping federal agents lift a veil of corporate secrecy.
}
corporate & "k\co rp@r@t & adj. & 法人的; 全体的; 公司的; 团体的\crr
versatile & "v\rse s@tl & adj. & 多才多艺的; 多方面的\crr
pearl & p\rse l & noun. & 珍珠\crr
harbour & "h\ca rb\rse & nouon.\newline verb. & 海港\newline 庇护; 窝藏\crr
\linetab{
    \exx\eng \ci t's an offence to harbour the criminals.\newline
    \eng When did you enter the harbour.
}
harden & "h\ca rdn & verb. & 使坚强; 使坚硬\crr
\linetab{
    \exx\eng Hardship can harden you will.\newline
    \eng \ct hey harden clay by putting it in a fire.
}
tumour & "tu:m\rse & noun. & 肿瘤; 肿块\crr
lane & len & noun. & 小路; 小港; 航道; 车道; 航线\crr
sculpture & "sk2lpt\cs \rse & noun.\newline verb. & 雕刻; 雕刻品\newline 雕塑; 刻蚀\crr
seam & sim & noun.\newline verb. & 接缝; 缝合处\newline 缝合; 有裂纹\crr
pulse & p2ls & noun.\newline verb. & 脉冲; 脉搏; 脉动\newline 脉动; 搏动; 跳动\crr
adolescent & ""\ae d@"lesnt & noun.\newline adj. & 青少年\newline 青少年的; 青春期的\crr
ego & "\ci go\cu  & noun. & 自我; 自负; 自尊心\crr
fatigue & f@"tig & noun. & 疲乏; 劳累\crr
vanish & "v\ae n\ci \cs  & verb. & 销声匿迹; 突然消失\crr
harvest & "h\ca rv\ci st & noun.\newline verb. & 收获; 收成\newline 收割; 收获\crr
\linetab{
    \exx\eng In his new career as a restaurateur he has blossomed and harvested many awards.
}
hay & he & noun. & 干草\crr
instill & \ci n"st\ci l & verb. & 逐步渗透; 逐渐灌输\crr
\linetab{
    \exx\eng Parents instill the ideas into their children.
}
penetrate & "p\ce n@tret & verb. & 渗透; 看穿; 洞察\crr
\linetab{
    \exx\eng We should penetrate the appearance to see the essence.\newline
    \eng \ct he sun's radiation penetrate the skin.\newline
    \eng Computers nowadays deeply penetrate into our daily life
    and we can not do without them even for a minute.
}
mold & mold & noun.\newline verb. & 摸具; 霉菌\newline 制模; 塑造; 发霉\crr
\linetab{
    \exx\eng \ct he write's experiment show that downlifting helps her mold philosophy of life.
}
lyric & "l\ci r\ci k & noun.\newline adj. & 抒情诗; 歌词\newline 抒情的; 吟唱的\crr
\end{engvc}

\medskip
\begin{engvc}[18-9-5]
alloy & "\ae l""\co \ci & noun.\newline verb. & 合金； 把...铸成合金\crr
\linetab{
    \exx\eng Bronze is an alloy of copper and tin.\newline
    \eng \ci dealism that was alloy with political skill.
}
cast & k\ae st & verb.\newline noun. & 投掷; 铸造\newline 全体演员\crr
liberate & "l\ci b@""ret & verb. & 解放; 释放\crr
\linetab{
    \relative
    \tword{liberty}{"l\ci b@ti}{自由}
    \tword{literary}{"l\ci t@reri}{文学的}
    \tword{literature}{"l\ci t@r@""t\cs \rse}{文学}
    \tword{library}{"la\ci breri}{图书馆}
}
tort & t\co rt & noun. & 侵权行为(不构成刑事犯罪但可以引起民事诉讼)\crr
\linetab{
    \relative
    \tword{torture}{"t\co :t\cs e}{拷问}
    \tword{retort}{r\ci "t\co :rt}{反驳}
    \tword{distort}{d\ci "st\co :rt}{歪曲}
    \tword{contort}{k@n"t\co :rt}{歪曲}
}
version & "v\rse \cz n & noun. & 版本; 样式\crr
briefcase & "brif""kes & noun. & 公文包; 手提包\crr
tough & t2f & adj. & 强硬的; 艰苦的; 严厉的\crr
\linetab{
    \exx\eng \ct he las is tough on offenders.\newline
    \eng Condiitons are rather tough here.
}
commission & k@"m\ci \cs @n & noun.\newline verb. & 委员会; 佣金\newline 委托; 委任\crr
\linetab{
    \exx\eng Plublishers commission her to translate the book.\newline
    \eng He earned a lot in commission.
}
motel & mo\cu "tel & noun. & 汽车旅馆\crr
division & d\ci "v\ci \cz @n & noun. & 划分; 除法; 部门\crr
\linetab{
    \exx\eng \cs ocial divisions will break down if people get to know each other.\newline
    \eng \ca ddicion and division are forms of computation.
}
association & @""s\co s\ci "e\cs n & noun. & 协会; 联系; 联想\crr
\linetab{
    \tword{associate}{@""s\co s\ci "et}{\vtop{verb.\quad 结交; 结伙; 联合; 联想\newline noun.\quad 交往; 结交; 合作人; 同事\newline \ adj.\quad 副的}}
    \texx{I filed charges against my associate.}
    \tword{associated}{@""s\co s\ci et\ci d}{关联的; 联合的}
    \tword{associative}{@""s\co \cs j@t\ci v}{联想的; 联合的; 组合的}
    \tword{associable}{@""s\co \cs j@bl}{可联想的; 协会的}
    \tword{associationism}{@""s\co si"e\cs @n\ci s@m}{联想心理学; 观念联合论}
    \tword{associability}{@s\co \cs @"b\ci l\ci t\ci }{可联想性; 交感性}
}
exclude & \ci K"sklud & verb. & 拒绝; 排斥; 排除\crr
include & \ci n"klud & verb. & 包括; 包含\crr
consume & k@n"sum & verb. & 消耗; 消费; 毁掉; 使沉溺; 使沉迷; 使充满\crr
\linetab{
    \exx\eng \cs he was consume with curiosity.\newline
    \eng to consume away a building.
}
consult & k@n"s2lt & verb. & 请教; 咨询; 商量; 顾及\crr
equator & \ci "kwet\rse & noun. & 赤道\crr
\linetab{
    \relative
    \tword{tropical}{"tr\ca p\ci kl}{热带的}
    \tword{formulation}{""f\co rmj@"le\cs @n}{规划; 策划(noun.)}
}
postage & "po\cu st\ci d\cz  & noun. & 邮费; 邮资\crr
extensive & \ci k"st\ce ns\ci v & adj. & 广大的; 广阔的; 广泛的; 大量的\crr
\linetab{
    \relative
    \tword{extend}{\ci k"st\ce nd}{扩展}
    \tword{extension}{\ci k"st\ce n\cs @n}{延申; 扩展}
    \tword{extent}{\ci k"st\ce nt}{程度; 范围}
    \tword{extant}{"\ce kst\ae nt}{现存的}
}
stale & stel & adj. & 不新鲜的; 陈腐的\crr
\linetab{
    \exx\eng Flowing water does not get stale.
}
instrument & "\ci nstr@m@nt & noun. & 仪器; 乐器; 工具; 手段; 法律文件\crr
\linetab{
    \exx\eng Language is an instrument for communication.\newline
    \eng \ci mposing restrictions on the basis of nationality is the bluntest of instrument.
    \chn \word{bluntest}{bl2n"test}{直言不讳的; 生硬的}
}
cigarette & "s\ci g@r\ce t & noun. & 香烟\crr
\linetab{
    \relative
    \tword{cigar}{s\ci "g\ca r}{雪茄烟}
    \tword{tobacco}{t@"b\ae ko\cu }{烟草}
}
commitment & k@"m\ci tm@nt & noun. & 承诺; 投入\crr
\linetab{
    \relative
    \tword{commit}{k@"m\ci t}{犯罪; 承诺; 委托; 收押}
    \tword{committee}{k@"m\ci ti}{委员会}
}
smash & sm\ae \cs  & verb.\newline noun. & 粉碎; 重撞\newline 撞碎; 破碎的哗啦声\crr
\linetab{
    \relative
    \eng \ci t's time to smash the stereotype\newline
    \tword{stereotype}{"st\ce ri@""ta\ci p}{\vtop{陈规旧习; 固定的形式; 铅板(noun.)\newline 使成陈规; 把...浇铸成铅板; 使固定; (verb.)}}
}
upfront & "2p"fr2nt & adj.\newline adv. & 坦率的; 预付的\newline 在前面\crr
\linetab{
    \exx\eng upfront work search scheme\chn 预先求职计划\newline
    \eng \cs he is upgront with her views.
}
jealous & "d\cz \ce l@s & adj. & 嫉妒的; 妒忌的\crr
\linetab{
    \exx\eng \cs he is jealous of our success.\newline
    \eng be jealous of one's reputation.
}
observe & @b"z\rse v & verb. & 观察; 注意到; 遵守; 庆祝\crr
\linetab{
    \relative
    \tword{reserve}{r\ci "z\rse v}{\vtop{储备; 保留; 预约(verb. noun.) 保护区; 替补队员(noun.)\newline 保留的; 预备的(adj.)}}
    \tword{deserve}{d\ci "z\rse v}{值得; 应受; 应受的报答; 应受的惩罚}
    \tword{preserve}{pr\ci "z\rse v}{保存; 保鲜; 保持; 反腐处理(verb.) 蜜饯; 防护用品; 独占的事物(noun.)}
    \exx\eng \ca ll citizens should observe the traffic rules.\newline
    \eng Facts about the world are waiting to be observed and collected 
    by objective researchers who use the scientific method.
}
nightmare & "na\ci tm\ae r & noun.\newline adj. & 噩梦; 可怕的事情\newline 噩梦的; 可怕的\crr
prescription & pr\ci "skr\ci p\cs @n & noun. & 处方; 法规; 指示\crr
\linetab{
    \exx\eng \ca  doctor made a special prescription for illiterate patient.\newline
    \tword{illiterate}{\ci "l\ci t@r\ci t}{文盲(noun.) 文盲的; 目不识丁的(adj.)}
}
warrant & "w\co r@nt & noun.\newline verb. & 授权证; 许可证; 依据; 正当理由\newline 保证; 担保; 授权; 批准\crr
composure & k@m"p\ca \cz \rse & noun. & 镇静; 镇定; 沉着\crr
\linetab{
    \exx\eng Composure is a state of mind made possible by the
    structuring of one's relation to one's environment.
    \chn 宁静是一种心态, 通过构建人与环境的联系来实现.\newline
    \eng \ci n so doing they give composure to a segment of the inarticulate environment in 
    which they take their stand.\newline
    \tword{inarticulate}{""\ci n\ca r"t\ci kj@l@t}{不善言辞的; 笨口拙舌的}
}
recur & r\ci "k\rse & verb. & 重现; 再发生\crr
resistant & r\ci "z\ci st@nt & adj. & 抵抗的; 有抵抗力的\crr
\linetab{
    \relative
    \tword{resist}{rI"zIst}{抵制; 抵抗}
    \tword{desist}{dI"sIst}{停止}
    \tword{subsist}{s@b"sIst}{生存; 维持生活}
    \exx\eng \ci f people just two degree removed from the initial influential prove
    resistant the cascade of change won't propagate very far.
}
cascade & k\ae "sked & noun.\newline verb. & 瀑布; 串联; 倾泻\newline 流注; 大量落下\crr
propagate & "pr\ca p@get & verb. & 繁衍; 增殖; 扩散\crr
\linetab{
    \exx\eng The cascade of change won't propagate very far or affect many people.
}
methodology & ""m\ce \ct @"d\ca l@d\cz i & noun. & 方法学; 一套方法\crr
frighten & "fra\ci tn & verb. & 使惊吓; 使惊恐\crr
reinforce & ""ri\ci n"f\co rs & verb. & 增强; 增援; 加强; 加固\crr
\linetab{
    \exx\eng We must reinforce the troops at the front.
}
glitter & "gl\ci t\rse & noun.\newline verb. & 闪耀; 闪烁; 小发光物\newline 闪耀; 闪亮; 流露\crr
\linetab{
    \exx\eng \ct he ceiling of cathedral glittered with gold.
}
paradox & p\ae r@"d\ca ks & noun. & 悖论; 自相矛盾的论点\crr
farewell & ""fe\rse"wel & noun. & 再会; 别了\crr
divert & da\ci "v\textrhookrevepsilon t & verb. & 转移; 分心\crr
\linetab{
    \exx\eng \ct he war divert people's attention away from the economic situation.\newline
    \eng \ct he government is trying to divert more public funds from west to east.\newline
    \eng For the government, the war was welcome a diversion from country's economic problems.
    \relative
    \tword{diversion}{da\ci "v\textrhookrevepsilon \cz n}{转移; 改道; 分散注意力; 消遣(noun.)}
    \tword{diverse}{da\ci "v\textrhookrevepsilon s}{不同的; 相异的}
    \tword{diverge}{da\ci "v\textrhookrevepsilon d\cz }{分歧; 分开; 叉开; 发散}
    \tword{diver}{"da\ci v\rse}{潜水员}
}
analytical & ""\ae n@"l\ci t\ci kl & adj. & 分析的; 解析的\crr
unionism & "jun\ci @n\ci z@m & noun. & 联合主义; 工会主义; 工联主义\crr
\linetab{
    \exx\eng \ct he strike is the ultima ratio of \ct rade \cu nionism.
}
brandy & "br\ae ndi & noun. & 白兰地酒\crr
aspiration &: ""\ae sp@"re\cs @n & noun. & 渴望; 抱负; 志向; 吸气; 送气音\crr
\linetab{
    \exx\eng \cs he had an aspiration to be an actress.\newline
    \eng \co ld people still cherish high aspiration.
    \relative
    \tword{aspire}{@"spa\ci r}{渴望; 立志; 追求(verb.)}
    \tword{inspire}{\ci n"spa\ci r}{激励; 赋予灵感; 启迪; 吸气}
    \tword{inspiration}{""\ci nsp\ci "re\cs @n}{灵感; 启发灵感的人}
}
metropolitan & ""m\ce tr@"p\ca l@tn & adj. & 主要都市的; 大城市的\crr
compassion & k@m"p\ae \cs @n & noun. & 同情; 怜悯\crr
\linetab{
    \exx\eng He teaches us have compassion on the poor.
}
evoke & \ci "vo\cu k & verb. & 唤起; 引起\crr
\linetab{
    \exx\eng \ct he songs evoke my old memories.
}
inhabitant & \ci n"h\ae b\ci t@nt & noun. & 居住者; 居民\crr
similarity & ""s\ci m@"l\ae r@ti & noun. & 相似点; 相像性\crr
essay & "\ce se & noun.\newline verb. & 散文; 文章; 企图; 尝试\newline 企图; 尝试\crr
\linetab{
    \relative
    \tword{article}{"\ca rt\ci cl}{文章; 条款}
    \tword{thesis}{"\ct is\ci s}{论文}
    \tword{masterpieces}{"m\ae st@rpis}{著作; 名著; 杰出的事}
    \exx\eng He essayed to speak but was told to be quiet by the chairman.
}
headache & "h\ce d""ek & noun. & 头痛; 令人头痛的事\crr
orchestrate & "\co rk\ci stret & verb. & 策划; 精心安排; 改编为管弦乐\crr
\linetab{
    \exx\eng \ct oyota Motor alleviated some of the damage from its recall crisis with
    a relative quick and well-orchestrated social-media.
}
dioxide & da\ci "aksa\ci d & noun. & 二氧化物\crr
appraisal & @"prez@l & noun. & 鉴定; 评价\crr
\linetab{
    \relative
    \tphrase{asset appraisal}{资产评估}
    \tphrase{performance appraisal}{绩效评估}
}
parasite & "p\ae r@""sa\ci t & noun. & 寄生虫; 寄生生物; 依赖他人过活者\crr
\linetab{
    \exx\eng \ct he kind of people live as a parasite on society.
}
robust & ro\cu "b2st & adj. & 强健的; 强壮的; 结实的\crr
\linetab{
    \exx\eng Yet the \cu \cs  economy has created jobs at a steady, robust rate as 
    the workforce has grown, and unemployment usually has been low.\newline
    \tword{workforce}{"w\rse kf\co rs}{全体员工; 劳动人口}
}
glance & gl\ae ns & verb.\newline noun. & 一瞥; 随便提到; 掠过\newline 浏览; 闪光\crr
neither & "nid\rse & adj.\newline pronoun.\newline adv.\newline conjunction. & 两者都不的\newline 两者都不\newline 两者都不\newline 也不\crr
\linetab{
    \defn
    {\bf adverb.} \quad\vtop{\hsize=.82\hsize
        1. used before first of two (occasionally more) alternatives that are specified 
        (the other are introduced by "nor") to indicate that they are each untrue or 
        each do not happend.\newline
        2. used to introduce a further negative statement.
    }
    \exx
    \eng \ci 'm neither a liberal(自由主义) nor a conservative(保守主义).\newline
    \eng \ct hey produced two reports, neither of which contained any useful suggeston.\newline
    \eng He didn't remember and neither did \ci .
}
risky & "r\ci ski & adj. & 危险的; 冒风险的\crr
\linetab{
    \exx\eng \ci t's risky to explore an active volcano.\quad \word{volcano}{v\ca l"keno\cu }{火山}
}
prick & pr\ci k & verb.\newline noun. & 刺; 戳\newline 扎; 刺; 锥\crr
proficiency & pr@"f\ci \cs @nsi & noun. & 熟练; 精通\crr
\linetab{
    \exx\eng proficiency makes perfect.\newline
    \eng \ce vidence of basic proficiency in \ce nglish is part of admission requirement.
    \relative
    \tword{proficient}{pr@"f\ci \cs @nt}{熟练的; 精通的(adj.) 能手; 老手; 专家(noun.)}
}
flush & fl2\cs  & verb.\newline noun.\newline adj. & 冲洗; 脸红; 冲(抽水马桶)\newline 冲洗; 脸红; 一阵强烈的情感\newline 满面红光的; 富足的; 齐平的\crr
\linetab{
    \exx\eng He was flush for having quarrel with his boss.\newline
    \eng Flush pipe out with clean water.\newline
    \eng \cd rinking lots of water will help flush toxins out of body. \word{toxin}{"t\ca ks\ci n}{毒素}
}
sophisticated & s@"f\ci st\ci ""ket\ci d & adj. & 复杂的; 精致的; 富有经验的; 深奥微妙的\crr
\linetab{
    \exx\eng Medical techniques are becoming more sophisticated all the time.\newline
    \eng the sophisticated pleasure of city life.
}
enlightenment & \ce n"la\ci tnm@nt & noun. & 启示; 启迪; 教化; 开导\crr
\end{engvc}


\medskip
\begin{engvc}[18-9-6]
exotic & \ci g"zat\ci k & adj. & 外来的; 外国来的; 奇异的\crr
\linetab{
    \exx\eng \ct he exotic atmosphere will fascinate you.
}
generalise & "d\cz en@r@la\ci z & verb. & 概括; 归纳; 泛论; 推广\crr
\linetab{
    \exx\eng generalise about something\newline
    \eng \ci t is difficult to generalise about job trends.
}
neurology & n\cu "r\ca l@d\cz  & noun. & 神经病学; 神经学\crr
conservation & ""k\ca ns\rse"ve\cs n & noun. & 保护; 保存; 节约\crr
\linetab{
    \exx\eng decreasing oil ocnsumption through conservation.\newline
    \eng fashion conservation measures.\chn 制定保护措施\newline
    \eng Cheaper energy conservation techniques has been put into operation
    in the developed world.
    \relative
    \tword{conservative}{k@n"s\rse vet\ci v}{保守的; 守旧的}
    \texx{A linguist and controversialist of mixed liberal and conservative views.}
}
ancestry & "\ae n""s\ce stri & noun. & 祖先; 世系; 血统\crr
compensatory & "k@mp\ce ns@t\co ri & adj. & 赔偿的; 补偿的\crr
\linetab{
    \exx\eng \ct hey are discussing the compensatory policy.\newline
    \eng He received a compensatory payment.
    \relative
    \tword{compensate}{"kAnpenset}{赔偿; 补偿}
    \tword{compensation}{""kAnpen"seS@n}{补偿(noun.)}
    \tword{atone}{@"toUn}{赎罪; 弥补; 补偿(verb.)}
    \tword{atonement}{@"tonm@nt}{赎罪; 弥补; 调和}
}
aggressive & @"gr\ce s\ci v & adj. & 侵略性的; 攻击性的; 有进取心的\crr
\linetab{
    \exx\eng \ca n aggressive young man can go far in our firm.
}
alternate & "\co lt\rse net & adj.\newline verb.\newline noun. & 交替的; 轮流的; 间隔的\newline 使交替; 使轮流\crr
\linetab{
    \relative
    \tword{alternative}{\co l"t\rse net\ci v}{备选的; 其他的(adj.) 可供选择的事物(noun.)}
    \exx\eng 
    We alternate in doing the housework.
}
infest & \ci nf\ce st & verb. & 大批出没于; 遍布于; 寄生\crr
\linetab{
    \exx\eng 
    \ct he prison is infested with rats.
}
elapse & \ci "l\ae ps & verb.\newline noun. & 逝去; 过去\newline 光阴逝去\crr
\linetab{
    \exx\eng \ct hey met again after an elapse of many years.\newline
    \eng With the elapse of time, it has faded from our memory.
    \relative
    \tword{collapse}{k@"l\ae ps}{\vtop{verb.\quad 崩溃; 倒塌; 坐下; 瓦解\newline noun.\quad 垮台; 身体的衰弱}}
    \tword{eclipse}{I"klIps}{\vtop{noun.\quad 日或月食; 丧失; 没落\newline verb.\quad 遮避; 使黯然失色}}
}
blunder & "bl2nd\rse & noun.\newline verb. & 愚蠢的错误; 失误\newline 犯愚蠢的错误; 失误\crr
\linetab{
    \exx\eng It was seen as a blunder, he said. The move turned out to be forsignted.
}
crushingly & "kr2\cs \ci \cn li & adv. & 及其\crr
\linetab{
    \relative
    \tword{crush}{kr2\cs i}{压碎; 弄皱; 变形}
    \tword{crushing}{"kr2\cs \ci \cn }{惨重的; 难以承受的; 强烈批评的}
}
brisk & br\ci sk & adj.\newline verb. & 轻快的; 爽快而清新的; 兴荣的\newline 使...活泼; 使...轻快\crr
\linetab{
    \exx\eng \cs he is noted for her brisk heanding of business.\newline
    \ci ce-cream verdors were doing a brisk trade.
    \relative
    \tword{energetic}{""En@"dZetIk}{精力充沛的}
    \tword{vigorous}{}{"vIg@r@s}{精力充沛的; 充满活力的}
}
overfish & ""o\cu v@"f\ci \cs  & verb. & 捕捞过度\crr
distruptive & d\ci s"r2pt\ci v & adj. & 引起混论的; 分裂性的; 破坏性的\crr
\linetab{
    \relative
    \tword{disrupt}{d\ci s"r2pt}{使混乱; 使中断}
    \tword{disruptive}{dIs"r2ptIv}{j起混乱的; 分裂性的; 破坏性的}
    \tword{disruption}{d\ci s"r2p\cs @n}{中断; 崩溃}
    \tword{interrupt}{""\ci nt@"r2pt}{打扰; 打岔}
    \tword{corrupt}{k@"r2pt}{腐败的(adj.) 堕落; 爆发(verb.)}
    \exx\eng \ct o understand that disruptive change and technological revolutions
    can spread both immense good and harm.
}
herd & h\textrhookrevepsilon d & noun.\newline verb. & 兽群; 牧群; 群众; 民众\newline 把...赶在一起放牧; 成群\crr
\linetab{
    \exx\eng \cn ot choice, but habit rules the unreflecting herd.
    \eng We all herded on to the bus.
}
antenna & \ae n"t\ce n@ & noun. & 触角; 天线\crr
\linetab{
    \exx\eng The antenna for may car is broken.
}
sake & sek & noun. & 缘故; 理由\crr
\linetab{
    \exx\eng He is away all year for the ssake of his work.\newline
    \eng We made concession for the sake of peace.
}
concession & k@n"s\ce \cs @n & noun. & 让步; 迁就; 特许权\crr
parliament & "p\ca rl@m@nt & noun. & 国会; 议会(British)\crr
clasp & kl\ae sp & noun.\newline verb. & 钩; 扣; 紧握; 紧抱\newline 抱紧; 握紧; 扣紧\crr
\linetab{
    \exx\eng He held her in a tight clasp\newline
    \eng He learned forward, his hands clasped tightly together.\chn 俯身向前, 双手紧握
}
sphere & sf\ci \rse & noun. & 球体; 范围\crr
pervasive & p\rse"ves\ci v & adj. & 遍布的; 弥漫的\crr
\linetab{
    \exx\eng \ca geism is pervasive in our society.\chn\word{ageism}{"ed\cz \ci z@m}{对老年人的年龄歧视}
    \eng \cs ymptoms of pervasive anti-intellectualism in our schools aren't difficult to find.
    \relative
    \tword{pervade}{p@r"ved}{弥漫; 散布(verb.)}
    \tword{pervasion}{p@"ve\cz @n}{弥漫; 分散}
}
onerous & "\ca n@r@s & adj. & 繁重的; 艰巨的; 费力的\crr
\linetab{
    \exx\eng \cs cientists accustomed to making decision purely based
    on evidence may find this to be an onerous task.
}
accustom & @"k2st@m & verb. & 使习惯\crr
extravagant & \ci k"st\ae v@g@nt & adj. & 奢侈的; 铺张的; 过分的; 放肆的\crr
\linetab{
    \exx\eng He is extravagant in his speech.
}
exempt & \ci g "z\ce mpt & adj.\newline verb. & 被免除的; 被豁免的\newline 豁免; 免除\crr
\linetab{
    \exx\eng \cs outh Carolina claimed the power to exempt its citizens 
    from the obligation to obey federal law.
}
medieval & ""midi"iv@l & adj. & 中世纪的; 中古的\crr
intimidate & \ci n"t\ci m\ci ""det & verb. & 胁迫; 威胁; 恐吓\crr
inflate & \ci n"flet & verb. & 膨胀; 使充气; 夸口; 吹嘘\crr
\linetab{
    \exx\eng He likes to inflate his achievement.
}
ripe & pa\ci p & adj. & 成熟的\crr
motive & "mo\cu t\ci v & noun. & 动机; 目的\crr
\linetab{
    \exx\eng \ct here seemed to be no motive for the murder.
}
motivation & ""m\co t@"ve\cs @n & noun. & 动机; 动力; 诱因\crr
disstill & d\ci "st\ci l & verb. & 蒸馏; 用蒸馏法提取; 蒸馏出; 提炼\crr
\linetab{
    \relative
    \tword{diffuse}{d\ci "fjuz}{扩散}
    \tword{dissolve}{d\ci "z\ca lv}{溶解; 融化; 散去; 消失}
    \tword{dilute}{d\ci "lut}{稀释(verb.) 稀释的}
}
realm & r\ce lm & noun. & 领域; 王国\crr
\linetab{
    \exx\eng \ct he king was concerned about the safety of the realm.\newline
    \eng He made contributions in the realm of foreign affairs.
}
bronze & br\ca nz & noun.\newline adj. & 青铜; 青铜色\newline 青铜色的\crr
steward & "stu\rse d & noun. & 乘务员; 管家\crr
\linetab{
    \exx\eng He is a steward on a plane\newline
    \eng \ct hey employed a steward to manage the house.
}
workshop & "w\rse k\cs \ca p & noun. & 车间; 工厂; 研讨会\crr
\linetab{
    \relative
    \tword{seminar}{"s\ce m@""n\ca r}{专题研讨会}
    \tword{conference}{"k\ca nf\rse r@ns}{研讨会; 会议(noun.) 举行或参加会议(verb.)}
    \tword{congress}{k\ca n"g@r@s}{国会; 代表大会(noun.) 开会; 集合(verb.)}
}
cooperative & k\co "\ca p@r@t\ci v & adj.\newline noun. & 合作的; 协作的\newline 合作社\crr
\linetab{
    \exx\eng \ci  have always found her cooperative.\newline
    \relative
    \tword{corporation}{""k\co p@"re\cs @n}{公司; 法人; 团体}
    \tword{coordinate}{ko"\co rd@"net}{协调; 同等; 搭配(verb.) 同等的(adj.) 坐标; 套装; 同等重要的人(noun.)}
    \tword{cooperate}{k\co "\ca p@""ret}{合作}
}
unionize & "jun\ci rna\ci z & verb. & 组织工会; 加入公会\crr
\linetab{
    \exx\eng 
    \ct hey were forbidden to unionize.
}
spectrum & "sp\ce ktr@m & 光谱; 频谱; 范围\crr
cordial & "k\co rd\cz @l & adj.\newline noun. & 热诚的; 衷心的\newline 兴奋剂; 甜酒\crr
\linetab{
    \exx\eng 
    Please accept my cordial apology.
}
correspond & ""k\co r@"sp\ca nd & verb. & 符合; 通信; 相类似; 相对应\crr
\linetab{
    \exx\eng those who thought that the images higher up the attractiveness scale were 
    real directly conrresponded with those who showed other.\newline
    \relative
    \tword{correspondent}{""k\co r@"sp\ca nd@nt}{通讯记者; 通信者}
    \eng With more details, here's our foreign affairs correspondent.\newline
    \tword{correspondence}{k\co r@sp\ca nd@ns}{符合; 一致; 通信; 信件(noun.)}
    \eng \ci n \ca frican languages there is a close correspondence between sounds and letters.
}
exact & \ci g"z\ae kt & adj.\newline verb. & 精确的; 准确的\newline 强求; 急需; 要求\crr
moist & m\co \ci st & adj. & 潮湿的; 湿润的\crr
\linetab{
    \exx\eng Winds from the sea are usually moist.
    \tword{moist}{mOIst}{微湿, 侧重不干; 但不会湿的令人不快}
    \tword{humid}{"hjumId}{空气特别的潮湿, 相对湿度大}
    \tword{damp}{d\ae mp}{吸金或覆盖着一点水分, 表示潮湿的让人不舒服}
    \tword{wet}{wet}{一般的潮湿}
}
priest & prist & noun. & 牧师; 神父; 教士\crr
\linetab{
    \exx\eng The priest is listening to his confession.
}
orientation & ""\co ri\ce n"te\cs @n & noun. & 方向; 定位; 取向\crr
\linetab{
    \tphrase{sexual orientation}{性取向}
    \tphrase{marketing orientation}{营销定位}
}
retreat & r\ci "trit & verb.\newline noun. & 撤退; 退却; 退缩\newline 撤退; 退却; 退缩\crr
\linetab{
    \relative
    \tword{shrink}{\cs ri\cn k}{收缩; 退缩; 皱缩}
    \tword{obstacle}{"\ca bst@kl}{障碍物; 障碍}
    \tword{withdraw}{w\ci \ct "dr\co }{撤退; 取钱; 退出}
    \tword{retract}{r\ci "tr\ae kt}{缩回; 缩进; 撤回; 撤销}
    \tword{entreat}{\ce n"trit}{恳求; 祈求(verb.)}
    \tword{maltreat}{m\ae l"trit}{虐待; 亏待}
    \tword{recede}{r\ci "sid}{后退; 减弱; 变坏}
}
revolve & r\ci "v\ca lv & verb. & 旋转; 考虑; 围绕\crr
\linetab{
    \exx\eng Most of the action has revolved around efforts to tap consumer market.\newline
    \eng newton lived in a world that had only just stopped assuming that the 
    sun revolved around the Earth.
    \relative
    \tword{involve}{In"vAlv}{使...卷入; 牵涉; 包含}
    \tword{resolve}{rI"zAlv}{决心; 决议; 使分解; 解体(verb.) 决定; 决议(noun.)}
    \tword{evolve}{I"vAlv}{进化; 发展; 制定; 发出; 设计(verb.)}
}
revolt & r\ci "vo\cu lt & verb.\newline noun. & 叛乱; 反叛; 使厌恶\newline 叛乱; 厌恶; 反感\crr
stalk & st\co k & noun.\newline verb. & 茎; 柄; 梗\newline 跟踪; 偷偷接近; 昂首阔步地走\crr
\linetab{
    \exx\eng He cut off the flowers at the stalk.\newline
    \eng \ct he lion will often stalk its prey for hours.\newline
    \eng We stalk around thinking we're hot stuff.
}
stain & sten & noun.\newline verb. & 污点\newline 玷污\crr
\linetab{
    \relative
    \tword{blot}{blAt}{污点(表示不好的)}
    \tword{spot}{spAt}{点}
    \tword{stain}{sten}{污渍}
}
astronaut & "\ae str@""n\co t & noun. & 宇航员\crr
fracture & "fr\ae kt\cs \rse & noun.\newline verb. & 破裂; 骨折\newline 使断裂; 使骨折; 使分裂\crr
\linetab{
    \exx\eng \co ld people's bones are easy to fracture.\newline
    \eng \ct he fracture of \cu \cs -China relationship severely affects trades of both sides.
}
augment & \co g"m\ce nt & verb. & 增强; 增加; 扩大\crr
\linetab{
    \exx\eng We augment our own intelligence by turning to others.
}
crew & kru & noun. & 全体船员; 全体人员\crr
peep & pip & verb.\newline noun. & 窥看; 微露出; 唧唧叫\newline 窥视; 隐现; 唧唧声\crr
drift & dr\ci ft & verb.\newline noun. & 漂流; 漂移\newline 漂流; 趋势; 冲积物\crr
\linetab{
    \exx\eng \ct here is a drift of farmers to the cities.
}
draft & dr\ae ft & noun.\newline verb.\newline adj. & 草稿; 选派; 气流\newline 起草; 征募; 草图\newline 草图的; 初步画出的\crr
magnify & "m\ae gn@""fa\ci  & verb. & 增加; 增强; 扩大\crr
struggle & "str2g@l & verb.\newline noun. & 斗争; 挣扎; 抗争\newline 斗争; 奋斗; 抗争\crr
\linetab{
    \relative
    \tword{compaign}{k\ae m"pen}{运动; 战役(noun.) 作战; 参战(verb.)}
    \tword{warfare}{w\co r"fe@}{战争; 战争状态; 冲突}
    \tword{combat}{"k\ca mb\ae t}{战斗; 搏斗(noun.) 与...战斗(verb.)}
}
exquisite & \ci k"skw\ci z\ci t & adj. & 精美的; 细腻的; 强烈的\crr
\linetab{
    \relative
    \tword{requisite}{"r\ce kw\ci z\ci t}{必需的; 必备的}
    \tword{perquisite}{"p\rse kw\ci z\ci t}{额外补贴; 特权}
    \tword{prerequisite}{pri"r\ce kw\ci z\ci t}{先决条件; 先决条件的}
}
sector & "s\ce kt\rse & noun. & 部门; 行业; 扇形\crr
fringe & fr\ci nd\cz  & noun.\newline verb. & 流苏; 边缘; 刘海\newline 作为...的边缘\crr
fume & fjum & noun.\newline verb. & 烟雾; 烟气; 愤怒; 烦恼\newline 用烟熏; 冒烟; 大为生气\crr
\linetab{
    \exx\eng \ci t's \co K to keep pouring fumes into the air until we know for sure.
}
infringement & \ci n"fr\ci nd\cz m@nt & noun. & 违反(法规、规章制度等); 侵犯(合法权益)\crr
\linetab{
    \relative
    \tword{infringe}{\ci n"fr\ci nd\cz }{侵犯; 违反; 破坏}
    \exx\eng Won't multinationals production from one place to another when a
    nation gets too strict about infringement to comptition.\newline
    \eng infringement of regulation should be punishable by a fine.
}
humidity & hju"m\ci d\ci ti & noun. & 湿度; 湿气\crr
\linetab{
    \relative
    \tword{humid}{"hjum\ci d}{潮湿的}
    \tword{humidify}{hju"m\ci d@fa\ci }{使潮湿}
    \tword{humidifier}{hju"m\ci d@""fa\ci \rse}{加湿器}
    \tword{humility}{hju"m\ci l\ci ti}{谦逊}
    \tword{humanity}{hju"m\ae n\ci ti}{人道}
}
hurl & h\rse l & verb. & 猛投; 用力投; 大声叫骂\crr
valve & v\ae lv & noun. & 阀; 活门; 瓣膜; 壳瓣\crr
exhaust & \ci g"z\co st & verb. & 排出; 用尽(verb.) 排气装置; 排气(noun.)\crr
emission & \ci "m\ci \cs @n & noun. & 排放; 辐射; 排放物; 发行; 发布\crr
hypothesis & ha\ci "p\ca \ct @s\ci s & noun. & 假设; 假说\crr
\linetab{
    \exx\eng \ct he hypothesis has not been proved.\newline
    \eng to formulate / confirm a hypothesis\newline
    \eng But a tool to build apps, or create artwork, or test hypothesis.
    \relative
    \tword{hypothetical}{""ha\ci p@"\ct \ce t\ci k@l}{假设的; 爱猜测的}
    \tword{hypocrisy}{h\ci "p\ca kr@si}{虚伪; 伪善}
}
overtake & ""ov\rse"tek & verb. & 赶上; 超过\crr
\linetab{
    \exx\eng \ci t is very dangerous to overtake at a corner.
}
tune & tun & verb. & 调整; 调音\newline 曲调; 调子\crr
merry & "m\ce ri & adj. & 欢乐的\crr
avert & @"v\rse t & verb. & 转开; 避免; 防止\crr
\linetab{
    \exx\eng \ct he government failed to avert a national strike.\newline
    \eng \ca ccidents can be averted by careful driving.
}
furnish & "f\rse n\ci \cs  & verb. & 布置家具; 配备; 供给; 提供\crr
\linetab{
    \exx\eng \ce xceptionally detailed theory lined up with ever-better observational data 
    to furnish predictions about phsical phenomena.
}
phenomenon & f@"n\ca m\ci n@n & noun. & 现象; 事件; 奇迹; 非凡的人\crr
\linetab{
    \relative
    \tword{phenomena}{f\ci "n\ca m@n@}{现象(plural of phenomenon)}
}
fuss & f2s & noun.\newline verb. & 不必要的紧张; 忙乱; 大惊小怪\newline 瞎忙活; 大惊小怪; 过分关爱\crr
ivory & "a\ci v@ri & noun. & 象牙; 乳白色\crr
\linetab{
    \exx\eng the international ban on the sale of ivory.
}
prosperous & "pr\ca sp@r@s & adj. & 繁荣的; 兴旺的\crr
\linetab{
    \exx\eng \ci t used to be a very prosperous town.\newline
    \eng \ca merica and \ca mericans were prosperous beyond the dreams of the \ce uropeans 
    and \ca sians whose economies the war had destroyed.
}
propaganda & ""pr\ca p@"g\ae nd@ & noun. & 宣传; 宣传活动\crr
propagandize & ""pr\ca p@"g\ae nda\ci z & verb. & 宣传\crr
\end{engvc}

\medskip
\begin{engvc}[18-9-7]
ultraviolet & ""2ltr@"va\ci @l\ci t & adj.\newline noun. & 紫外的; 紫外线的\newline 紫外线辐射; 紫外光\crr
contrive & k@n"tra\ci v & verb. & 图谋; 发明; 设计; 设法做到\crr
\linetab{
    \exx\eng \ct hey contrive a new machine for flying.\newline
    \eng to contrive an escape from the prison.
}
infirm & \ci n"f\rse m & adj. & 体弱的; 虚弱的\crr
disguise & d\ci s"ga\ci z & verb.\newline noun. & 掩盖; 隐瞒; 伪装\newline 伪装; 借口\crr
\linetab{
    \exx\eng \ci  finally penestrate her disguise.
}
admit & @d"m\ci t & verb. & 承认; 许可进入; 允许\crr
quota & "kwo\cu t@ & noun. & 配额; 限额; 定额\crr
\linetab{
    \exx\eng From the top, quotas are being introduced for higher job levels.\newline
    \eng We fulfilled the quota in half the time.
    \relative
    \tword{quote}{kwo\cu t}{引用; 报价(verb. noun.)}
    \tword{quotation}{kwo\cu "te\cs n}{引用}
}
stage & sted\cz  & noun.\newline verb. & 阶段; 时期; 舞台\newline 举行; 上演\crr
aesthetic & \ce s"\ct \ce t\ci k & adj. & 审美的; 美学的\crr
\linetab{
    \exx\eng My aesthetic standards are different from his.\newline
    \eng \ca esthetic effect came from the landscape, new materials and forthright detailing.
}
consequently & "k\ca ns@kwentli & adv. & 从而; 结果; 因此\crr
\linetab{
    \relative
    \tword{consequent}{"k\ca ns@""kwent}{作为结果的; 随之发生的}
    \tword{sequent}{"sikw@nt}{接踵而来的}
    \tword{sequency}{s\ci "kw@ns\ci }{顺序}
    \tword{sequential}{s\ci "kw\ce n\cs @l}{按次序的}
}
objectionable & @b"d\cz \ce k\cs @n@b@l & adj. & 令人不快的; 令人反感的; 讨厌的\crr
guild & g\ci ld & noun. & 行会; 同业公会; 协会\crr
\end{engvc}

\medskip
\begin{engvc}[18-9-11]
waggon & "w\ae g@n & noun. & 四轮货车\crr
rest & r\ce st & verb.\newline noun. & 休息； 使依靠； 停留在； 中止\newline 休息; 其他; 剩余部分; 宁静\crr
\linetab{
    \exx\eng copyright rested with the journal publisher.
}
lifetime & "la\ci f""ta\ci m & noun. & 寿命; 一生; 终身\crr
\linetab{
    \exx\eng 
    \ci t's the chance of a lifetime.
    \eng
    Learning is a enterprise of a lifetime.
}
disciplinary & "d\ci s@pl@neri & adj. & 训练的; 纪律的; 训诫的\crr
\linetab{
    \exx\eng
    \ca  disciplinary dog can be a guide to the blind.\newline
    \eng \ct he social sciences are focused on disciplinary and internal scholarly
    debates, rather than on topics with external impact.\newline
    \relative
    \tword{discipline}{"d\ci s@pl\ci n}{训练; 处罚; 使有纪律(verb.) 纪律;学科(noun.)}
    \tword{disciplinarian}{""d\ci s@pl\ci "neri@n}{纪律实施者}
    \tword{disciplined}{"d\ci s@pl\ci nd}{受过训练的; 遵守纪律的}
    \tphrase{discipline educate}{纪律教育}
}
scissors & "s\ci z\rse z & noun. & 剪刀\crr
conceive & k@n"s\ci v & verb. & 设想; 构想; 怀孕; 怀有\crr
\linetab{
    \relative
    \tword{conceivably}{k@n"siv@bli}{可以想象地; 令人信服地; 可能}
    \exx\eng He conceive the idea of transforming the old power tation to an arts centre.
}
cliff & kl\ci f & noun. & 悬崖; 峭壁\crr
lawn & l\co n & noun. & 草坪; 草地\crr
\linetab{
    \exx\eng At dawn, a fawn is yawning on the lawn.
}
hominid & "h\ca m\ci n\ci d & noun.\newline adj. & 原始人类\newline 人科的\crr
hindrance & "h\ci ndr@ns & noun. & 妨碍; 造成妨碍的人; 阻挠\crr
\linetab{
    \exx\eng \ct o be honest, she was more of a hindrance than a help.
    \relative
    \word{hinder}{"hInd\rse}{\vtop{verb.\quad 妨碍; 阻碍\newline \ adj.\quad 后面的; 后方的}}
}
cruise & kruz & verb.\newline noun. & 乘船游览; 航游; 缓慢行进\newline 乘船游览; 航游\crr
\end{engvc}

\medskip
\begin{engvc}[18-9-13]
inhuman & \ci n"hjum@n & adj. & 野蛮的; 无人性的; 残忍的\crr
mercilessly & "m@s\ci l\ci sli & adv. & 无情地; 残忍地; 无慈悲地\crr
\linetab{
    \exx\eng Caroonists then mercilessly mocked him.
    \relative
    \tword{mercy}{"m3rsi}{仁慈}
    
}
suppress & s@"pr\ce s & verb. & 镇压; 压抑; 查禁; 使止住\crr
\linetab{
    \relative
    \tword{impress}{\ci m"pr\ce s}{使印象深刻}
    \tword{depress}{d\ci "pr\ce s}{压下; 使萧条; 使沮丧}
    \tword{compress}{k@m"pr\ce s}{压缩}
    \tword{decompress}{dik@m"pr\ce s}{解压}
    \tword{oppress}{@"pr\ce s}{使烦恼; 压迫; 虐待; 欺辱}
    \tword{oppresion}{@"prES@n}{压迫; 压制; 压抑; 镇压}
}
excel & \ci k"s\ce l & verb. & 优于; 擅长; 胜过\crr
distil & d\ci "st\ci l & verb. & 蒸馏; 用蒸馏法提取; 提炼\crr
\linetab{
    \exx\eng \cd istil the essence of natural plants.\newline
    \eng Please distil the crucial points of the book.
}
crucial & "kru\cs @l & adj. & 决定性; 关键的\crr
gravity & "gr\ae v@ti & noun. & 重力; 地心引;； 严重性; 庄重; 严肃\crr
\linetab{
    \exx\eng \cs ir \ci saac \cn ewton supposedly discovered gravity throught the fall of an apple.\newline
    \eng We understand the gravity of the climate threat.
}
fuss & f2s & noun.\newline verb. & 不必要的紧张; 慌乱; 大惊小怪\newline 瞎忙活; 大惊小怪; 过分关爱\crr
\linetab{
    \exx\eng \cs he make a fuss when \ci 'm minutes late.
}
prosecute & "pr\ca s\ci kjut & verb. & 起诉; 控告; 检举; 指控; 继续从事\crr
\linetab{
    \exx\eng Will you be ablee to prosecute your responsibilities?\newline
    \eng \ct hs \cu \cs  would prosecute the war to end.
}
provision & pr@"v\ci \cz @n & noun. & 供应; 预备; 存粮; 规定; 条款\crr
\linetab{
    \exx\eng \ct hree provisions of \ca rizona's plan were overturned because they overstepped
    the authority of federal immigration law.\newline
    \eng \ct his is a provision in car insurance.
}
curtail & k\textrhookrevepsilon r"tel & verb. & 削减; 剥夺\crr
cunning & "k@n\ci \cn  & adj.\newline noun. & 狡猾的\newline 狡猾; 狡黠\crr
\linetab{
    \exx\eng \ci t was a cunning piece of detective work.\newline
    \eng \cs ince the dawn of human ingeuity, people have devised
    ever more cunning tools to cope with work that is dangerous, burdensome.
}
curse & k\rse s & verb.\newline noun. & 诅咒; 咒骂\newline 诅咒; 咒骂\crr
\linetab{
    \exx\eng \ct elevision ads for erectile dysfunction, stroke or toenail fungus treatments 
    have been called both a boon and a curse.
    \tword{erectile}{\ci "r\ce kt@l}{可直立的; 勃起的}
    \tword{dysfunction}{d\ci s"f2\cn \cs @l}{功能障碍; 机能失调}
}
swift & sw\ci ft & adj. \newline noun. & 快的; 迅速的; 敏捷的\newline 雨燕\crr
punctual & "p2\cn t\cs \cu @l & adj. & 准时的\crr
\linetab{
    \exx\eng He is always punctual for appointments.\newline
    \eng \ct he tenants are punctual in paying the rent.
}
escapable & \ci s"kep@bl & adj. & 可避免的\crr
\linetab{
    \relative
    \tword{inescapable}{""\ci n\ci "sk2p@bl}{不可避免的}
    \tword{inescapbly}{""\ci n\ci "skep@bli}{逃不掉地}
}
tail & tel & noun.\newline verb. & 尾巴; 尾部; 尾随者\newline 尾随; 跟踪; 为...装尾; 行列散开\crr
beach & bit\cs  & noun. & 海滩; 沙滩\crr
beverage & "b\ce v@nd\cz  & noun. & 饮料\crr
\linetab{
    \exx\eng He never drinks alcoholic beverage.
}
omit & o"m\ci t & verb. & 省略; 遗漏\crr
\linetab{
    \exx\eng \ct ell me what happened and don't omit any details.\newline
    \eng \cd on't omit his name from the list.
}
bulletin & "b\cu l\ci t\ci n & noun. & 公告; 布告; 公报\crr
\linetab{
    \exx\eng We posted bulletins all day long.\newline
    \eng Let's pin the notice on the bulletin board.
}
calcium & "k\ae Lsi@m & noun. & 钙\crr
\linetab{
    \remark
    元素名称常以"-ium"结尾
}
grown-up & "gron""2p & adj.\newline noun. & 成年的; 成人的\newline 成年人\crr
predatory & "pred@t\co ri & adj. & 食肉的; 掠夺性的\crr
\linetab{
    \exx\eng Predatory fishing behaviour destroyed the ecology balance.
}
drown & dra\cu n & verb. & 淹没; 溺死\crr
\linetab{
    \exx\eng \cd on't play by the river in case you fall in and drown!\newline
    \eng \ci t is no use trying to drown your sorrows in drink.
}
crab & kr\ae b & noun.\newline verb. & 蟹; 螃蟹\newline 抱怨; 发牢骚\crr
\linetab{
    \exx\eng \ct o crab the conduct of a neighbour.
}
dew & du & noun. & 露; 露水\crr
\linetab{
    \exx\eng \ct he timely dew of sleep.\newline
    \eng \ct he grass is wet with dew.s\newline
    \eng \ct he dew gathered on the leaves.
}
dose & do\cu s & noun.\newline verb. & 剂量; 一剂\newline 服药\crr
\linetab{
    \relative
    \tword{dove}{do\cu v}{鸽子}
    \tword{doze}{do\cu z}{瞌睡}
    \tword{antidote}{"\ae nt\ci do\cu t}{解药}
    \tword{overdose}{"o\cu v\rse do\cu s}{服药过量}
    \tword{dope}{do\cu p}{麻醉剂; 毒品}
    \tword{dosage}{"do\cu s\ci d\cz }{用药剂量}
}
knock & n\ca k & verb.\newline noun. & 敲; 撞; 击; 打\newline 撞击; 敲击\crr
\linetab{
    \relative
    \tphrase{knock at}{敲门 窗}
    \tphrase{knock off}{击倒; 停工; 中断}
    \tphrase{knock down}{击倒; 拆卸}
    \tphrase{knock out}{敲空; 击倒; 打破; 使筋疲力竭}
    \tphrase{knock into}{撞上; 撞倒}
    \tphrase{knock over}{打翻; 撞倒}
    \tphrase{knock in}{钉入}
    \tphrase{knock up}{敲门唤醒; 往上敲}
    \tphrase{knock back}{反击; 逆行}
    \tphrase{knock against}{撞击; 与...冲}
}
optimum & "\ca pt\ci m@m & adj. & 最适的; 最佳的\crr
\linetab{
    \relative
    \tword{optimist}{"\ca pt\ci m\ci st}{乐观主义者}
    \tword{optimal}{"\ca pt@m@l}{最佳的; 最理想的}
    \tword{optimise}{"\ca pt\ci ma\ci z}{使最优化; 使尽可能有效}
    \eng \ct his means using knowledge gleaned from data to optimise and automate
    all kinds of processes.
}
librarian & la\ci "brer\ci rn & noun. & 图书管理员\crr
harness & "h\ca rn\ci s & noun.\newline verb. & 马具; 挽具\newline 套马具; 驾驭; 利用; 治理\crr
\linetab{
    \exx\eng \ci f you can harness you emotion, you will get great success.
}
guardianship & "g\ca rd\ci @n\cs \ci p & noun. & 监护人身份; 监护人的职责\crr
\linetab{
    \exx\eng \ci f the guardian has done his duty of guardianship, his civil liability 
    may be appropriately reduced.\newline
    \eng \ct his is depriving <<mothers of the guardianship> of their children>.
}
masculine & "m\ae skj@l\ci n & adj. & 男性的; 男子气概的; 阳性的\crr
\linetab{
    \relative
    \tword{feminine}{"f\ce m@n\ci n}{女性的; 阴性的}
    \tword{muscular}{"m2skj@l\rse}{肌肉的}
}
pail & pel & noun. & 桶; 一桶之量\crr
\linetab{
    \exx\eng \ce ducation is not the filling of a pail, but lighting of a fire.
}
peasant & "p\ce z@nt & noun. & 农民; 乡巴佬; 庄稼人\crr
\linetab{
    \exx\eng \cs he war born in a poor peasant family.
}
peanut & "pi""n2t & noun.\newline adj. & 花生; 微不足道的人; 小人物\newline 微不足道的\crr
oar & \co r & noun. & 浆; 船桨\crr
pebble & "p\ce b@l & noun. & 鹅软石; 小圆石\crr
\linetab{
    \relative
    \tword{rubble}{"r2b@l}{碎石; 瓦砾}
    \tword{bubble}{"b2b@l}{气泡; 泡影; 妄想(verb. noun.)}
    \tword{paddle}{"p\ae d@l}{浆; 涉水; 用浆划动(verb. noun.)}
    \tword{peddle}{p\ce "dl}{传播; 散播; 兜售; 叫卖}
    \tword{pedal}{p\ce "dl}{踏板; 脚蹬子; 骑自行车}
    \tword{pedlar}{p\ce "dl\rse}{流动小贩; 商贩; 传播者}
}
prohibit & pro"h\ci b\ci t & verb. & 禁止; 阻止; 防止; 不允许\crr
prohibition & ""pro@h\ci "b\ci \cs n & noun. & 禁令; 禁止; 诉讼中止令\crr
\linetab{
    \exx\eng Citizens still have a right to expect private documents to remain protected
    by the C's prohibition on unreasonable searches.
}
projector & pr@"d\cz \ce kt\rse & noun. & 投影仪; 放映机\crr
queue & kju & noun.\newline verb. & 队列; 辫子\newline 排队等候\crr
queen & kwin & noun. & 女王; 王后\crr
rug & r2g & 小地毯; 垫子\crr
\linetab{
    \exx\eng weave a rug.
}
hardly & "h\ca rdli & adv. & 几乎没有; 简直不\crr
soap & sop & noun. & 肥皂\crr
stocking & "st\ca k\ci \cn  & noun. & 长袜\crr
\linetab{
    \relative
    \tword{sock}{s\ca k}{短袜}
    \tword{stock}{st\ca k}{\hbox{\noindent\vtop{股票; 库存; 树干; 家畜(noun.)\newline 常备的; 存货的; 陈旧的(adj.)\newline 提供货物; 出新芽; 囤积(verb.)}}}
}
towel & "ta\cu @l & noun. & 毛巾\crr
village & "v\ci l\ci d\cz  & noun. & 村庄; 乡村\crr
warm & w\co rm & adj.\newline verb. & 温暖的\newline 使变暖\crr
trunk & tr2\cn k & noun. & 树干; 躯干; 大衣箱; 象鼻子\crr
\linetab{
    \exx\eng \ct he athlete has a powerful trunk.\newline
    \eng \ct he branch separated from the trunk of the tree.
}
dentist & "d\ce nt\ci st & noun. & 牙科医生\crr
last & l\ae st & adj.\newline verb. & 最后的; 最近的\crr
\linetab{
    \exx\eng \ct he low inflation rate will last for some time.\newline
    \eng My life has changed a lot in the last few months.
    \remark
    "last" and "lastest":\newline
    last: 表示最后的, 暗示以后不会有了\newline
    lastest: 表示最新的, 暗示以后还会有.
}
drag & dr\ae g & verb.\newline noun. & 拖; 硬拉; 拖沓\newline 累赘; 阻力\crr
\linetab{
    \exx\eng Wasted time is a drag on \ca mericans' economic and private lives.\newline
    \eng \ci  drag the heavy case across the floor.
}
restaurant & "r\ce str\ca nt & noun. & 餐厅; 餐馆\crr
abrupt & @"br2pt & adj. & 突然的; 唐突的; 粗鲁无礼的; 不连贯的; 陡峭的\crr
\linetab{
    \relative
    \tword{corrupt}{k@"r2pt}{腐败的; 堕落的}
    \tword{disrupt}{d\ci s"r2pt}{干扰; 打断; 分裂}
    \tword{interrupt}{""\ci nt@"r2pt}{干扰; 打断; 中断}
    \tword{bankrupt}{"b\ae \cn ""kr2pt}{破厂的; 枯竭的}
}
shorthand & "\cs \co rth\ae nd & noun. & 速记\crr
\linetab{
    \exx\eng He took down the minute in shorthand.\newline
    \eng \cs he is learning to write shorthand.\newline
}
nephew & "n\ce fju & noun. & 侄子; 外甥\crr
adapt & @"d\ae pt & verb. & 适应; 改编; 改写; 改变\crr
\linetab{
    \relative
    \tword{adaptable}{@"d\ae pt@b@l}{能适应地; 可适用地}
    \tword{adaptive}{@"d\ae p@t\ci v}{有适应能力地}
    \tword{adaptor}{@"d\ae p@t\rse}{改编者; 电源适配器}
    \tword{adaptation}{""\ae t\ae p"te\cs @n}{适应; 改编的作品}
    \tword{adaptability}{@""d\ae p@t@"b\ci l@ti}{适应能力}
}
engineering & ""end\cz \ci "n\ci r\ci \cn  & noun. & 工程; 工程学\crr
approachable & @"pro\cu t\cs @bl & adj. & 和蔼可亲的; 可接近的\crr
biased & "ba\ci @st & adj.\newline verb. & 有偏见的; 片面的\newline 使倾向于; 使有偏见(bias的过去分词)\crr
\linetab{
    \exx\eng
    Mothers are biased to think their children are best in the world.\newline
    \eng biased against classical liberal ideas.
}
compete & k@m"pit & verb. & 竞争; 竞赛; 参加比赛\crr
\linetab{
    \exx\eng \ct he stores will inevitably end up competing with each other in
    their push for increasing market shares.\chn\phrase{market share}{市场占有率}
    \relative
    \tword{competence}{"k\ca mp\ci t@ns}{能力; 胜任; 本领(noun.)}
    \tword{competition}{k@m"pit\ci \cs @n}{竞争(noun.)}
    \eng The American areospace industry has been challenged by some stiff competition.\newline\word{stiff}{st\ci f}{严厉的; 呆板的; 坚硬的}
    \tword{competent}{"k\ca mp\ci t@nt}{有能力的; 胜任的; 足够的}
    \eng Most adults do not feel competent to deal with a medical emergency involving a child.
    \chn \phrase{medical emergency}{紧急医疗}
    \tword{competitive}{k@m"p\ce t\ci t\ci v}{竞争的}
    \eng \co nly by keeping down costs will \ca merican maintain its competitive advantage over other countries.
}
contributory & k@n"tr\ci bj@t\co ri & adj.\newline noun. & 有贡献的; 促成的; 促进的\newline 贡献人; 捐助者\crr
courtship & "k\co rt\cs \ci p & noun. & 求爱; 恋爱; 求偶\crr
\linetab{
    \exx\eng Just as the bewildering variety of human courtship rituals might all be
    considered forms of sexual selection.\chn\word{bewilder}{b\ci "w\ci ld\rse}{使困惑; 使为难; 使手足无措}
}
cure-all & "kj\cu r""\co l & noun. & 仙丹\crr
granny & "gr\ae ni & noun. & 奶奶; 外婆\crr
democrat & "d\ce m@""kr\ae t & noun. & 民主主义者; 民主党员\crr
\linetab{
    \relative
    \tword{democratic}{""d\ce m@"kr\ae t\ci k}{民主的; 大众的; 民主政治的}
    \tword{democracy}{d\ci "m\ca kr@si}{民主; 民主政治}
}
genome & "d\cz ino\cu m & noun. & 基因组; 染色体组\crr
indictment & \ci n"da\ci tm@nt & noun. & 起诉; 控告; 起诉状\crr
\linetab{
    \exx\eng \ci t risks turning one sensational incident into an indictment of tens 
    of thousands of police encounters.\newline
    \eng The suspect will face an indictment.
    \chn 它有可能把一起耸人听闻的事件变成对数以万计的警察遭遇的起诉.
    \relative
    \tword{indict}{\ci n"da\ci t}{告发; 控告; 起诉}
    \tword{incriminate}{\ci n"kr\ci m@""net}{控告; 使某人显得有罪; 归罪于}
}
inequality & ""\ci n"kw\ca l@ti & noun. & 不平等; 不平衡; 不平均\crr
\end{engvc}

\begin{engvc}[18-9-14]
canteen & k\ae n"tin & noun. & 食堂; 小卖部\crr
tattoo & t\ae"tu & noun.\newline verb. & 纹身; 归营鼓\newline 刺青; 连续的敲击\crr
majesetic & m@"dZEstIk & adj. & 宏伟的; 壮丽的; 威严的\crr
giggle & "gIg@l & verb.\newline noun. & 咯咯地笑\newline 咯咯笑; 趣事\crr
\linetab{
    \exx\eng Today's lesson was a bit of giggle\newline
    \eng Both girls began to giggle.
}
skeptical & "skeptIk@l & adj. & 怀疑的; 无神论地; 好怀疑的\crr
\linetab{
    \relative
    \tword{skeptic}{"skEptIk}{怀疑性的 怀疑论者}
    \tword{skepticism}{"skEptI""sIz@m}{怀疑主义者}
}
quick-witted & "kwIk""wItId & adj. & 才思敏捷的; 聪敏的; 机智的\crr
entrance & "Entr@ns & noun.\newline verb. & 入口; 进入; 到场\newline 使出神; 使入迷\crr
slap & sl\ae p & verb.\newline noun. & 拍; 掴; 拍击\crr
\linetab{
    \relative
    \tword{clap}{kl\ae p}{鼓掌(verb. noun.)}
}
therm & T3rm & noun. & 克卡; 小卡(热量单位)\crr
\linetab{
    \relative
    \tword{thermic}{"T3mIk}{热的; 由热造成的}
    \tword{thermal}{"T3rml}{热的; 保温的}
    \tword{thermae}{"T3mi}{温泉; 温泉浴场; 公共浴池}
    \tword{thermometer}{T@r"mAmIt@}{温度计}
    \tword{thermoanalysis}{T3m@@"n\ae lIsIs}{热学分析}
    \tword{thermicfever}{T3rmIk"fiv\rse}{中暑}
    \tword{thermostat}{"T\rse m@st\ae t}{自动调温器; 恒温器}
}
flock & flAk & noun.\newline verb. & 群; 聚集; 群集\crr
attract & @"tr\ae kt & verb. & 吸引; 诱惑; 引起注意\crr
\linetab{
    \relative
    \tword{attractive}{@"tr\ae ktIv}{有吸引力的}
    \tword{attractable}{@t"tr\ae kt@b@l}{可被吸引的}
    \tword{attraction}{@"tr\ae kS@n}{吸引; 吸引力; 吸引人的事物}
    \tword{attractiveness}{@"tr\ae ktIvn@s}{吸引力; 迷惑力}
    \tword{attractor}{@"tr\ae kt\rse}{吸引子; 引起注意的人}
}
fist & fIst & noun.\newline verb. & 拳头; 笔迹; 掌握\newline 用拳头打; 紧握\crr
extinct & Ik"stINkt & adj. & 灭绝的; 熄灭的; 绝种的\crr
extinction & Ik"stINkS@n & noun. & 熄灭; 消灭; 灭绝; 废除\crr
instigate & "InstI""get & verb. & 教唆; 煽动; 激起\crr
historic & hI"stOrIk & adj. & 有历史意义的; 历史性的\crr
\linetab{
    \exx\eng This is a historic occasion.
}
confess & k@n"fEs & verb. & 坦白; 承认\crr
edge & EdZ & noun.\newline verb. & 边缘; 边沿; 锋; 刃; 锋利; 优势\newline 使锋利; 使侧着移动\crr
\linetab{
    \exx\eng He edged closer to the telephone, ready to grab it.\newline
    \eng The threee days France have to prepare could give them the edge over England.
}
privacy & "praIv@si & noun. & 隐私; 秘密; 私事\crr
\linetab{
    \relative
    \tword{private}{"praIv}{私人的; 私有的; 内心的(adj.) 士兵; 列兵; 二等兵(noun.)}
    \tword{privilege}{"prIvIl@dZ}{特权(noun.) 给...特权(verb.)}
    \tword{privity}{"prIv@ti}{默契; 私下知悉}
    \eng You know me very well, you always know what I need. I enjoy privity between us.
    I hope this state will last forever, in spite of wherever we are.\newline
    \tword{privy}{"prIvi}{秘密的; 个人的(adj.) 有利害关系的人}
    \tword{deprive}{dI"praIv}{夺去; 剥夺; 使丧失}
}
inexorable & In"Eks@r@b@l & adj. & 不可阻挡的; 无情的\crr
\linetab{
    \exx\eng It was the inexorable rise of capitalism and the bourgeosis that had overthrown
    the feudal aristocratic order.\newline
    \tword{captitalism}{"k\ae pItl""Iz@m}{资本主义(制度); 资本的支配地位}
    \tword{bourgeosis}{""bUrZwA"zi}{中产阶级; 资产阶级(noun.)}
    \tword{aristocratic}{@"rIstt@kr\ae t}{贵族; 贵族政治论者}
}
injurious & In"dZUri@s & adj. & 有害的; 中伤的\crr
\linetab{
    \exx\eng but might possible be injurious to intellect, and more probably to
    moral character.
}
integration & ""IntI"greS@n & noun. & 结合; 整合; 一体化\crr
\linetab{
    \relative
    \tword{integrity}{In"tEgrIti}{正直; 忠诚; 完整}
    \tword{integrated}{"IntIgretId}{互相协调的; 整体的; 完全的}
    \tword{integrate}{"Int@""gret}{使成一体; 合并; 积分运算(verb.)}
}
intensify & In"tEns@""faI & verb. & 加强; 强化; 深化\crr
\linetab{
    \exx\eng Failures intensify my desire to succeed.
}
intervene & ""Int@r"vin & verb. & 干预; 阻碍; 出面; 插嘴\crr
\linetab{
    \relative
    \tword{intervention}{""Int@"venSn}{干预; 介入; 调解}
    \tword{interference}{""Int@"fIr@ns}{干涉; 介入; 冲突; 障碍物(noun.)}
    \tword{interfere}{""Int@r"fIr}{干涉; 打扰; 调停; 排解(verb.)}
}
lawsuit & "lO""sut & noun. & 诉讼\crr
neural & "nUr@l & adj. & 神经的\crr
\linetab{
    \relative
    \tword{neutral}{"nutr@l}{中立的; 不带电的; 中性的(adj.) 中立人士; 中立国; 空挡位置(noun.)}
    \tword{neutralization}{""nutr@lI"zeS@n}{中立化}
    \tword{neutralize}{"nutr@laIz}{使中立化}
    \tword{neutrality}{nu"tr\ae l@ti}{中性; 中立}
    \tword{neutralism}{"njutr@lIz@m}{中立主义}
    \tword{neutralist}{"nutr@lIst}{中立主义者}
    \tword{neutron}{"nutrAn}{中子}
}
scandal & "sk\ae ndl & noun. & 丑闻; 丑行\crr
overstate & ""oUv\rse"stet & verb. & 夸大; 言过其实\crr
\linetab{
    \exx\eng We shouldn't overstate our past achievements.
}
philosophical & ""fIl@"sAfIcl & adj. & 哲学的; 达观的\crr
preconception & ""prik@n"sEpS@n & noun. & 事先形成的看法; 先入之见; 成见\crr
\linetab{
    \exx\eng Preconception is an important factor to misconception.
}
progress & "prAgres & noun.\newline verb. & 进步; 发展\newline 发展; 促进; 增进\crr
\linetab{
    \relative
    \tword{progression}{pr@"grES@n}{进步; 发展}
}
whistle & "wIsl & noun.\newline verb. & 哨子; 口哨; 口哨声; 汽笛声\newline  吹口哨; 鸣汽笛\crr
\linetab{
    \exx\eng In that fight, whistle-blowers have become an essential source on
    insider information.
    \relative
    \tword{whisper}{"hwIsp\rse}{耳语; 低声的说(verb. noun.)}
    \tword{wrinkle}{"rINk@l}{皱纹; 起皱纹(verb. noun.)}
    \tword{wrestle}{"rEs@l}{摔跤(verb. noun.)}
    \tphrase{wrestle with}{绞尽脑汁}
}
proverb & "prAv\rse b & noun. & 谚语; 格言\crr
representational & ""rEprIzEn"teS@n@l & adj. & 具象派的\crr
umbrella & 2m"brEl@ & noun. & 雨伞\crr
special & "spES@l & adj.\newline noun. & 特殊的; 专门的; 专用的; 重要的\newline 专车; 特价; 特刊\crr
\linetab{
    \relative
    \tword{speciality}{""spESi"\ae lIti}{特长; 专长; 特制品}
    \tword{specialty}{"spES@lti}{特长; 专长(noun.) 特色的; 专门的(adj.)}
    \tword{specialize}{"spES@""laIz}{专攻; 特化; 使专门化; 详细说明}
    \tword{specialization}{""spES@lI"zeS@n}{专门化; 特殊化}
    \tword{species}{"spiSIz}{物种; 种类; 类型}
    \tword{specific}{spI"sIfIk}{具体的; 明确地; 特种的(adj.) 特效药; 特效; 细节(noun.)}
    \tword{specification}{""spEs@fI"keS@n}{说明书; 规格; 详述}
    \tword{specimen}{"spEs@m@n}{样品; 范例; 抽样; 某种类型的人}
    \tword{specious}{"spiS@s}{似是而非的(adj.) 似是而非地(adv.)}
    \tword{specify}{"spEs@""faI}{指定; 详述; 提出...地条件; 明确提出}
    \tword{conspecific}{""kAnspI"sIfIc}{同种的(植物,动物)}
    \tword{especially}{I"spES@li}{尤其; 特别; 专门}
}
stakeholder & "stekhoUld\rse & noun. & 利益相关者; 股东; 赌金保管者\crr
standardize & "st\ae nd\rse daIz & verb. & 使合乎标准; 使合规格\crr
stark & stArk & adj. & 完全的; 荒凉的; 光秃秃的; 僵硬的\crr
spook & spuk & noun.\newline verb. & 鬼; 幽灵; 间谍\crr
stuck & st2k & adj.\newline verb. & 卡住的; 动不了的; 受困的\newline 粘贴; 刺; 戳(stick的过去分词)\crr
\linetab{
    \tword{stick}{stIk}{粘贴; 刺; 戳; 容忍(verb.) 棍; 棒(noun.)}
    \tword{stack}{st\ae k}{堆; 垛; 干草堆(noun.) 使堆积(verb.)}
    \tword{stake}{stek}{股份; 桩; 重大利益(noun.) 用桩支撑(verb.)}
    \tword{stroke}{stroUk}{中风; 一击; 击球(noun.) 划掉; 轻抚; 击球}
}
conscious & "kAnS@s & adj. & 有意识的; 自觉地\crr
\linetab{
    \relative
    \tword{unconscious}{2n"kAnS@s}{无知觉的; 无意识的}
    \tword{consciousnesss}{"kAnS@sn@s}{意识; 感觉; 知觉}
    \tword{subconscious}{"s2b"kAnS@s}{潜意识}
    \texx{They vast majority of the brain's activity is subconscious.}
}
kitchen & "kItS@n & noun. & 厨房\crr
viable & "vaI@b@l & adj. & 可行的; 可实施的\crr
cease & sis & verb. & 停; 息; 停止\crr
\linetab{
    \exx\eng The Thudra Time, a weekly newspaper in Alaska,
    ceased publication this week.
    \relative
    \tword{grease}{gris}{动物油脂; 油膏; 润滑油; 贿赂(verb. noun.)}
    \tword{crease}{kris}{皱; 起皱; 弄皱(verb. noun.)}
}
situate & "sItSuet & verb. & 使位于; 使坐落于\crr
\linetab{
    \exx\eng First let us situate this discussion in the context of the recent 
    acheivements of neoroscience.
}
wage & wedZ & noun.\newline verb. & 工资\newline 发动\crr
weary & "wIri & adj.\newline verb. & 疲倦的; 厌烦的\newline 使厌烦; 厌烦\crr
whirl & w\rse l & verb.\newline noun. & 使回旋; 使旋转\newline 一连串的事; 混乱; 尝试\crr
\linetab{
    \exx\eng He was whirl Anne around the floor.
}
chaos & "keAs & noun. & 混乱; 紊乱; 混沌世界\crr
harsh & hArS  & adj. & 刺耳的; 粗糙的; 严厉的\crr
\linetab{
    \exx\eng poet William Blake's harsh remarks against the mechanistic 
    worldview fo Isaac Newton.
}
leadrship & "lid\rse SIp & noun. & 领导才能; 领导地位\crr
\linetab{
    \exx\eng Research has found that IQ predicted leadership skills
    with the tests were given under low-stress conditions.
}
leisure & "liZ\rse & noun. & 空闲; 闲暇\crr
\linetab{
    \exx\eng It was specifically to provide city dwellers with spaces
    for leisure where tyey could experience a refreshing air.
}
partial & "pArSl & adj. & 部分的; 偏袒的\crr
\linetab{
    \relative
    \tword{impartial}{Im"pArSl}{公平的; 无偏见的}
}
mature & m@"tSU\rse & adj.\newline verb. & 成熟的; 到期的; 充分考虑的\crr
\linetab{
    \exx\eng Girls mature ealier than boys.
}
pessimistic & ""pesI"mIstIk & adj. & 悲观的; 厌世的\crr
\linetab{
    \exx\eng In pessimistic forecasts of the impact of climate change, 
    the cost to adapt to a warming planet will eventually be huge.
    \relative
    \tword{optimistic}{""AptI"mIstIk}{乐观的}
}
lifelike & "laIf""laIk & adj. & 逼真的; 生动的; 栩栩如生的\crr
\linetab{
    \exx\eng The mask was so lifelike it was quite frightening.
}
sense & sEns & noun. & 感觉\crr
\linetab{
    \relative
    \tword{sensible}{"sEns@b@l}{能感觉的; 明智的}
    \tword{sensibility}{""sEns@"bIlIti}{敏感性; 感情}
    \tword{sensitive}{"sEns@tIv}{敏感的}
    \tword{sensory}{"sEns@ri}{感觉的; 知觉的}
    \tword{sentimental}{""sEntI"mEntl}{多感情的; 感伤的; 多愁善感的}
}
tolerate & "tAl@ret  & verb. & 容忍; 宽容\crr
\linetab{
    \exx\eng Their capicity for tolerating stress may even be greater than men's.\newline
    \eng Americans are willing to tolerate time-consuming security protocols 
    in return for increased safety.
}
protocol & "proUt@kOl & noun. & 外交礼节; 礼仪; 协定书; 协议\crr
polite & p@"laIt & adj. & 有礼貌的; 有教养的; 客套的; 应酬的; 上流社会的\crr
denote & dI"noUt & verb. & 表示; 代表\crr
donate & "doUnet & verb.\newline noun. & 捐赠; 捐献\crr 
eminent & "Em@n@nt & adj. & 著名的; 非凡的; 杰出的\crr
\linetab{
    \exx\eng Even the most eminent doctor could not cure him.
    \relative
    \tword{eminence}{"Em@n@ns}{杰出; 著名}
    \tword{imminent}{"ImIn@nt}{急迫的; 即将来临的}
    \tword{preeminent}{pri"Em@n@nt}{卓越的; 杰出的(adj.) 卓越地; 杰出地(adv.)}
    \tword{prominent}{"prAmIn@nt}{突出的; 显著的}
    \tword{prominence}{"prAmIn@ns}{杰出; 突出; 声望}
}
gradual & "gr\ae dZu@l  & adj. & 逐渐的; 逐步的; 渐进的\crr
immerse & I"m\rse s  & verb.  & 陷入; 沉浸于\crr
\linetab{
    \exx\eng I immerse myself in my career.
}
clockwise & "klAkwaIz & adj.\newline adv. & 顺时针的\newline 按顺时针地\crr
counterclockwise & ""kaUt"klAkwaIz & adj.\newline adv. & 逆时针的\newline 按逆时针地\crr
likewise & "laIk""waIz & adv. & 同样地; 照样地\crr
\linetab{
    \exx\eng You must pack plenty of food. Likewise you need warm clothes.
}
designate & "dEzIg""net & verb.\newline adj. & 指定; 标明; 选派\newline 指定而未上任的\crr
\linetab{
    \exx\eng It is the first worldwide epidemic dessignated by the world
    Health Organization in 41 years.
}
toll & toUl & noun.\newline verb. & 伤亡人数; 通行费; 钟声\newline 敲钟\crr
claim & klem & noun.\newline verb. & 要求; 主张; 声称; 索取; 申领; 夺走\crr
\linetab{
    \exx\eng This illness can claim a child's life.
    \relative
    \tword{proclaim}{pr@"klem, prO-}{声明; 宣布; 赞扬; 称颂}
    \tword{disclaim}{dIs"klem}{否认; 放弃}
    \tword{exclaim}{Ik"sklem}{呼喊; 大声说}
    \tword{reclaim}{rI"klem}{撤回}
    \tword{allege}{@"lEdZ}{声称; 断言; 辩解}
    \tword{allegation}{""\ae lI"geS@n}{断言; 辩解; 指控(noun.)}
    \texx{
        Hearing allegations of cruelty to animals in research settings,
        many are perplexed that anyone would 
        deliberately harm an animal.
    }
}
perplex & p@r"pleks & verb. & 使迷惑; 使混乱\crr
margin & mAr"dZ@n & noun.\newline verb. & 边缘; 旁注; 利润; 极限\newline 为...加旁注; 留边; 成为...的边\crr 
\linetab{
    \relative
    \tword{marginalize}{"mArdZIn@laIz}{使边缘化; 忽略; 排斥}
}
bore & bOr & noun.\newline verb. & 钻孔; 使人讨厌的人\newline 开凿; 钻孔; 使厌烦\crr
genius & "dZinj@s & noun. & 天才; 天赋\crr
incur & In"k\rse & verb. & 遭受; 招致\crr
\linetab{
    \exx\eng His unfriendly words incur my anger.\newline
    \eng His speech will incur hostility from the enemies.
}
glowing & "gloUiN & adj. & 热情的\crr
glowingly & "gloUiNli & adj. & 热情地; 热心地\crr
signature & "sIgn@tS\rse & noun. & 签名\crr
addict & @"dIkt & noun.\newline verb. & 瘾君子; 入迷的人\newline 使沉溺; 使上瘾\crr
\linetab{
    \relative
    \tword{addictive}{@"dIktIv}{上瘾的}
    \tword{addiction}{@"dIkS@n}{上瘾; 沉溺; 嗜好}
}
brace & bres & noun.\newline verb. & 支撑物; 支架; 一对\newline 支撑; 绷紧; 紧靠; 准备好\crr
fortune & fOrtS@n & noun. & 命运; 财产; 运气\crr
compatible & k@m"p\ae t@b@l & adj. & 兼容的; 可和谐共存的\crr
\linetab{
    \relative
    \tword{compat}{k@m"p\ae t}{兼容性}
    \tword{incompatible}{""Ink@m"p\ae t@b@l}{不兼容的}
    \tword{compact}{"kAm"p\ae kt}{\noindent\vtop{\ adj.\quad 紧凑的; 简洁的\newline
                                                verb.\quad 压紧; 使变紧; 简洁; 简化\newline
                                                noun.\quad 协议; 条约; 小汽车; 带镜小粉盒}}
}
virtual & "v\rse tSu@l & adj. & 几乎的; 虚拟的(计算机用语)\crr
\linetab{
    \exx\eng Compare the explosion and accessibility of digital information with
    the establishment of automobile use as a virtual necessity.
}
comment & "kAnmEnt & verb.\newline noun. & 评论; 表达意见\newline 评论; 意见; 批评\crr
commend & k@"mEnd & verb. & 表扬; 推荐; 托付; 收到赞同\crr
\end{engvc}

\begin{engvc}[18-9-15]
revolutionary & rEv@"luS@n@ri & adj. & 革命的; 改革性的\crr
subject & "s2bdZEkt & noun.\newline adj.\newline verb. & 学科; 主题; 对象; 话题\newline 受...支配的; 受制于...的; 易患...的\newline 提供; 使屈从; 使附属\crr
\linetab{
    \exx\eng At the very least, the court should make itself subject to the code of conduct
    that applies to the rest of the federal judiciary.\newline
    \eng The area is subject to devastating seasonal winds.
}
renewable & rI"nu""@bl & adj. & 可更新的; 可再生的\crr
crow & kroU & noun.\newline verb. & 乌鸦; 雄鸡的啼声\newline 打鸣; 啼叫; 欢叫; 自鸣得意\crr
\linetab{
    \relative
    \tword{crown}{kraUn}{王冠}
    \tword{crew}{kru}{全体人员}
    \tword{clown}{klaUn}{小丑}
    \tword{chew}{tSu}{嚼}
    \exx\eng The cock crows and the dawn chorus begins.\tword{chorus}{"kOr@s, "kor-}{合唱; 合唱歌}
    \eng We've seen them all crowing that the movement is dead.
}
outrage & "aUt"rEdZ & noun.\newline verb. & 暴行; 愤怒; 愤慨\newline 激怒; 使震怒\crr
\linetab{
    \exx\eng Indeed, if he has a reputation for slacking, you might even be outraged.
}
comply & k@m"plaI & verb. & 顺从; 遵守\crr
speculate & "spEkj@""let & verb. & 推测; 思索; 投机\crr
\linetab{
    \exx\eng It would be pointless to specualte without any proof.
    \relative
    \tword{spectacle}{"spEkt@k@l}{景象; 奇观; 场面}
}
concise & k@n"saIs & adj. & 简明的; 简要的\crr
indifferent & In"dIf@r@nt & adj. & 漠不关心的\newline 不注意的\crr
\linetab{
    \exx\eng His English is indifferent.
}
priority & praI"Or@ti & noun. & 先; 前; 优先权; 需优先考虑的事\crr
statute & "st\ae tSut & noun. & 法令; 法规; 条例\crr
\linetab{
    \relative
    \tword{state}{stet}{州; 国家; 情况; 资格(noun.)\newline 陈述; 说明(verb.)\newline 国家的; 正式的(adj.)}
    \tword{statue}{"st\ae tSu}{雕像; 雕塑(noun.)\newline 用雕像装饰(verb.)}
    \tword{status}{"st\ae tS, "stets}{地位; 身份; 情形; 状态}
}
tactics & "t\ae ktIks & noun. & 策略; 战术\crr
\linetab{
    \relative
    \tword{tactic}{"t\ae ktIk}{按顺序的; 依次排列的(adj.)\newline 策略; 战术(noun.)}
    \tword{tactical}{"t\ae ktIk@l}{战术的; 策略的; 善于策略的}
    \tword{tactician}{t\ae k"tIS@n}{战术家; 谋士}
}
architect & "ArkItekt & noun. & 建筑师; 创制者; 设计者\crr
grain & gren & noun. & 谷物; 颗粒\crr
preach & pritS & verb. & 宣扬; 鼓吹; 布道\crr
\linetab{
    \exx\eng We preach freedom around the world.\par
    \eng Self-help books preach the life-changing benefits of happiness.\tphrase{self-help book}{励志书籍}
}
reverse & rI"v\rse s & verb.\newline noun.\newline adj. & 使倒转; 使颠倒; 倒车; 撤销\newline 反面\newline 背面\crr
\linetab{
    \exx\eng Anyone can see this trend is unsustainable. Yet few seem willing to try to reverse it.
}
recurse & rI"k\rse s & verb. & 递归\crr
\linetab{
    \relative
    \tword{recursion}{"rIk\rse S@n}{递归; 递归表达式}
    \tword{iteration}{""It@"reS@n}{重复; 反复; 迭代}
}
precedent & "prEsId@nt & noun. & 先例; 前例\crr
susceptible & s@"sEpt@b@l & adj. & 易受影响的\newline 易动感情的; 易受感染的\crr
\linetab{
    \relative
    \tword{sensitive}{"sEnsItIv}{敏感的}
    \tword{accessible}{\ae k"sEs@b@l}{易接近的; 可进入的; 可理解的}
    \tword{impressionable}{Im"prES@n@b@l}{敏感的; 易受影响的}
    \tword{vulnerable}{"v2ln@r@b@l}{易受伤害的}
}
proposal & pr@"poUzl & noun. & 建议; 提案; 求婚\crr
somewhat & "s2mw2t & adv. & 有点; 稍微\crr
hike & haIk & noun.\newline verb. & 徒步旅行; 远足; 升起; 增加\newline 徒步旅行; 远足; 升起; 增加\crr
orient & "OrI@nt & noun.\newline adj.\newline verb. & 东方\newline 东方的\newline 使适应\crr
council & "kaUns@l & noun. & 居委会; 政府服务机构\crr
dictate & "dIktet & verb.\newline noun. & 听写; 口述; 要求\newline 命令; 指令; 指示\crr
\linetab{
    \exx\eng I had not realised how profoundly marketing trends 
    dictated our perception of what is natural to kids.
}
profoundly & pr@"faUndli & adv. & 深深地; 深刻地\crr
disastrous & dI"z\ae str@s & adj. & 灾难性的\crr
\end{engvc}

\begin{engvc}[18-9-16]
waken & "we.k@n & verb. & 醒来； 唤醒\crr
\linetab{
    \relative
    \tword{rouse}{raUz}{主动时态时, 强调弄醒别人的努力\newline 被动语态时, 指轻而易举的醒过来}
    \tword{arouse}{@"raUz}{一般的唤醒}
    \tword{awake}{@"kek}{真正的醒来; 可以用做及物动词和不及物动词}
    \tword{waken}{"wek@n}{唤醒; 使觉醒}
}
tedious & "ti\sepe di\sepe @s & adj. & 冗长的; 沉闷的\crr
ash & \ae S & noun. & 灰烬\crr
deceit & dI\sepe sit & noun. & 欺骗; 欺诈\crr
exempt & Ig"zEmpt & adj.\newline verb. & 被免除的; 被豁免的\newline 免除; 豁免\crr
\linetab{
    \exx\eng exempt from conviction on the charge of favoritism.
}
visionary & "vIZ@neri & adj.\newline noun. & 幻想的; 有远见的\newline 空想家; 有远见的人\crr
\linetab{
    \exx\eng The second half of the 20th century saw a collection of geniuses,
    warriors and visionaries labor to create a fabulous machine.
}
lion & "laI@n & noun. & 狮子\crr
\linetab{
    \relative
    \twocol{
    \tword{horse}{"hOrs}{马}
    \tword{bear}{ber}{熊}
    \tword{bee}{bi}{蜜蜂}
    \tword{bird}{b3rd}{鸟}
    \tword{dog}{dOg}{狗}
    \tword{tiger}{"taIg\rse}{老虎}
    \tword{elephant}{"El@f@nt}{大象}
    \tword{rabbit}{"raIbIt}{兔子}
    \tword{chick}{tSIk}{小鸡}
    \tword{starfish}{"stArfIS}{海星}
    \tword{swan}{swAn}{天鹅}
    \tword{cock}{kAk}{雄鸡}
    \tword{owl}{aUl}{猫头鹰}
    }{
    \tword{hawk}{hOk}{鹰}
    \tword{hen}{hEn}{母鸡}
    \tword{fish}{fIS}{鱼}
    \tword{cat}{k\ae t}{猫}
    \tword{kitten}{"kItn}{小猫}
    \tword{panda}{"p\ae nd@}{熊猫}
    \tword{rat}{raIt}{耗子}
    \tword{snake}{snek}{蛇}
    \tword{ox}{Aks}{公牛}
    \tword{sheep}{Sip}{羊}
    \tword{lamb}{l\ae m}{羊羔}
    \tword{monkey}{"m2Nki}{猴子}
    \tword{pig}{pIg}{猪}
    }
}
essay & "Ese & noun.\newline verb. & 散文; 文章\newline 尝试; 企图\crr
horn & hOrn & noun. & 号角; 喇叭\crr
locality & lO"k\ae l@ti & noun. & 地点; 地区\crr
tame & tem & adj.\newline verb. & 养训的; 顺从的; 枯燥无味的\newline 驯养; 驯服; 使变得平淡\crr
anxiety & \ae N"zaI@ti & noun. & 忧虑; 焦虑; 渴望\crr
\linetab{
    \exx\eng What's the origin of your anxiety?\newline
    \eng Anxiety aged her overnight.
}
adjoin & @"dZOin & verb. & 临近; 毗邻\crr
blossom & "blAs@m & verb.\newline noun. & 开花; 繁荣; 兴旺; 长成\newline 花; 群花; 开花时期; 兴旺时期\crr
vaccine & v\ae k"sin & noun. & 疫苗\crr
vaccum & "v\ae kjUm & noun.\newline verb.\newline adj. & 真空; 空虚\newline 用真空吸尘器打扫\newline 真空的\crr
intrude & In"trud & verb. & 闯入; 打扰; 强使\crr
\linetab{
    \exx\eng Arizona had thus intruded on the federal's privileged power.
}
estate & I"stet & noun. & 庄园; 财产; 房地产\crr
\linetab{
    \exx\eng property estate bubble.\newline
    \eng His estate was divided among the children.
}
excerpt & "Eks\textrhookrevepsilon pt & noun.\newline verb. & 摘录; 摘要\newline 摘录; 引用\crr
aural & "Or@l & adj. & 听觉的; 听的\crr
imprison & Im"prIz@n & verb. & 监禁; 束缚\crr
\linetab{
    \exx\eng You can imprison my body but not my mind.\lower2.5ex\hbox{\quad-- I only need your body, LOL.}
}
scare & sker & verb.\newline noun.\newline adj. & 使惊恐; 使惊吓\newline 恐慌; 恐惧\newline 骇人的; 令人恐惧的\crr
\linetab{
    \relative
    \tword{scar}{skAr}{\vtop{noun.\quad 伤疤; 精神上的创伤; 有损伤外观的地方; 断崖\newline verb.\quad 结疤; 留下伤疤}}
    \tword{scary}{"skeri}{使人惊慌的; 胆小的; 可怕的}
    \tword{scarecrow}{"skercroU}{(在田里吓鸟)稻草人; 邋遢的人; 骨瘦如柴的人}
    \tword{sacred}{"sekrId}{宗教的; 神圣的; 庄严的}
}
embody & Im"bAdi & verb. & 体现; 使具体化; 包含\crr
\linetab{
    \exx\eng The proposal has been embodied in a draft resolution.
    \relative
    \tword{embodiment}{Im"bAdim@nt}{体现; 具体化; 化身}
}
reptile & "rEptaIl & noun.\newline adj. & 爬行动物\newline 爬虫类的\crr
shortlist & "SOrtlIst & noun.\newline verb. & 最后候选人名单\newline 把...列入最后候选人名单\crr
birthright & "b@T""raIt & noun. & 与生俱来的权利\crr
couragous & k@"redZ@s & adj. & 勇敢的\crr
poach & poUtS & verb. & 水煮; 偷猎; 盗用\crr
\linetab{
    \exx\eng Exectives and headhunters have adhered to the rule that 
    the most attractive CEO candidates are the ones who must be poached.
}
scanty & "sk\ae nti & adj. & 欠缺的; 过小的; 少量的\crr
\linetab{
    \relative
    \tword{scant}{sk\ae nt}{不足的; 少量的(adj.) 限制; 节省; 吝惜(verb.)}
    \texx{This hole was a scant .23 inches in diameter.}
}
closet & "klAzIt & noun.\newline adj. & 壁橱; 储藏室\newline 隐藏的\crr
psychoactive & ""saIkoU"\ae ktIv & adj. & 作用于心灵的; 影响精神的\crr
\linetab{
    \relative
    \tword{psyche}{"saIki}{精神; 灵魂}
    \tword{psychic}{"saIkIk}{精神的(adj.) 通灵的人(noun.)}
    \tword{psychiatric}{""saIki"\ae trIk}{精神病学}
    \tword{psychiatrist}{""saIkI"\ae trIst}{精神病科医生}
    \tword{psycho}{"saIkoU}{精神病患者(noun.) 发疯的(adj.)}
    \tword{psychology}{saI"kAl@dZ}{心理学}
    \tword{psychological}{saI"kAl@dZIkl}{心理学的}
    \tword{psychologist}{saI"kAl@dZIst}{心理学家}
    \tword{psychoanalysis}{""saIkoU@"n\ae l@sIs}{精神分析}
}
yearning & "j\rse niN & noun.\newline adj.\newline verb. & 渴望; 向往\newline 渴望的; 向往的\crr
\linetab{
    \relative
    \tword{yearn}{j3rn}{渴望; 渴求; 向往; 怀念}
    \texx{Is it not in the nature of all human beings to yearn for freedom?}
}
abolish & @"bAliS & verb. & 取消; 废除; 废止\crr
\linetab{
    \exx\eng It takes a very long time to abolish classes.
}
neglect & nI"glEkt & verb. & 疏忽; 忽略\crr
\linetab{
    \relative
    \tword{negligible}{"nEglIdZ@b@l}{微不足道的; 无足轻重的}
    \tword{negligence}{"nEglIdZ@ns}{疏忽; 过失; 失职}
}
identification & aI""dEnt@fI"keS@n & noun. & 识别; 鉴定; 身份证明\crr
\linetab{
    \relative
    \tword{identify}{aI"dEntI""faI}{识别; 鉴定; 确定}
    \tword{identity}{aI"dEntIti}{身份; 恒等式}
    \tword{identical}{aI"dEntIcl}{相同的}
}
obscure & @b"skjUr & adj.\newline verb. & 昏暗的; 不清楚的; 无名的\crr
\linetab{
    \exx\eng The legal issues in the case are obscure.\newline
    \eng Yes, there are preils. But they should not obscure the huge benefits
    from the dawn of AI.
}
upscale & "2p""skel & adj. & 高消费的; 高档的\crr
\linetab{
    \exx\eng Journalists are more likely to live in upscale
    neighborhoods, have maids, own Mercedeses, and trade stocks.
}
dazzle & "d\ae z@l & verb.\newline noun. & 使目眩; 使眼花; 使惊叹\newline 耀眼; 眩惑; 灿烂\crr
serious & "sIri@s & adj. & 严肃的; 严重的; 庄重的; 认真的\crr
\linetab{
    \tword{earnest}{"3rnIst}{热心的; 真诚的; 重要的(adj.) 认真; 诚挚; 热心(noun.)}
    \tword{grave}{grev}{\vtop{  adj.\quad 严重的; 沉重的; 重大的\newline
                              \ adv.\quad 严重地; 沉重地; 极慢地\newline
                               noun.\quad 墓穴; 墓地; 下场; 死亡\newline
                               verb.\quad 雕刻; 铭记}}
    \texx{The magazine isn't trying to ruin his career, the man is digging his own grave by refusing an interview.}
    \tword{severe}{sI"vIr}{严峻的; 严厉的; 剧烈的; 苛刻的}
    \tword{solemn}{"sAl@m}{庄严的; 神圣的; 犹豫的; 阴沉的}
    \tword{sober}{"soUb@}{\vtop{\ adj.\quad 头脑清醒的; 没醉的; 有节制的\newline verb.\quad 冷静; 清醒; 使严肃}}
}
accommodate & @"kAm@det & verb. & 容纳; 为...提供住宿; 适应\crr
beast & bist & noun. & 兽; 凶残的人\crr
setback & "sEt""b\ae & noun. & 退步; 挫折\crr
immemorial & ""Im@"mOri@l & adj. & 古老的; 远古的\crr
memorandum & ""mEm@"r\ae nd@m & noun. & 备忘录; 便签\crr
significant & sIg"nIfIk@nt & adj. & 有意义的; 重大的\crr
simple & "sImp@l & adj. & 简单的; 朴素的; 单纯的\crr
\linetab{
    \tword{sample}{"s\ae mpl}{样本}
    \tword{simply}{"sImpli}{仅仅}
    \tword{simplify}{"sImpl@""faI}{简化}
    \tword{simplification}{""sImpl@f@"keS@n}{简单化}
}
bacterium & b\ae k"tIri@m & noun. & 细菌\crr
\linetab{
    \tword{germ}{dZ\rse m}{病菌; 萌芽}
    \tword{virus}{"vaIr@s}{病毒}
    \tword{fungus}{"f2Ng@s}{霉菌; 菌类; 真菌}
}
affiliate & @"fIli""et & verb.\newline noun. & 隶属于; 并入; 联合\newline 分公司; 附属机构\crr
\linetab{
    \exx\eng International affiliate account for a fast-growing segment of production in economies
    that open up.\newline
    \eng All youth groups will have to affiliate to the National Affiliate Agency.
}
subsidiary & s@b"sIdI\rse li & adj.\newline noun. & 辅助的; 附属的; 次要的\newline 附属事物; 附属公司\crr
chef & SEf & noun. & 主厨; 厨师长\crr
encounter & In"kaUnt\rse & verb.\newline noun. & 遭遇; 遇到; 邂逅\newline 遭遇; 遭遇站\crr
\linetab{
    \exx\eng Women are outliving men in every country in the world, 
    despite facing greater odds of encountering sexual violence.
}
militant & "mIlIt@nt & adj.\newline noun. & 激进的; 好战的\newline 激进; 好战\crr
\linetab{
    \exx\eng Our contry's education system is in grips of people who 
    "joyfully and militantly proclain their hostility to intellect ..."
}
awkward & "Okw\rse d & adj. & 笨拙的; 别扭的; 难堪的\crr
respective & rI"spektIv & adj. & 各自的; 各个的\crr
\linetab{
    \exx\eng They are recognized as specialists in their respective fields.
}
proposition & ""prAp@"zISn & noun. & 命题; 建议; 主张\crr
\linetab{
    \relative
    \tword{propose}{pr@"poUz}{提议; 求婚; 举荐}
    \tword{proposal}{pr@"poUzl}{建议; 提案; 求婚}
    \tword{preposition}{""prEp@"zISN}{介词}
}
nervous & "n\rse v@s & adj. & 担忧的; 焦虑的; 紧张不安的; 神经系统的\crr
bewilder & bI"wIld\rse & verb. & 使迷惑; 使...不知所措\crr
\linetab{
    \exx\eng My colleagues were bewildered by people who refused to act 
    in accord with scientific recommendation.
}
bibliography & ""bIbli"Agr@fi & noun. & 参考书目; 书籍学; 文献学\crr
biography & baI"Agr@ri & noun. & 传记\crr
\linetab{
    \exx\eng A biography is a form of narration.
}
comet & "kAm@t & noun. & 彗星\crr
applause & @"plOz & noun. & 鼓掌; 喝彩\crr
installaton & ""Inst@"leS@n & noun. & 安置; 装置物\crr
liner & "laIn\rse & noun. & 邮轮; 客轮\crr
cheif & tsIf & adj.\newline noun. & 主要的; 级别高的; 最重要的\newline 首长; 酋长\crr
embark & Im"bArk & verb. & 上船; 上飞机; 从事\crr
glory & "glOri & noun. & 荣誉; 光辉\crr
pest & pEst & noun. & 害虫; 令人讨厌的物\crr
\linetab{
    \relative
    \tword{pesticide}{"pEstI""saId}{杀虫剂}
    \tword{paste}{pest}{浆糊; 酱(noun.) 张贴; 黏贴(verb.)}
}
infant & "Inf@nt & noun.\newline adj. & 婴儿; 幼儿\newline 婴儿的; 幼儿的; 初期的\crr
relish & "rElIS & verb.\newline noun. & 喜欢; 享受; 从...获得乐趣\newline 享受; 乐趣; 调味品\crr
bolt & boUlt & noun.\newline verb. & 插销; 螺栓; 闪电\newline 用插销栓上\crr
\linetab{
    \exx\eng Her dismissal came as a bolt from the blue.\newline
    \eng But bolting on security after the fact is much harder than 
    building it in from the start.
}
abdomen & "\ae bd@m@n & noun. & 腹部\crr
facilitate & f@"sIl@""tet & verb. & 使容易; 使便利; 促进; 帮助\crr
\linetab{
    \exx\eng It facilitates public investment in scientific research.
    \relative
    \tword{facile}{"f\ae sl}{容易做的; 轻率做出的; 轻易可得的}
    \tword{facility}{f@"sI@@ti}{便利; 设备; 能力}
    \tword{factor}{"f\ae kt\rse}{\vtop{noun.\quad 要素; 动力; 因子\newline verb.\quad 把...考虑进去; 作代理商}}
    \tword{benefactor}{"bEn@""f\ae kt\rse}{捐助者; 恩人}
    \tword{benefaction}{"bEn@""f\ae kS@n}{善事; 恩惠}
}
waist & west & noun. & 腰\crr
\linetab{
    \relative
    \tword{wrist}{rIst}{腕部}
    \tword{breast}{brEst}{\vtop{noun.\quad 胸; 胸怀; 乳房\newline verb.\quad 升高; 攀登; 与...搏斗}}
}
\end{engvc}

\begin{engvc}[18-9-17]
magnify & "m\ae gn@fai & verb. & 放大; 扩大; 夸大\crr
\linetab{
    \exx\eng image we present is magnified by social-media services.
}
abide & @"baId & verb. & 遵守; 服从; 容忍; 忍受; 居住; 逗留\crr
\linetab{
    \exx\eng I cannot abide such a loud noise.
}
outbreak & "aUt""brek & noun. & 爆发; 发作\crr
expend & Ik"spEnd & verb. & 花费; 消耗\crr
\linetab{
    \exx\eng You expand so much effort for so little return.
}
gigantic & dZaI"g\ae ntIk & adj. & 巨大的; 庞大的\crr
occupy & A"kjupaI & verb. & 占领; 从事; 使用; 任职\crr
\linetab{
    \relative
    \tword{occupation}{""Akju"peSn}{占领; 占有; 职业; 消遣}
    \texx{You discover that we are in a period of unprecedented calm with comparatively
    few jobs shifting between occupations.}
    \tword{occupied}{"AkjupaId}{已占有的; 无空闲的; 使用中的}
    \tword{occupancy}{""Akj@p@nsi}{居住; 占有; 占用}
    \tword{occupant}{"Akj@p@nt}{居住人; 占有者}
}
massacre & "m\ae s@ k\rse & verb.\newline noun. & 屠杀\newline 大屠杀\crr
trace & tres & noun.\newline verb. & 痕迹; 轨迹; 微量\newline 追踪; 追溯; 找出根源\crr
\linetab{
    \exx\eng One difficulty is that almost all of what is called behavioral science 
    coutinues to trace behavior to state of mind.
}
unprecedented & 2n"prEsI""dEntId & adj. & 前所未有的; 空前的; 崭新的\crr
avert & @"v\rse t & verb. & 转开; 避免; 防止\crr
\linetab{
    \exx\eng The government fail to avert a national strike.
}
utilize & "juti""aIz & verb. & 利用\crr
\linetab{
    \relative
    \tword{utility}{ju"tIl@ti}{效用; 有用的物体或器械}
    \texx{%
        1. Belief in utility of higher education is shared by students nationwide.\newline
        2. The utility was entering a new and uncharted territory.\newline
        3. The ware is suitable for decorative purpose but unsuitable for utility.
    }
    \tword{utilization}{""jutIlaI"zeS@n}{利用; 效用}
    \texx{
        1. Computers are found an increasely wide utilization in all fields.\newline
        2. Some of characters and questionn on the current utilization of 
           resources were dicussed and analysed.
    }
    \tword{utilitarian}{""jutIlI"teri@n}{实用的; 功利的(adj.) 功利主义者; 实用主义者(noun.)}
}
meantime & "min""taIn & adv.\newline noun. & 与此同时\newline 其间; 其实\crr
offend & @"fEnd & verb. & 冒犯; 得罪; 违反; 犯罪\crr
dimension & dI"mEnS@n & noun. & 尺寸; 维度\crr
venture & "vEntS\rse & verb.\newline noun. & 冒险; 投机\newline 冒险事业; 商业冒险; 投机\crr
\linetab{
    \exx\eng May I venture to suggest a change.
}
therapy & "TEr@pi & noun. & 治疗; 疗法\crr
\linetab{
    \exx\eng In therapy, she began to go of her obsession with Mike.
}
ventilate & vEntIlet & verb. & 使通风; 公开表达\crr
\linetab{
    \exx\eng He began to ventilate his opinion angrily.\newline
    \eng He did not think it is the job of officals to ventilate their doubts and daydreams.
}
justify & "dZ2st@"fai & verb. & 替...辩护; 证明...正当\crr
\linetab{
    \exx\eng Dno't try to justify your mistakes.
}
masterpiece & "m\ae st\rse pis & noun. & 杰作; 名著\crr
decisive & dI"saIsIv & adj. & 决定性的\crr
weld & wEld & verb.\newline noun. & 焊接\newline 焊接\crr
\linetab{
    \relative
    \tword{wild}{waIld}{野生的; 野蛮的}
    \tword{wield}{wIld}{使用; 行使; 施加}
}
journey & "dZ\rse ni & noun. & 旅行; 旅程\crr
\linetab{
    \relative
    \tword{journal}{"dZ\rse n@l}{杂志}
    \tword{journalist}{"dZ\rse n@lIst}{新闻记者}
    \tword{journalism}{"dZ\rse n@lIz@m}{新闻业}
}
rally & "r\ae li & verb.\newline noun. & 集合起来; 振作; 复苏\newline 集会\crr
\linetab{
    \exx\eng At ralies and in town hall meetings, liberal Democrats have pressed 
    lawmakers to support the creation of a single-payer system.\newline
    \eng The defense of the Church became a rallying cry for the conervative forces.
}
illusion & I"lud@n & noun. & 错觉; 幻觉\crr
illusionary & I"lud@neri & adj. & 错觉的; 幻影的\crr
majority & m@"dZOr@ti & noun. & 大多数; 大部分\crr
\linetab{
    \relative
    \tword{minority}{maI"nOr@ti}{少数; 少数民族; 未成年}
    \tword{major}{"medZ@}{主要的(adj.) 主修科目(noun.) 兼修(verb.)}
    \tword{minor}{maIn\rse}{次要的; 未成年的; 辅修的}
}
lag & l\ae g & verb.\newline noun. & 缓慢移动; 滞后\newline 时间间隔\crr
genre & "ZAnr@ & noun. & 类型; 体裁\crr
\linetab{
    \exx\eng My favorite music genre is blues.
}
savage & "s\ae wIdZ & adj.\newline noun.\newline verb. & 野性的; 凶猛的; 荒野的\newline 野蛮人; 粗人; 凶猛的人\newline 凶狠的攻击; 激烈抨击\crr
\linetab{
    \exx\eng He like savege mountain scenery.\newline
    \eng They look at an aranic being as a savage looks at a ship,
    as at something wholly beyong his comprehension.
}
quest & kwEst & verb.\newline noun. & 探求; 追求; 搜寻之物\newline 寻找; 进行探求\crr
worship & "w\rse SIp & noun.\newline verb. & 崇拜; 崇敬; 礼拜\newline 崇拜; 崇敬; 做礼拜\crr
\end{engvc}

\begin{engvc}[18-9-18]
bellicose & "belIkoUs & adj. & 好战的； 好斗的\crr
flap & fl\ae p & noun.\newline verb. & 扁平物; 拍打; 拍打声; 不安; 恐慌\newline 轻拍; 摆动\crr
trump & tr2mp & noun.\newline verb. & 王牌\newline 胜过\crr
terrace & "tErIs & noun. & 阳台; 台阶\newline 把...修成梯田\crr
gospel &  "gAspl & noun.\newline adj. & 福音; 真理; 信条\newline 传播福音的\crr
affinity & @"fInIti & noun. & 亲密关系; 吸引力; 类似; 近似\crr
chronic & "krAnIk & adj. & 慢性的; 长期的\crr
parallax & "p\ae r@"l\ae ks & noun. & 视差角度\crr
mop & mAp & noun.\newline verb. & 拖把\newline 擦拭\crr
mite & maIt & noun. & 小虫; 极少量; 小孩子\crr
denouement & ""denu"maN & noun. & 结局\crr
abet & @"bEt & verb. & 怂恿; 支持; 教唆\crr
fecund & "fEk@nd & adj. & 肥沃的; 富饶的; 多产的\crr
radish & "r\ae dIS & noun. & 小萝卜\crr
groggy & "grAgi & adj. & 不稳定的; 不会的; 摇摆的\crr
abridge & @"brIdZ & verb. & 缩短; 节略; 减少\crr
erect & I"rEkt & adj.\newline verb. & 使直立; 竖起来\newline 直立的; 垂直的\crr
glut & gl2t & verb.\newline noun. & 使吃饱; 过量地吃\newline 供过于求; 吃得过多\crr
coalesce & ""koU@"les & verb. & 联合; 合并\crr
inhibit & In"hIbIt & verb. & 抑制; 禁止\crr
fraud & faUd & noun. & 骗子; 欺诈; 冒牌货\crr
mantle & "m\ae ntl & noun.\newline verb. & 斗篷; 披风; 覆盖物\newline 覆盖\crr
deplete & dI"plit & verb. & 耗尽; 用尽; 减少; 损耗\crr
iconoclast & aI"kAn@kl\ae st & noun. & 攻击传统观念地人\crr
ingenious & In"dZinj@s & adj. & 精巧地; 灵巧的; 有天才的; 聪明的\crr
tremble & "trEmb@l & verb.\newline noun. & 发抖; 战栗\newline 发抖; 战栗\crr
deprecatory & ""depr@"ketli & adj. & 反对的; 不赞成的; 恳求的\crr
snuff & sn2f & verb. & 熄灭; 扑灭; 死去; 吸入\newline 烛花; 鼻烟; 气息\crr
oven & "2v@n & noun. & 烤炉; 烤箱\crr
choke & tSoUk & verb.\newline noun. & 哽咽; 阻塞; 遏止\newline 窒息; 哽咽; 阻塞\crr
refine & rI"faIn & verb. & 精炼; 使高雅; 改善\crr
audit & "OdIt & verb.\newline noun. & 审查; 查账; 审计\newline 审计; 查账\crr
\linetab{
    \exx\eng A bill in Congress cails for the Fed's decisions.
}
nectar & "nEkt\rse & noun.\newline adj. & 花蜜; 琼浆玉液\newline 充满美酒的\crr 
punch & p2ntS & verb. & 打孔; 穿孔\newline 冲床; 打孔器\crr
cargo & "kArgoU & noun. & 货物; 荷载; 荷重\crr
plough & plaU & noun.\newline verb. & 犁; 耕作; 耕地\newline 用梨耕田; 开路\crr 
chastise & tS\ae s"taIz & verb. & 严惩某人\crr
jack & dZ\ae k & verb.\newline noun. & 上升; 抬起\newline 千斤顶\crr
inflict & In"flIkt & verb. & 把...强加给; 使遭受\crr
luminous & "lum@n@s & adj. & 发光的; 明亮的; 清楚的\crr
ember & "Emb\rse & noun. & 余烬; 余火\crr
gloss & glOs & noun.\newline verb. & 光彩; 光泽\newline 给...加光泽\crr
ulcer & "2ls\rse & noun. & 溃烂\crr
spray & spre & verb.\newline noun. & 喷射; 喷\newline 喷雾; 浪花; 喷雾器\crr
quiescence &  kwI"esns & noun. & 静止\crr
quiver & kwI"v\rse & verb.\newline noun. & 微颤; 震动\newline 抖动; 颤音\crr
insular & "Ins@l@r & adj. & 孤立的; 与世隔绝的\crr
resin & "resn & noun.\newline verb. & 树脂; 合成树脂\newline 用树脂处理\crr
motile & "mo""taIl & noun.\newline adj. & 能动的; 显示活力的\newline 运动型\crr
stink & stInk & verb.\newline noun. & 发出恶臭; 找人厌恶\newline 恶臭; 难闻的气体\crr
oblivion & @"blIvi@n & noun. & 遗忘; 淹没; 赦免\crr
pendant & "pEnd@nt & noun. & 吊坠; 垂饰\crr
revise & rI"vaIz & verb. & 校阅; 修正; 温习; 改变\crr
\linetab{
    \exx\eng Los Angeles Unified are revising their thinking on this educational ritual.
}
monopoly & m@"nAp@li & noun. & 垄断\crr
\linetab{
    \relative
    \tword{monotony}{m@"nAt@ni}{单调}
    \tword{monologue}{"mAn@""lOg}{独白}
    \tword{monograph}{"mAn@gr\ae f}{专题论文}
    \tword{monogamy}{m@"nAg@mi}{一夫一妻制}
    \exx\eng Any threat of monoply, they argue, is removed by fierce 
    competition from trucks.
}
concerted & k@n"s\rse tId & adj. & 协同的; 共同的\crr
\linetab{
    \exx\eng with concerted efforts they pulled through the difficulties.
}
striker & "straIk\rse & noun. & 罢工者; 前锋\crr
juggle & "dZ2g@l & verb.\newline noun. & 玩杂耍; 耍花招; 欺骗\newline 玩杂耍; 花招; 骗局\crr
\linetab{
    \relative
    \tword{jungle}{"dZ2ng@l}{丛林}
}
assimilate & @"sIm@""let & verb. & 吸收; 消化; 使同化\crr
\linetab{
    \exx\eng China needs to assimilate a good deal of foreign progressive
    culture, but she must not swallow anything uncritically.
}
clue & klu & noun. & 线索; 提示\crr
arithmetic & @"rITm@tIk & noun. & 算术\crr
overlook & ""oUv\rse"lUk & verb. & 忽略; 俯视\crr
\linetab{
    \exx\eng We can overlook the scenery on the mountain through this window.
}
\end{engvc}

\begin{engvc}[18-9-19]
plague & pleg & noun.\newline verb. & 瘟疫； 疫病\newline 困扰; 折磨\crr
\linetab{
    \relative
    \tword{pledge}{plEdZ}{保证; 誓言; 许诺(verb. noun.)}
    \tword{plunge}{pl2ndZ}{用力插入; 使陷入; 跳入; 跳水(verb. noun.)}
    \exx\eng She was plagued by weakness, fatigue, dizziness.
}
reap & rip & verb. & 收割; 收获; 获得\crr
\linetab{
    \exx\eng You reap what you sow.\newline
    \eng For those that master the intricacies of wholesaleing is 
    Europe stand to reap condierable gains.
}
reccession & rI"sES@n & noun. & 后退; 不景气\crr
\linetab{
    \relative
    \tword{recess}{rI"sEs}{\vtop{verb.\quad 暂时休息; 休会; 制造凹陷\newline noun.\quad 休息; 隐蔽处; 凹处}}
    \tword{recede}{rI"sid}{后退; 减弱; 变坏; 跌落}
    \tword{concession}{k@n"sES@n}{让步}
    \tword{procession}{pr@"sES@n}{列队行进(noun. verb.)}
    \tword{succession}{s@k"sES@n}{继承; 继任}
}
scrutiny & "skrutni & noun. & 细阅; 详细检查; 仔细研究\crr
\linetab{
    \exx\eng Indeed, as high-school graduation rates increase, the actual 
    value of diplomas is coming under closer scrutiny.\newline
    \eng The diamond passed the scrutiny of the jewler.
}
homogenize & h@"mAdZ@""naIz & verb. & 使均匀; 使类同\crr
\linetab{
    \relative
    \tword{homolog}{"hAm@lOg}{相当或相同的事情}
    \tword{homosecxual}{""hoUm@"sekSu@l}{同性恋的}
    \tword{homogeneity}{""hAm@dZ@"nieti}{同质; 同种; 同次性}
    \tword{homogeneous}{""hoUm@"dZini@s}{均质的; 齐次的}
    \tword{assimilate}{@"sIm@""let}{吸收; 消化; 同化; 透彻理解}
}
leakage & "likIdZ & noun. & 泄露\crr
hijack & "haI"dZ\ae k & verb.\newline noun. & 劫持(交通工具)\newline 劫持; 劫机\crr
cope & koUp & verb. & 应付; 处理\crr
\linetab{
    \exx\eng I cannot cope with so much work.\newline
    \eng It's not necessarily that women don't cope as well.
}
motion & "moUSn & verb.\newline noun. & 打手势; 示意\newline 运动; 动作; 提议; 手势\crr
dedicate & "dEdI"ket & verb. & 奉献; 献身; 致力\crr
\linetab{
    \exx\eng Back on the island, he dedicated himself to politics.
}
probe & proUb & noun.\newline verb. & 探针; 探测器; 探究\newline 探究; 探查\crr
\linetab{
    \exx The policeman probe into the case of murder.
}
chop & tSAp & verb.\newline noun. & 砍; 劈\newline 砍; 剁; 排骨\crr
\linetab{
    \relative
    \tword{chopsticks}{"tSApstIks}{筷子}
}
lament & l@"mEnt & verb.\newline noun. & 悲伤; 哀悼; 痛惜; 悔恨\newline 哀歌; 挽歌; 悲痛之情\crr
\linetab{
    \exx\eng She spoke of the professional woman's lament that a woman's 
    judgement is questioned more that a man's.
}
cripple & "krIp@l & verb.\newline noun. & 瘫痪; 严重削弱\newline 瘫痪; 残疾 \crr
provided & pr@"vaIdId & conjunction. & 假如; 如果; 在...条件下\crr
\linetab{
    \exx\eng Provided that you born with superpower, what would you do for refuges?
}
interpersonal & ""Int\rse p\rse s@nl & adj. & 人与人之间的; 人际关系的\crr
\linetab{
    \relative
    \tword{interpose}{""Int\rse "poUz}{置于; 介入}
    \tword{intersect}{""Int\rse "sekt}{横断; 切断; 交叉}
    \tword{intervene}{""Int\rse "vin}{干涉; 阻碍}
    \tword{intercept}{""Int\rse "sept}{截击; 拦截(verb.) 截距(noun.)}
    \tword{interaction}{""Int\rse "\ae kS@n}{互相影响(noun.)}
    \tword{interchangeable}{""Int\rse "tSendZ@bl}{可互换的}
}
oppression & @"prES@n & noun. & 压迫; 压制; 抑制; 镇压\crr
\linetab{
    \exx\eng Where there is oppression, there is resistance.
}
cooperation & ko"Ap@"reS@n & noun. & 合作; 协作\crr
\linetab{
    \exx\eng Their cooperation helped to increase the production.
}
gasp  & g\ae sp & verb.\newline noun. & 喘气; 喘息; 倒抽气\newline 喘息; 喘气\crr
\linetab{
    \exx\eng The poor man was at his last gasp.
}
withstand & wIT"st\ae nd & verb. & 抵挡; 经受住\crr
\linetab{
    \exx\eng Cannot easily withstand repeated strain inflicated by oversize limbs.
}
supervision & "sjup\rse"vIZ@n & noun. & 监督; 管理\crr
\linetab{
    \exx\eng They will have to operate with less human supervision
    and be able to make at least a few decisions for themselves.
    \relative
    \tword{supervise}{"sup\rse vaIz}{监督; 管理; 指导}
}
enlist & In"lIst & verb. & 招募; 使入伍; 获得赞助\crr
\linetab{
    \exx\eng Enlist the support of the professionals.\par
    \eng The latest was a panel from the National Academy of Science, enlisted by the White House.
}
bang & b\ae N & noun.\newline verb. & 重击; 突然的巨响\newline 发出巨响; 砰然作响; 猛击\crr
depict & dI"pIkt & verb. & 描述; 描绘\crr
\linetab{
    \exx\eng After all, what is the one modern form of expression
    almost completely dedicated to depicting happiness?
    \relative
    \tword{describe}{dIs"kraIb}{用文学语言描述}
    \tword{portray}{pOr"tre}{通过故事, 小说等方式用文字来描述}
    \tword{depict}{dI"pIkt}{指给物体着色或是素描, 强调外表, 形象, 色彩等具体细节}
}
constituent & k@n"stItSU@nt & adj.\newline noun. & 组成的; 构成的; 立宪的\newline 成分; 要素; 选区内的选民\crr
\linetab{
    \exx\eng Public officials will hear from their constituents and act on their concerns.
}
persuade & p\rse swed & verb. & 说服; 劝说\crr
pervail & prI"vel & verb. & 获胜; 盛行; 劝服\crr
\linetab{
    \exx\eng We must, all of use, prevail upon our congressman to act.\newline
    \eng Americans have been migrating south and west in larger numbers since World War II, and the patterns still 
    pervails.
}
bribery & "braIb@ri & noun. & 受贿; 行贿\crr
\linetab{
    \exx\eng A recent study attempts tom separate them by looking at 
    bribery presecutions under FCPA.\newline
    \eng He was accused of taking bribery.
}
mutual & "mjutSu@l  & adj. & 相互的; 共同的\crr
\linetab{
    \exx\eng Mutual understading is essential to friendship.\newline
    \eng We havethe mutual interest in poetry.
    \relative
    \tword{immutable}{I"mjut@b@l}{不变的; 永恒的}
}
flee & fli & verb. & 逃跑; 逃离\crr
cognitive & "kAgn@tIv & adj. & 认知的; 认识的\crr
\linetab{
    \exx\eng Results from intuitive rather than cognitive exercises.
}
impose & Im"poUz & verb. & 强加; 征收; 施加影响; 利用; 以...欺骗\crr
\linetab{
    \exx\eng Britain imposed fines on airlines which bring in passengers without 
    proper papers.\newline
    \eng You shouldn't let them impose on your kindness.
    \relative
    \tword{depose}{dI"poUz}{废黜; 罢免; 宣誓作证}
    \texx{The emperor attempted to depose the Pope.}
    \tword{decompose}{""dik@m"poUz}{分解}
    \texx{The fertiliser releases nurtients gradually as bacteria decompose it.}
    \tword{compose}{k@m"poUz}{创作; 组成; 构成; 镇静}
    \texx{She quickly composed herself as the car started off.}
    \tword{dispose}{dI"spoUz}{处理; 放置}
    \texx{They have no way to dispose the hazardout waste they produce.}
    \tword{propose}{pr@"poUz}{建议; 求婚; 打算; 提名}
    \texx{Britain is about to propose changes to some institutions.}
    \tword{expose}{Igz"poUz}{暴露}
    \texx{For an instant her whole back was exposed.}
}
appointment & @"POIntm@nt & noun. & 任命; 约会; 职位; 职务\crr
motivate & "motIvet & verb. & 引起动机; 激发; 激励\crr
contend & k@n"tEnd & verb. & 竞争; 争斗; 声称\crr
\linetab{
    \exx\eng Soem scientists contend that there must be life on Mars.\newline
    \eng It is the palygoers, the RSC contends, who bring in much 
    of the town's revenue because they spend the night.
}
transplant & tr\ae ns"pl\ae nt & verb.\newline noun. & 移栽; 移植\newline 移植\crr
found & faUnd & verb.\newline verb. & 建立; 创建\newline 找到; 发现; 认为(find的过去式)\crr
ladder & "l\ae d\rse & noun. & 梯子; 阶梯\crr
relish & "rElIS & verb.\newline noun. & 喜欢; 享受; 从...获得乐趣\newline 享受; 乐趣; 调味品\crr
\linetab{
    \exx\eng Relish each moment in your life.
}
comprehension & ""kAmprI"henSn & noun. & 理解; 领悟\crr
fluctuate & "fl2ktSu""et & verb. & 波动; 起伏不定\crr
\linetab{
    \exx\eng In rich countries, income loss mainly results from fluctuating crude oil price.
}
cling & klIN & verb. & 紧贴; 坚守\crr
\linetab{
    \exx\eng We should cling to our priciples.
}
caress &  k@"rEs & noun.\newline verb. & 爱抚; 抚摸; 吻\crr
\linetab{
    \exx\eng "you okay?" he asks tenderly; as his thumb lightly caresses my bottom lip.
}
passerby "p\ae s\rse"baI & noun. & 行人; 过路人\crr
saucer & "sOs\rse & noun. & 茶托; 碟子\crr
scatter & "sk\ae t\rse & verb. & 分散; 散开; 散布\crr
\linetab{
    \exx\eng Small villages scatter at the foot of the mountain.\newline
    \eng Don't scatter garbage all over the place.
}
vehicle & "vI@kl & noun. & 车辆; 交通工具; 媒介物; 传达手段\crr
equip & I"kwIp & verb. & 装备; 配备\crr
impetus & "ImpIt@s & noun. & 冲力; 推动力; 刺激\crr
\linetab{
    \exx\eng Her speech gave an impetus to my ideas.\newline
    \eng The unparalleled size of its workforce had given an impetus to its economy.
}
advisory & \ae dvaIz@ri & adj. & 劝告的; 顾问的; 咨询的\newline 公告; 警告\crr
bay & be & noun. & 海湾\crr
adverse & \ae d"v\rse s & adj. & 不利的; 有害的; 相反的; 敌对的\crr
\linetab{
    \exx\eng The development was adverse to our interests.
    \relative
    \tword{converse}{k@n"v\rse s}{交谈; 谈话(verb.) 相反的; 逆的(adj.)}
    \tword{perverse}{p\rse v\rse s}{不当的; 堕落的; 刚愎的}
    \tword{obverse}{"Abv\rse s}{对立面; 对应的部分(noun.)}
    \tword{transverse}{"tr\ae nzv\rse s}{横向的(adj.) 横断面; 横轴(noun.)}
    \tword{diverse}{daI"v\rse s}{不同的; 多种多样的}
    \tword{reverse}{rI"v\rse s}{\vtop{verb.\quad 逆转; 反转; 换掉; 交换\newline \ adj.\quad 反面的; 颠倒的}}
    \tword{irreversible}{""IrIv3r"s@bl}{不可逆转的}
    \tword{averse}{@"v\rse s}{厌恶的; 反感的; 反对的}
    \tword{conversion}{"k@nv\rse Zn}{转化; 转变}
    \tword{adversary}{"\ae dv\rse seri}{对手; 敌手}
    \tword{diversity}{daI"v\rse s@ti}{差异; 多样化; 分歧}
    \texx{Few countries have as rich a diversity of habitat as South Africa.}
}
habitat & "h\ae bI""t\ae t & noun. & 场地; 栖息地; 住处\crr
claimant & "klem@nt & noun. & 要求者; 索赔人; 原告\crr
latent & "letnt & adj. & 潜在的; 潜伏的; 隐藏的\crr
\linetab[
    \exx\eng In our society there is an acceptance of violence against women 
    either explicit or latent
]
tmepo & "tempoU & noun. & 拍子; 节奏; 速度\crr
blankt & "bl\ae NkIt & noun.\newline verb. & 毛毯; 厚的覆盖物\newline 用毯子裹; 覆盖\crr
fornight & "fOrtnaIt & noun. & 两星期\crr
mount & maUnt & verb.\newline noun. & 登上; 爬上; 上升; 装上; 安放\newline 山; 峰\crr
dissipate & "dIs@pet & verb. & 驱散; 消散; 浪费; 挥霍\crr
\linetab{
    \exx\eng clouds dissipate before the wind.
    \relative
    \tword{disperse}{dIs"p\rse s}{使分散; 散开; 使消散; 色散(verb.) 分散的(adj.)}
    \texx{Polices fired shots and used teargas to disperse the demostrators.}
    \tword{teargas}{"te@rg\ae s}{催泪弹}
}
vest & vet & noun.\newline verb. & 背心; 马甲; 汗衫\newline 授予; 使穿衣\crr
\linetab{
    \exx\eng Congress is vested with the power to declare war.
}
pretext & "pri""tEks & noun. & 接口; 托词\crr
\linetab{
    \exx\eng He went away on the pretext of a headache.
}
excedingly & Ik"sidINli & adv. & 非常地; 极度地\crr
\linetab{
    \exx\eng That is an exceedingly difficult problem.
}
evaporate & I"v\ae p@""ret & verb. & 蒸发; 消失\crr
\linetab{
    \exx\eng Once they see us all together, these vicious rumors will evaporate before they began.
}
coupon & "kupAn & noun. & 优惠券; 息票; 配给券\crr
\linetab{
    \relative
    \tword{voucher}{"vaUtS\rse}{代金券; 证件; 证人}
    \tword{coup}{ku}{政变; 大事件; 机敏的棒击}
}
exile & "Ek""zaIl & noun.\newline verb. & 流放; 放逐; 流亡\crr
\linetab{
    \relative
    \tword{expel}{Ik"spEl}{驱逐; 赶走; 把...除名; 排出气体}
    \tword{banish}{"b\ae nIS}{放逐; 驱逐; 消除; 排除}
}
fountain & "faUntn & noun. & 喷泉; 源泉\crr
dread & drEd & verb.\newline noun. & 害怕; 畏惧\newline 恐惧; 畏惧\crr
\linetab{
    \exx\eng Consumers say they're not in despair because, depite the 
    dreadful headlines, their own fortunes still feel pretty good.
}
fortune & "fOrtSun & noun.\newline verb. & 运气; 时运; 财富; 命运\newline 给予财富; 偶然发生\crr
drip & drIp & verb.\newline noun. & 滴落\newline 水滴\crr
invert & In"v\rse t & verb. & 倒置; 倒转\crr
\linetab{
    \relative
    \tword{inverse}{""In"v\rse s}{倒转的; 相反的(adj.) 反面; 相反的事物(noun.)}
}
roundabout & "raUnd@""baUt & adj.\newline noun. & 绕道的; 迂回的\newline 环形交叉路口\crr
\linetab{
    \exx\eng It's painful to read these roundabout account today.
}
excavation & ""Eksk@"veS@n & noun. & 挖掘; 发掘\crr
\linetab{
    \relative
    \tword{excavate}{""Eksk@"vet}{挖掘; 开凿(verb.)}
    \tword{excavator}{""Eksk@"vet\rse}{挖掘机; 凿地机}
}
cough & kOf & noun.\newline verb. & 咳嗽\crr
dairy & "dEri & adj.\newline noun. & 牛奶的; 乳品的\newline 乳品店\crr
dome & doUm & noun. & 穹顶; 圆屋顶\crr
manufacturer & ""m\ae njU"f\ae ktS\rse \rse & noun. & 制造商\crr
\linetab{
    \relative
    \tword{manufactory}{""m\ae nj@"f\ae kt@ri}{制造厂}
    \tword{facture}{"f\ae ktS@}{制作法; 制作(noun.)}
    \texx{This paper investiaged the hydrogen effects on facture toughness%
          in the fusion area of stainless steel weld overlay.}
    \tword{factual}{"f\ae ktSul}{事实的; 真实的; 确凿的}
}
fleet & flit & noun.\newline adj.\newline verb. & 舰队; 船队; 机群\newline 快速的\newline 掠过; 疾飞\crr
exert & Ig"z\rse t & verb. & 运用 ; 施加\crr
\linetab{
    \exx\eng exert great influence on ...\newline
    \eng He likes to exert his authority.
}
regret & rI"grEt & verb.\newline noun. & 懊悔; 惋惜\newline 遗憾; 痛惜\crr
propel & pr@"pEl & verb. & 推动; 推进\crr
\linetab{
    \exx\eng It now appears that they also have an important influence
    on the geophysical processes that propel the
    plates across the globe.
    \tword{globel}{gloUb}{地球仪; 地球; 天体(noun.) 使成球状(verb.)}
}
negotiate & nIgoUSiet & verb. & 协商; 谈判; 通过; 越过\crr
\linetab{
    \exx\eng The are a natural result of brain development, a normal
    part of adolescents learning how to 
    negotiate a complex world.\newline
    \eng We'll leave you to negotiate with them.
}
extravagant & Ik"str\ae v@g@nt & adj. & 奢侈的; 过度的\crr
\linetab{
    \exx\eng satire on an extravagant lifestyle.
}
satire & "s\ae taIr & noun. & 讽刺; 讽刺文学\crr
whatsoever & ""hwAtso"Ev\rse & adv. & 无论什么; 任何\crr
\linetab{
    \exx\eng So what you need to know is that there's no evidence whatsoever to back 
    these claims.
}
groom & grum & noun.\newline verb. & 新郎; 马夫\newline 打扮; 梳理毛发; 培养\crr
\linetab{
    \exx\eng Monkeys groom each other.
}
relieve & rI"liv & verb. & 减轻; 缓解\crr
\linetab{
    \exx\eng Customers might be relieved of their disasters through lassuits.
    \relative
    \tword{relief}{rI"lif}{宽慰; 宽心; 免除; 减轻; 救援物资; 代班人}
}
proportion & pr@"pOSn & noun.\newline verb. & 比; 比率; 面积; 相称; 平衡\newline 使成比例; 使对称\crr
\linetab{
    \relative
    \tword{proportionality}{pr@""pOrS@"n\ae l@ti}{相称原则(战争, 惩罚犯罪)}
    \tword{proportional}{pr@"pOrS@nl}{成比例的; 相称的}
}
substantiate & s@b"st\ae nSiet & verb. & 证实; 实体化\crr
\linetab{
    \relative
    \tword{substance}{"s2bst\ae ns}{物质}
    \tword{substantial}{s@b"st\ae nS@l}{实质的; 内容充实的(adj.)\newline 本质; 重要材料(noun.)}
    \tword{substanitive}{"s2bst@ntIv}{真实的; 独立的; 本质的; 实质的}
    \tword{unsubstantiated}{""2ns@b"st\ae nSietId}{未经证实的; 无事实依据的}
    \exx\eng The witnes can substantiate all the testimony.
    \tword{testimony}{"testImoUni}{证词; 证据; 声明; 宣言}
}
clarify & "kl\ae r@""faI & verb. & 使清楚; 澄清; 说明; 使清醒\newline (液体)净化; 变得清楚\crr
rack & r\ae k & noun.\newline verb. & 架子; 支架; 齿条; 破坏\newline 折磨; 使痛苦; 放在架上; 累计\crr
\linetab{
    \relative
    \tphrase{to rack up points}{累计得分}
    \tphrase{to rack one's brain}{绞尽脑汁}
    \tphrase{on the rack}{焦虑万分}
}
vowel & "vaU@l & noun. & 元音; 母音\crr
choke & tSoUk & noun.\newline verb. & 窒息; 阻塞\crr
\linetab{
    \exx\eng Raise interest rates too quickly, and they risk choking 
    off America's recovery.
}
dim & dIm & adj.\newline verb. & 暗淡的; 昏暗的; 模糊的\newline 使暗淡; 使变模糊; 使减弱\crr
thorn & TOrn & noun. & 刺; 荆棘\crr
\linetab{
    \exx\eng She got her finger pricked by a thorn.
}
straw & strO & noun. & 稻草; 吸管\crr
\linetab{
    \exx\eng A drowning man will catch a t a straw.
}
indulgent & In"d2ldZ@nt & adj. & 纵容的; 宽厚的; 溺爱的\crr
\linetab{
    \relative
    \tword{indulge}{In"d2ldZ}{放纵; 迁就; 满足; 使(自己)沉溺于(verb.)}
    \tword{indulgence}{In"d2ldZ@ns}{放纵; 迁就; 溺爱; 宽容(noun.)}
    \exx\eng complete with reforms to an obviously indulgent system.\newline
    \eng We shouldn't be indulgent towards his mistakes.\newline
    \eng They are indulgent with their children.
}
mobility & moU"bIl@ti & noun. & 流动性; 灵活性; 迁移率\crr
\linetab{
    \exx\eng Recent years have witnessed a growing social mobility.
    \relative
    \tword{mobile}{"moUbIl}{活动的; 移动的(adj.) 手机; 风铃(noun.)}
    \tword{inmobile}{I"moUbl}{不动的}
    \tword{mobilize}{"moUb@laIz}{调动; 动员(verb.)}
    \tword{demobilize}{dI"moUb@laIz}{遣散(verb.)}
}
meditate & "mEdI""tet & verb. & 沉思; 冥想; 思考; 仔细计划\crr
\linetab{
    \exx\eng On the day her son began school, she meditated on the uncertainties of his future.
    \relative
    \tword{meditation}{""mEdI"teS@n}{冥想; 沉思(noun.)}
}
medium & "midi@m & noun.\newline adj. & 媒介; 方法; 居中\newline 中等的; 平均的; 半生熟的\crr
\linetab{
    \exx\eng The most powerfull mass medium was the church.
    \relative
    \tword{medial}{"midi@l}{中间的; 平均的}
    \tword{median}{"midi@n}{中央的; 中间的(adj.) 中位数; 中线(noun.)}
    \tword{mediate}{"midi""et}{调停; 调解(verb.) 居中的; 间接的(adj.)}
    \tword{mediation}{""midI"eS@n}{调解; 仲裁(noun.)}
    \tword{mediater}{"midi""et\rse}{调解人}
    \tword{immediate}{I"midIt}{即刻的; 直接的; 当前的; 直觉的}
    \tword{mediocre}{""midi"oU@r}{平庸的; 中等的}
}
absorb & \ae b"zOrb & verb. & 吸收; 吸引; 承受; 承担\crr
\linetab{
    \exx\eng The banks would be forced to absorb large losses.
}
cater & "ket\rse & verb. & 迎合; 满足需要; 供应酒菜\crr
\linetab{
    \exx\eng It is difficult to cater to everyone's wish\newline
    \eng Instead of intimate shops catering to a knowledgeable elite.
}
skeleton & "skElItn & noun.\newline adj. & 骨架; 骷髅; 纲要; 梗概\newline  骨干的; 骨骼的\crr
\linetab{
    \relative
    \tword{skull}{sk2l}{颅骨}
    \tword{sketchy}{"skEtSi}{简略的; 不完全的}
    \tword{skeletal}{"skEl@tl}{骨骼的; 像骨骼的; 骸骨的}
    \tphrase{steel skeleton}{钢骨架}
    \tphrase{skeleton structure}{骨架构造}
    \tphrase{skeleton staff}{基干人员}
}
oblige & @"blaIdZ & verb. & 迫使; 责成; 施惠; 效劳\crr
\linetab{
    \exx\eng Managers oblige their underlings to add new collaborative tools 
    such as Slack and Chatter to existing ones.
    \relative
    \tword{obligaton}{""AblI"geS@n}{责任; 义务; 契约; 恩惠}
}
obsession & @b"sES@n  & noun. & 痴迷; 困扰; 着魔; 强迫观念\crr
\linetab{
    \exx\eng In other words, if you're going to print product, make
    it for the people who are already obseessed with it.
    \relative
    \tword{obsess}{@b"sEs, Ab-}{使着迷; 迷住}
    \texx{She stopped drinking but began obsessing about her weight.}
}
temptation & tEmp"teS@n & noun. & 诱惑\crr
\linetab{
    \exx\eng He overcame a strong temptation to run away.
}
unerlie & ""2nd\rse"lai & verb. & 构成...的基础\crr
\linetab{
    \exx\eng In America a complex set of cultural signals, 
    assumptions, and conventions underiles all social interrelationships.
}
yield & yild & verb.\newline noun. & 生产; 获利; 屈服; 让步\newline 产量; 利润\crr
\linetab{
    \exx\eng Self-doubt has yield to blind pride.\newline
    \eng We shall never yield to a conqueror.
}
youth & juT & noun. & 青春; 年轻; 青年\crr
condidate & "k\ae ndIdet & noun. & 候选人; 投考者; 应试者\crr
\linetab{
    \exx\eng The company is being forced to reduce staff and 
    I'm a likely candidate for redundancy.
}
fabric & "f\ae brIk & noun. & 织物; 布料; 构造; 结构\crr
\linetab{
    \exx\eng The entire fabric of the house needs renovation.
    \relative
    \tword{fabricate}{"f\ae brI""ket}{编造; 捏造; 制造}
    \texx{We use steel to fabricate the tools}
}
gap & g\ae p & noun. & 缺口; 缝隙; 差距; 隔阂\crr
\linetab{
    \exx\eng Smaller class sizes, it is hoped, will help shrink
    the achievement gap that bedevils a school system.\newline
    \eng The gap between rich and poor.
}
bedevil & bI"dEv@l & verb. & 折磨; 困扰; 使困惑\crr
hamper & "h\ae mp\rse & verb. & 阻碍; 妨碍\crr
\linetab{
    \exx\eng More than anything, the historian say, the founders were 
    hampered by the culture of their time.
    \relative
    \tword{hammer}{"h\ae m\rse}{锤子(noun.) 捶打; 击败(verb.)}
    \tword{hinder}{"hInd\rse}{阻碍; 妨碍(verb.) 后面的(adj.)}
    \tword{handicap}{"h\ae ndI""k\ae p}{阻碍; 使不利(verb.) 缺陷; 障碍(noun.)}
}
\end{engvc}

\begin{engvc}
obsecure & @b"skjUr & adj.\newline verb. & 昏暗的; 不清楚的; 无名的\newline 使模糊; 使隐晦; 使费解\crr
\linetab{
    \exx\eng The room is too obscure for reading.
}
substitute & “s2bstItjut & noun.\newline verb. & 替代物; 代用品\newline 替代\crr
\linetab{
    \exx\eng There's no substitute for parents.\newline
    \eng Devoted concergoers who reply that recordings are no substitute
    for live performance are missing the point.
}
slave & slev & noun.\newline verb. & 奴隶； 受控制的人\newline 苦干； 辛勤地工作\crr
recruit & rI"krut & verb.\newline noun. & 征募; 招收; 招聘\newline 新兵; 新成员\crr
\linetab{
    \exx\eng That's because success depends on the ability to recruit 
    friends to help at critical times.
}
explanatory & Ik"spl\ae n@tOri & adj. & 解释的; 说明的\crr
\linetab{
    \exx\eng It is a little upsetting to read in the explanatory notes.
}
expensive & Ik"spEnsIv & adj. & 昂贵的\crr
\linetab{
    \relative
    \tword{expenditure}{Ik"spEndItS@}{开支; 消费}
    \tword{expansive}{Ik"sp\ae nsIv}{膨胀性的; 豁达的; 健谈的}
}
compulsive & k@m"p2lsIv & adj. & 强制的; 禁不住的\crr
transportation & ""tr\ae nspOr"teSn & noun. & 运输; 交通工具; 运输系统\crr
\linetab{
    \relative
    \tword{transmit}{tr\ae ns"mIt}{传播(verb.)}
    \texx{%
        \begin{engdefn}
        \item{verb}[1]to send an electronic signal, radio or television boardcast, etc
        \item{verb}[2]to pass sth from one person to another.
        \end{engdefn}
        \eng There was no danger of transmitting infection through operations.
    }
    \tword{transmission}{tr\ae nz"mIS@n}{传输(noun.)}
    \tword{transport}{"tr\ae nspOrt}{运输(verb. noun.)}
    \texx{
        \begin{engdefn}
            \item{noun}[1]a system or means of converying people or goods from place to place by means of
            a vehicle, aircarft, or ship.
            \item{noun}[2]an overwhelmingly strong emotion.
            \item{verb.}[1]take or carry from one place to another place by means of a vehicle, aircraft, or ship.
            \item{verb.}[2]overwhelm with strong emotion, especially joy.
        \end{engdefn}
    }
    \tword{transportation}{""tr\ae ns"pOrteSn}{运输; 运输系统}
    \tword{transit}{"tr\ae nzIt}{运输; 经过(verb. noun.)}
    \tword{transition}{tr\ae n"zIS@n}{转变; 过渡}
    \tword{transform}{tr\ae ns"fOrm}{转变; 改造(verb.)}
    \tword{transformation}{""tr\ae sf@"meSn}{转化; 改革}
    \tword{translate}{"tr\ae n""slet}{翻译}
    \tword{translation}{tr\ae ns"leS@n}{翻译(noun.)}
    \tword{transcend}{tr\ae n"sEnd}{超越}
    \tword{transcendence}{tr\ae n"sEnd@ns}{超越; 超凡}
}
wool & wUl & noun. & 羊毛; 毛织品\crr
\linetab{
    \relative
    \tword{woollen}{"wUl@n}{毛织的; 羊毛的}
    \tword{wood}{wUd}{木材; 木制品(noun.) 收集木材(verb.)}
    \tword{wooden}{"wUdn}{木制的}
}
glimpse & glImps & verb.\newline noun. & 瞥见\newline 一瞥\crr
\linetab{
    \exx\eng I glipse at her among the crowd.
}
gigantic & dZaI"g\ae ntIk & adj. & 巨大的; 庞大的\crr
confide & k@n"faId & verb. & 吐露; 委托; 信赖\crr
\linetab{
    \exx\eng I seldom confide in my friends.\newline
    \eng He could not confide them even to his wife, although they provide
    the unacknowledged foundation of his fiction.
}
playhourse & "plehaUs & noun. & 剧院; 儿童游戏室\crr
insurance  & In"SUr@ns & noun. & 保险\crr
confrontation & ""kAnfr@n"teSn & noun. & 对抗; 冲突\crr
\linetab{
    \relative
    \tword{confront}{k@n"fr2nt}{对抗; 冲突(verb.)}
    \exx The interaction and confrontation between shared and competing 
    beliefs about the science.
}
warrant & "wOr@nt & noun.\newline verb. & 搜查令; 逮捕状\newline 担保; 保证\crr
innovation & ""In@"veS@n & noun. & 创新; 改革\crr
\linetab{
    \exx\eng Techical innovation helps improve the qualities of products.
    \begin{engdefn}
        \item{noun} the action or process of innovating a new method, idea, or product, etc.
    \end{engdefn}
}
sensory & "sEns@ri & adj. & 感觉的; 感官的\crr
\linetab{
    \relative
    \tword{sensual}{"sEnSu@l}{肉感的; 肉欲的; 好色的}
    \tword{sensible}{"sEns@b@l}{明智的; 可察觉的}
    \tword{sentient}{"sensnt}{有知觉的; 有感觉的}
    \tword{sensitive}{"sEnsItIv}{敏感的; 易受伤的}
    \tword{sensation}{sEn"ses@n}{感觉; 感知}
    \tword{sensational}{sEn"seS@nl}{感动的; 轰动的; 骇人听闻的}
    \texx{Their sometimes sensational findings were filled with warnings about the growing competition from overseas.}
    \tword{sense}{sEns}{\vtop{感觉; 功能; 观念; 道理(noun.)\newline 感觉到; 检测到(verb.)}}
}
shelter & "SElt\rse & noun.\newline verb. & 避难所; 庇护所\newline 庇护; 遮蔽\crr
\linetab{
    \relative
    \tword{refuge}{"fEfjudZ}{\vtop{noun.\quad 避难; 避难所; 庇护者\newline verb.\quad 给予...庇护; 接纳...避难; 避难; 躲避}}
    \tword{refugee}{""rEfju"dZi}{难民}
}
possess & p@"zEs & verb. & 拥有; 占有\crr
perish & "pErIS & verb. & 死; 暴卒; 毁灭\crr
\linetab{
    \exx\eng We are genetically programmed to disintegrate and perish, even under ideal conditions.
}
swing & swIN & noun.\newline verb. & 摇摆; 秋千\newline 摇摆\crr
\linetab{
    \exx\eng Many consumers seem to have been influenced by stock-market swings.
}
permeate & "p\rse miet & verb. & 渗透; 弥漫; 贯穿\crr
\linetab{
    \exx\eng The traditional permeate through the system.
}
standstill & "st\ae nd""stIl & noun. & 停顿; 停止; 停止\crr
\linetab{
    \exx\eng As population growth in Northeast and Midwest reaches a near standstill.
}
somehow & "s2m""haU & verb. & 不知何故; 以某种方式\crr
\linetab{
    \exx\eng We must make up for the lost time somehow.
}
operative & "Ap@r@tIv & adj.\newline noun. & 起作用的; 运作的\newline 技工; 密探; 特工\crr
\linetab{
    \exx\eng His is the most skilled operative in teh factory.
}
ounce & aUns & noun. & 少量; 盎司\crr
\linetab{
    \relative
    \tphrase{not an ounce of}{一点没有}
}
due & du & adj.\newline noun.\newline adv. & 到期的; 预期的; 应得的\newline 应得物, 权利; 应缴款\newline 正向; 正对着\crr
disgust &  dIs"g2st & noun.\newline verb. & 厌恶; 反感\newline 使厌恶; 使作呕\crr
abacus & "\ae b@k@s & noun. & 算盘\crr
saddle & "s\ae dl & noun.\newline verb. & 马鞍; 鞍座\newline 装以马鞍; 使负担\crr
\linetab{
    \relative
    \tphrase{in the saddle}{在职; 掌权; 处于控制地位}
    \tphrase{out of the saddle}{落马; 下台; 免职}
    \tphrase{saddle with}{使...肩负重任}
    \tphrase{saddle up}{备马}
}
\end{engvc}

\begin{engvc}[18-9-22]
substantial & s@b"st\ae nS@l & adj. & 大量的; 实质的; 坚固的\crr
spoon & spun & noun. & 勺子; 汤匙\crr
mediority & ""midi"Akr@ti & noun. & 平庸; 平凡\crr
\linetab{
    \exx\eng The grand mediocrity of today means that natural selection has lost
    80\% of its power in upper-middle-class india.
}
petty & "pEti & adj. & 琐碎的; 微不足道的; 心胸狭隘的\crr
\linetab{
    \exx\eng He was miserable all teh time and fights would start over petty things.
}
\end{engvc}

\begin{engvc}[18-9-23]
butcher & "bUtS\rse & noun.\newline verb.\newline adj. & 屠夫; 肉贩\newline 屠宰; 杀戮\newline 更男性化; 更有男子气的\crr
\linetab{
    \relative
    \tword{butch}{bUtS}{\vtop{\ adj.\quad 男性化的; 平头的\newline noun.\quad 粗鲁的男人\newline verb.\quad 使崩溃\newline 屠杀}}
    \exx\eng Next time I will have a butcher haircut.
}
dilute & daI"lut & verb.\newline adj. & 稀释; 经稀释的\crr
\linetab{
    \exx\eng There was a clear intention to dilute black voting power.
}
stitch & stItS & noun.\newline verb. & 针脚; 缝线; 一针\newline 缝; 缝合\crr
\linetab{
    \exx\eng Though not yet loose on people, it has successfully stitched up
    the intestiones of piglets.
}
synthesis & "sInT@sIs & noun. & 综合体; 综合; 合成\crr
\linetab{
    \exx\eng His work is a synthesis of several ideas\newline
    \eng we made a synthesis of their studies.\newline
    \eng The organic synthesis
}
overwhelmingly & ""ov\rse"hwElmINli & adv. & 压倒性地; 不可抵抗地\crr
\linetab{
    \exx\eng Europe's top corporate-governace positions remain overwhelmingly male.
}
nuisance & "nusns & noun. & 讨厌的人; 讨厌的事\crr
\linetab{
    \exx\eng Don't make yourself a nuisance to others.\newline
    \eng Many of them instead become the kind of nuisance lawsuit filer that
    make the tort system a costly nightmare.
}
peak & pik & noun.\newline verb.\newline adj. & 高峰; 顶峰; 帽檐\newline 达到顶峰; 达到最高值\newline 最高的; 高峰期的\crr
\linetab{
    \begin{engdefn}
        \item{noun}The pointed top of a mountain.
        \item{verb}reach a highest point, ethier of a specified value or specified time.
        \item{adj}{greatest, maxmium}
    \end{engdefn}
}
open-access & "oUp@n"\ae ksEs & noun. & 开架阅览\crr
\end{engvc}

\begin{engvc}[18-9-25]
book & bUk & noun.\newline verb. & 书; 预定\crr
\linetab{
    \relative
    \tphrase{book fully}{全部预定}
    \tphrase{book down}{入账}
    \tphrase{book off}{登记下班}
    \tphrase{book out}{客满； 办离开(旅馆的)手续}
    \tphrase{book through}{预定直达...车票}
    \tphrase{book up}{预定; 预定座位}
    \tphrase{book for}{难免; 预定...; 盘问某人}
    \tphrase{book into}{签到; 登记}
    \tphrase{book on}{被登记备案}
    \tphrase{book oneself for}{给自己预定}
    \tphrase{book to}{托运到}
}
sprout & spraUt & verb.\newline noun. & 发芽; 长出; 迅速成长; 涌现\newline 新芽\crr
\linetab{
    \exx\eng New businesses began to sprout up across the country.
}
accountable & @"kaUnt@b@l & adj. & 负责任的; 可解释的; 可说明的\crr
\linetab{
    \relative
    \tword{account}{@"kaUnt}{解释; 导致}
    \texx{He gave a detailed account of what happend on the fateful night.}
    \tword{accountability}{@""kaUnt@"bIl@ti}{有责任; 有义务}
}
occurrence & @"k3r@ns & noun. & 发生的事; 发生\crr
\linetab{
    \exx\eng The occurrence of storms delayed our trip.
}
recipient & rI"sIpi@nt & noun.\newline adj. & 接受者; 容纳者; 容器\newline 容易接受的; 感受性强的\crr
twinkle & "twINk@l & verb.\newline noun. & 闪耀; 闪烁\newline 闪光; 瞬息\crr
\linetab{
    \exx\eng The stars twinked in the sky.
}
sponge & sp2ndZ & noun.\newline verb. & 海绵动物; 海绵块\newline 用海绵擦拭\crr
\linetab{
    \exx\eng I like to sponge my body in a bath.
}
monarch & "mAn\rse k & noun. & 君主; 帝王\crr
shepherb & "Sep\rse d & noun.\newline verb. & 牧羊人; 牧师; 指导者\newline 牧羊; 照看; 引领\crr
\linetab{
    \exx\eng Born into shepherd family, he likes modest life.\newline
    \eng Caffeine is my shepherd, I shall not doze.
}
dormitory & "dOrm@tOri & noun. & 宿舍\crr
lad & "l\ae d & noun. & 小伙子; 少年\crr
\linetab{
    \exx\eng He is a young lad with plenty of vigor.
}
kite & kaIt & noun.\newline verb. & 风筝; 空头支票\newline 使上涨; 轻快地移动; 涂改支票; 使用空头支票\crr
\linetab{
    \exx\eng The inflation will kite production costs.
}
waterproof & "wOt\rse pruf & adj. & 防水的; 不透水的\crr
\linetab{
    \relative
    \tword{dustproof}{"d2st"pruf}{防尘的}
    \tword{sunproof}{"s2n""pruf}{防嗮的}
    \tword{skidproof}{"skId""pruf}{防滑的}
    \tword{rustproof}{"r2stpruf}{防锈的}
    \tword{fireproof}{"faI\rse pruf}{防火的}
    \tword{dampproof}{"d\ae mpruf}{防潮的}
    \tword{rotproof}{"rAtpruf}{防腐的}
}
procedure & pr@"sidZ\rse & noun. & 程序; 手续; 步骤\crr
disturbance & dI"st\rse b@ns & noun. & 干扰; 障碍; 紊乱\crr
\linetab{
    \relative
    \tword{disturb}{dI"st\rse b}{打扰; 扰乱}
    \tword{tubulent}{"t\rse bj@l@nt}{动荡的; 混乱的}
    \tword{turbulence}{"t\rse bj@l@ns}{动荡; 骚乱}
    \tword{turbine}{"t3rbaIn}{涡轮}
}
silt & sIlt & noun.\newline verb. & 淤泥; 淤积\newline 使淤塞\crr
\linetab{
    \exx\eng the dam stopped the flooding but deprived the fertile silt that floods left.
}
stimulant & "stImj@l@nt & noun. & 兴奋剂; 刺激物\crr
\linetab{
    \exx\eng But beyond its widespread use as a stimulant, caffeine acturally
    has various hidden athletic benefits.
}
claw & klO & noun. & 爪; 爪形物体\newline 抓; 撕\crr
\linetab{
    \exx\eng The company has managed to claw back its share of the market.
}
affirm & @"f\rse m & verb. & 断言; 肯定; 证实\crr
\linetab{
    \exx\eng deserves praise for affirming the importance of the humanities 
    and social sciences to the prosperty and security of democracy.
}
persevere & ""p\rse s@"vI\rse & verb. & 坚持不懈; 不屈不挠\crr
\linetab{
    \exx\eng we will persevere regardless of failure.\newline
    \eng You must persevere with your english studies.
}
swamp & swAmp & noun.\newline verb. & 沼泽; 湿地\newline 淹没\crr
\linetab{
    \exx\eng Their company is in a financial swamp.
}
recede & rI"sid & verb. & 后退; 减弱; 退出\crr
\linetab{
    \exx\eng The company decided to recede from a bargain.
    \relative
    \tword{precede}{prI"sid}{领先}
    \tword{recession}{rI"sES@n}{衰退; 不景气; 后退}
    \tword{concede}{k@n"sid}{妥协; 退让(verb.)}
    \tword{concession}{k@n"sES@n}{让步; 承认; 退位}
    \tword{accede}{\ae k"sid}{继承; 加入; 同意; 任职}
    \tword{secede}{sI"sid}{退出; 脱离}
}
pave & pev & verb. & 铺路; 铺设\crr
\linetab{
    \exx\eng pave the road with stones.
}
deficit & "dEfIsIt & noun. & 不足额; 赤字; 亏损\crr
\linetab{
    \relative
    \tword{deficient}{dI"fIS@nt}{不足的; 有缺陷的; 缺乏的}
    \tword{sufficient}{"s@fIS@nt}{足够的; 充分的}
}
grocer & "groUs\rse & noun. & 食品商; 杂货商\crr
\linetab{
    \relative
    \tword{grocery}{"groUs@ri}{杂货店}
    \tword{gross}{groUs}{总的; 粗俗的; 恶劣的(adj.) 总额(noun.) 总共收入(verb.)}
}
reign & ren & verb.\newline noun. & 当政; 统治; 占主导地位\newline 君主的统治; 任期\crr
\linetab{
    \relative
    \tword{rein}{ren}{控制; 驾驭; 勒住马(verb.)}
    \tword{regime}{re"Zim}{政体; 政权}
    \texx{Born in the crisis of the old regime, many of the leaders of in dependence shared the ideals of representative government.}
    \tword{regiment}{"rEZ@m@nt}{军团; 军队(noun.) 严格管控(verb.)}
}
patriotic & ""petrI"AtIk & adj. & 爱国的\crr
\linetab{
    \exx\eng His patriotic action raised our admiration.
}
hamper & "h\ae mp\rse & verb. & 阻碍; 妨碍\crr
\linetab{
    \exx\eng Prejudice will hamper a person from doing the right thing.
}
handicap & "h\ae ndi""k\ae p & noun.\newline verb. & 障碍; 阻碍; 不利\newline 妨碍; 使不利\crr
\linetab{
    \exx\eng A history of long and effortless success can be a dreadful handicap, but, 
    if properly handled, it may become a driving force.\newline
    \eng Ignorance can handicap the progress of a city.
}
glamour & "gl\ae m\rse & noun.\newline verb. & 魅力; 魔力\newline 迷住\crr
\linetab{
    \exx\eng She likes the glamour of moonlight on the sea.\newline
    \eng  The witches glamour the man.
}
generous & "dZEn@r@s & adj. &: 慷慨的; 大方的\crr
levy & "lEvi & verb.\newline noun. & 征收; 征税; 征募\newline 征兵; 征税\crr
\linetab{
    \exx\eng The government decided to levy a tax on import cars.
}
manifest & "m\ae n@""fEst & adj.\newline verb.\newline noun. & 明显的; 显而易见的\newline 表明; 显现\newline 载货单; 旅客名单\crr
\linetab{
    \exx\eng The virus needs two weeks to manifest itself.\newline
    \eng Can you give us a copy of import manifest.
}
particle & "pArtIk@l & noun. & 粒子; 微粒; 极小量\crr
philosophy & f@"lAs@fi & noun. & 哲学\crr
\linetab{
    \relative
    \tword{philosophical}{""fIl@"sAfIkl}{哲学的; 达观的}
    \tword{philanthropy}{fI"l\ae nTr@pi}{慈善事业; 博爱}
    \tword{philharmonic}{""fIl@r"mAnIk}{\vtop{\ adj.\quad  交响乐团的; 爱好音乐的\newline 交响乐团; 爱好音乐的人}}
}
charity & "tS\ae rIti & noun. & 慈善; 慈善机关; 慈爱; 宽容\crr
\linetab{
    \relative
    \tword{charitable}{"tS\ae rIt@b@l}{慈善的; 仁慈的}
    \tword{charisma}{k@"rIzm@}{超凡魅力的}
    \tword{charismatic}{""k\ae rIz"m\ae tIk}{魅力非凡的}
}
corridor & "kOrId\rse & noun. & 走廊\crr
\linetab{
    \relative
    \tword{porch}{pOrtS}{走廊}
    \tword{gallery}{"g\ae l@ri}{画廊}
    \tword{lobby}{"lAbi}{走廊; 门庭}
    \tword{passage}{"p\ae sIdZ}{道路; 文章}
}
embed & Im"bEd & verb. & 插入; 嵌入\crr
\linetab{
    \relative
    \tword{embrace}{Em"bres}{拥抱(verb. noun.) 接受(verb.)}
    \tword{empathy}{"Emp@Ti}{同感; 共鸣(noun.)}
    \tword{embarrass}{Em"b\ae r@s}{使难堪; 使窘迫}
    \tword{embarrassment}{Em"b\ae r@sm@nt}{难堪; 窘迫(noun.)}
}
embryo & "EmbrioU & noun. & 胚胎\crr
\linetab{
    \exx\eng Knowingly endanger an embryoj's life.
    \relative
    \tword{bud}{b2d}{萌芽(noun.) 发芽(verb.)}
    \tword{larva}{"lArv@}{幼虫}
    \tword{fetus}{"fit@s}{胎儿}
}
uphold & 2p"hoUld & verb. & 拥护; 支持; 维护\crr
\linetab{
    \exx\eng Would the nominee vote to uphold Roe v. Wade, 
    the controversial decision recognizing the right to choose, or overturn it?
}
lenient & "lini@nt & adj. & 宽厚的; 仁慈的; 不严格的\crr
\linetab{
    \exx\eng The study found that, among prosecuted firms, those with the most
    comprehensive CSR programs, tended to get more lenient penalties.
}
inaugurate & I"nOg@ret & verb. & 开创; 为...举行就职(落成; 开幕)典礼\crr
\linetab{
    \exx\eng The new president will be inaugurated on January 20th.
    \relative
    \tword{augur}{"Og\rse}{预言(verb.) 占卜师(noun.)}
    \tword{inaugural}{In"Ogj@r@l}{就职的(adj.) 就职典礼(noun.)}
    \tword{inauguration}{In""Ogj@"reS@n}{就职仪式}
    \tphrase{inaugural address}{就职演说}
}
incentive & In"sEntIv & noun. & 刺激; 诱因; 动机\crr
\linetab{
    \exx\eng The bonus is an incentive for me to work hard.
    \relative
    \tword{incent}{In"sent}{激励}
    \tword{stimulate}{"stImj@""let}{刺激}
    \tword{irritate}{"IrI""tet}{激怒; 使兴奋; 引起愤怒}
    \tword{motivate}{"moUtIvet}{刺激; 使有动机; 促动; 激发}
    \tword{irrigate}{"IrI""get}{灌溉; 清洗; 使清新(verb.)}
}
lavatory & "l\ae v@tOri & 厕所\crr
cyberspace & "saIb\rse spes & noun. & 网络空间\crr
\linetab{
    \exx\eng In this cyberspace, I hope I can find a listener.
}
thrift & TrIft & noun.\newline adj. & 节俭; 节约\crr
\linetab{
    \exx\eng While in America the trend started as a reaction to the 
    economic decline and is still linked to the politics of thrift.
}
worship & "w\rse Sip & noun.\newline verb. & 崇拜; 崇敬; 礼拜\newline 崇拜; 崇敬; 做礼拜\crr
periodical & ""pIri"AdIkl & adj.\newline noun. & 周期的; 定期的\crr
\linetab{
    \exx\eng The worker has a periodical check on the machine.
}
perplex & p@"plEks & verb. & 是困惑; 使复杂化; 使混乱\crr
\linetab{
    \exx\eng Hearing allegations of cruelty to animals in research 
    settings, many are perplexed that anyone would deliberately harm an
    animal.
}
interactivity & ""Int@r\ae"ktIv@ti & noun. & 交互性; 互动性\crr
\linetab{
    \exx\eng A site selling the right kind of products with the right mix
    of interactivity, hopitality, and security will attact customers.
}
discourse & "dIskOrs & noun.\newline verb. & 演说; 论述; 交谈; 论文\newline 谈论; 交谈\crr
\linetab{
    \relative
    \tword{dissert}{di"s@t}{论述; 讨论; 写论文; 作学术演讲}
    \exx\eng We'll discourse on the subject tonight.
}
determinism & dI"t\rse mInIz@m & noun. & 宿命论; 决定论\crr
\linetab{
    \exx\eng If you believe in determinism, you have to believe it all the way.
}
ponder & "pAnd\rse & verb. & 深思; 仔细考虑\crr
\linetab{
    \exx\eng intelligence seeks to grasp, manipulate, reorder, and adjust, while intellect
    examines, ponders, wonders, therizes, criticizes and imagines.
}
mission & "mIS@n & noun. & 使命; 任务; 使团\crr
\linetab{
    \exx\eng His mission is to help poor people.
}
trail & tr2l & verb.\newline noun. & 跟踪; 尾随; 托; 落后于\newline 小径; 路径; 踪迹\crr
\linetab{
    \relative
    \tword{trial}{traIl}{实验; 审判; 磨难(noun.) 实验的(adj.)}
    \exx\eng Their long skirts trail along in the mud.
}
recognition & ""rEk@g"nIS@n & noun. & 认识; 识别; 承认; 认可; 褒奖; 酬劳\crr
\linetab{
    \exx\eng Please accept this cheque in recognition of all your help.
    \relative
    \tword{recognize}{"rEk@g""naIz}{认出; 承认}
    \tword{cognition}{kAg"nISn}{认识; 认知}
    \tword{cognitive}{"kAgnItIv}{认知的; 认识的}
}
slavery & "slev@ri & noun. & 奴隶制; 奴隶身份\crr
\linetab{
    \relative
    \tword{slave}{slev}{奴隶(noun.) 奴隶般工作(verb.)}
    \tword{slavish}{"slevIS}{奴性的; 盲从的; 奴隶的}
    \tword{slaveholding}{"slev""hoUldIN}{蓄奴的; 拥有奴隶的}
    \tword{slaveholder}{"slev""hoUld\rse}{奴隶拥有者}
    \tphrase{abolish slavery}{废除奴隶制}
    \tphrase{slavery society}{奴隶社会}
    \tphrase{slavery bond}{奴隶契约}
}
compromise & "kAmpr@maIz & noun.\newline verb. & 妥协; 和解\newline 妥协; 和解; 损害; 危及\crr
\linetab{
    \exx\eng The independence of standard setters, essential to the proper 
    functioning of capital markets, is being compromised.
}
devastate & "dEv@""stet & verb. & 毁灭; 摧毁; 变成废墟\crr
\linetab{
    \exx\eng Diseases such as HIV/AIDS not only exacerable malnutrition but can 
    devastate labour, farm productivity and livelihoods.
}
slip & slIp & verb.\newline noun. & 滑倒; 溜走; 疏忽\crr
\linetab{
    \exx\eng That wasn't really a mistake. It was only a slip.\newline
    \eng The office slipped up and the letter was never sent.
}
concert & "kAns\rse t & noun.\newline verb. & 音乐会; 演奏会; 一致; 和谐\newline 协调一致行动\crr
\linetab{
    \exx\eng They did not act in concert with one another.
}
confine & k@n"faIn & verb. & 限制; 禁闭\crr
\linetab{
    \exx\eng If its message were confined merely to information.
}
twist & twIst & verb.\newline noun. & 搓; 拧; 扭转; 曲折\crr
\linetab{
    \exx\eng A twist on a familiar quote "If at first you don't succeed, 
    give up" or a play on words or on a situation.
}
alleviate & @"livIet & verb. & 减轻; 缓解; 缓和\crr
\linetab{
    \exx\eng This medicine will alleviate your sore throat.\newline
    \eng A cold compress can alleviate your pain.
}
adopt & @"dApt & verb. & 收养; 采用; 采纳; 正式通过\crr
\linetab{
    \exx\eng Many childless couples adopt children.\newline
    \eng Scientists could "adopt" middle school classes and present their own research.
    \relative
    \tword{adapt}{@"d\ae pt}{适应; 改编}
    \tword{adept}{@"dEpt}{精通于; 擅长于(verb.) 专家; 能手(noun.)}
}
soak & soUk & verb. & 使浸透; 吸入\newline 浸泡\crr
commend & k@"mEnd & verb. & 推荐; 表扬; 举荐\crr
\linetab{
    \exx\eng Teh critics commend the new film.
}
steer & stI\rse & verb. & 驾驶; 引导\crr
\linetab{
    \exx\eng It also left wisdom, in both its triumphs and
    disasters, to help us steer through similar storms.\newline
    \eng Far less certain, however, is how successful experts and can select our peer
    groups and steer their activities in rightdirections.
}
prescription & prI"skrIpS@n & noun. & 处方; 药方\crr
moderate & "mAd@rIt & adj.\newline verb. & 中等的; 适度的; 温和的; 稳健的\newline 使缓和; 节制; 主持\crr
\linetab{
    \exx\eng Moderate exercise will be of benefit to you.
}
poverty & "pAv\rse ti & noun. & 贫困; 短缺\crr
\linetab{
    \exx\eng The poverty of imagination\newline 
    \eng Poverty is one of the causes of deaths.
}
trivial & "trIvi@l  & adj. & 不重要的; 琐碎的; 微不足道的\crr
\linetab{
    \exx\eng Don't waste your time on these trivial things.\newline
    \eng It's a trivial matter and not worth fighting about.
}
culprit & "k2lprIt & noun. & 罪犯; 犯错的人\crr
\linetab{
    \exx\eng Despite the contribution of English language to globalizaiton,
    it's considered the main culprit of loss of language diversity.
}
council & "kaUns@l & noun. & 理事会; 委员会; 议会\crr
counsel & "kaUns@l & noun.\newline verb. & 律师; 劝告\newline 劝告; 建议\crr
\linetab{
    \exx\eng Good counsel never comes to late.
}
snobbish & "snAbIS & adj. & 势力的; 媚上欺下的\crr
cohesive & koU"hisIv & adj. & 粘性的; 有粘聚性的; 统一的\crr
\linetab{
    \exx\eng They see themselves as a cohesive group.
}
renovate & "rEn@vet & verb. & 整修; 翻新\crr
commonplace & "kAm@nples & adj.\newline noun. & 普通的; 平庸的\newline 平凡的事\crr
\linetab{
    \exx\eng The challenge now is not in protecting what is innovative
    about people, but what is commonplace.
}
\end{engvc}

\begin{engvc}[18-9-26]
hypocrite & "hIp@""krIt & noun. & 伪君子； 伪善者\crr
hypocrisy & hI"pAkr@si & noun. & 伪善\crr
deem & dim & verb. & 认为; 判断; 以为\crr
\linetab{
    \exx\eng There is an overlap of only 50\% between the top collaborative contributors and those
    individuals deemed to the top performers.
}
perish & "pErIS & verb. & 死; 毁灭\crr
\linetab{
    \exx\eng Civilizations do eventually perish.
}
ideology & ""aIdI"Al@dZi & noun. & 意识形态; 思想体系\crr
\linetab{
    \exx\eng A man's ideology is reflected in his behavior.
}
renown & rI"naUn & noun. & 名声; 声誉\crr
\linetab{
    \exx\eng She used to be a singer of some renown.
}
likelihood & "laIkli""hUd & noun. & 可能性\crr
\linetab{
    \exx\eng There is no likelihood of his success.\newline
    \eng Basic economic suggests the greater the potential consumers, 
    the higher the likelihood of a better price.
}
drawback & "drO""b\ae k & noun. & 缺点; 不利条件\crr
expectation & ""EkspEk"teS@n & noun. & 期待; 预料\crr
\linetab{
    \tword{inspect}{In"spEkt}{检查; 视察}
    \tword{prospect}{"prAspekt}{前景; 期望; 景象(noun.) 勘探; 勘察(verb.)}
    \tword{suspect}{s@"spekt}{怀疑(adj. noun. adj.)}
    \tword{respect}{rI"spekt}{尊重; 尊敬; 遵守(verb.) 尊重; 某方面(noun.)}
    \tword{introspect}{""Intr@"spekt}{反省}
    \tword{aspect}{"\ae spekt}{方面; 方位; 面貌; 形式}
    \tword{retrospect}{"rEtr@""spekt}{回顾(verb. noun.)}
}
\end{engvc}

\begin{engvc}[18-9-27]
constrict & k@n"strIkt & verb. & 使紧缩; 压紧\crr
\linetab{
    \exx\eng She objects to the tests the Government's advisers have devised because
    they constrict her teaching style.
}
bureaucrat & "bjU@kr\ae t & noun. & 官僚; 官僚主义者\crr
\linetab{
    \exx\eng He is a conservative bureaucrat.
    \relative
    \tword{bureaucracy}{bjU"rAkr@si}{官僚主义}
    \tword{bureau}{"bjUroU}{机关单位}
}
presuppose & ""pris@"poUz & verb. & 预先假定; 预料; 以...为先决条件\crr
\linetab{
    \exx\eng I presuppose that you have done your work.
    \relative
    \tword{prerequisite}{pri"rEkwIzIt}{前提}
    \tword{requisite}{"rEkwIzIt}{必需的; 必不可少的(adj.) 必需品(noun.)}
    \tword{prefigure}{""pri"fIgj@r}{预示(verb.)}
}
\end{engvc}

\begin{engvc}[18-9-28]
allowance & @"laU@ns & noun. & 零钱; 津贴\crr
\linetab{
    \exx\eng There will now be a seven-day wait for the jobseeker's allowance.
}
confront & k@n"fr2nt & verb. & 面对; 遭遇; 对抗\crr
\linetab{
    \exx\eng But not even a great health-care system can cure death - and 
    our failure to confront that reality now theatens this greatness of.
}
siren & "saIr@n & noun. & 警报器; 汽笛; 海上女妖; 危险美丽的女人\crr
\linetab{
    \exx\eng Who can resist your temptation like a siren.
}
blush & bl2S & verb.\newline noun. & 脸红; 羞愧\crr
\linetab{
    \exx\eng His words raised a blush on her cheeks.
}
spiral & "spaIr@l & verb.\newline noun.\newline adj. & 螺旋式上升(下降)\newline 螺旋形; 陡升或骤降\newline 螺旋形的\crr
\linetab{
    \exx\eng Prices are spiraling out of control.\newline
    \eng A spring is a spiral.
}
expire & Ik"spI\rse & verb. & 停止; 期满; 失效; 断气\crr
\linetab{
    \exx\eng My visa is going to expire this week.
}
wink & wINk & verb.\newline noun. & 眨眼; 使眼色; 闪烁\newline 眨眼; 眼色; 瞬间\crr
\linetab{
    \exx\eng Wink the headlights on and off.
}
erupt & I"r2pt & verb. & 爆发; 喷发\crr
\linetab{
    \exx\eng Controversies have erupted when the tactics have been 
    used to sell questionable beauty creams or unhealthy foods.
    \relative
    \tword{rupture}{"r2ptS\rse}{破裂}
    \tword{abrupt}{@"br2pt}{突破的; 唐突的; 陡峭的; 不流利的}
}
miracle & "mIr@k@l & noun. & 奇迹; 奇事\crr
\linetab{
    \exx\eng It is a miracle that he escaped death.
}
preclude & prI"klud & verb. & 阻止; 排除\crr
\linetab{
    \exx\eng We try to preclude any possibility of misunderstanding.\newline
    \eng A piror engagement will preclude me from coming.
}
empirical & Em"pIrIk@l & adj. & 经验主义的; 以经验为根据的\crr
\linetab{
    \exx\eng Many empirical results supported the hypothesis.
}
vocation & vo"keSn & noun. & 职业; 行业; 使命\crr
\linetab{
    \exx\eng He was equipped with knowledge for the vocation.
}
herald & "hEr@ld & noun.\newline verb. & 使者; 传令官; 预示者\newline 预报; 标志\crr
\linetab{
    \exx\eng This is something to celebrate -- it heralds a time when 
    human beings are more respectful of one another.
}
thigh & Tai & noun. & 大腿; 屁股\crr
fever & "fiv\rse & noun.\newline verb. & 发热; 发烧\newline 使发烧; 使兴奋\crr
chancellor & "tS\ae ns@l\rse & noun. & 大臣; 总理\crr
namely & "nemli & adv. & 即; 也就是\crr
keen & kin & adj. & 热心的; 敏锐的; 渴望的\crr
pathetic & p@"TEtIk & adj. & 可怜的; 悲哀的; 差劲的; 令人讨厌的\crr
\linetab{
    \exx\eng pathetic men are always annoying to some extent.\newline
    \eng Human beings are weak, pathetic, feebleminded.
}
veto & "vitoU & noun.\newline verb. & 否决; 否决权\newline 否决\crr
\linetab{
    \exx\eng The president has the power to veto legistation.
}
ashore & @"SOr & adv. & 在岸上; 到岸上\crr
\linetab{
    \exx\eng During the breeding season the birds come ashore.
}
hostage & "hAstIdZ & noun. & 人质\crr
\linetab{
    \exx\eng An asset or compaign become hostage to consumers
    or other stakeholders who make negative allegations about 
    a brand or product.
}
allegation & ""\ae lI"geS@n & noun. & 主张; 宣称; 指控; 陈述\crr
narration & n\ae"reS@n & noun. & 叙述; 故事\crr
monument & "mAnjum@nt & noun. & 纪念碑; 历史遗迹; 不朽作品\crr
\linetab{
    \exx\eng The monument is in honor of a scientist.
}
commemorate & k@"mEm@ret & verb. & 纪念\crr
discrepancy & dI"skrEp@nsi & noun. & 差异; 矛盾\crr
\linetab{
    \exx\eng There is a discrepancy in the two reports of the accident.\newline
    \eng Many of the discrepancies between that the public sees as 
    healthy and how experts define it can be attributed to marketing.
}
mistress & "mIstrIs & noun. & 女主人; 情妇; 女英语老师\crr
\linetab{
    \exx\eng He has a wife and a mistress.
}
brim & brIm & noun.\newline verb. & 边; 边缘; 帽边\newline 满; 溢出\crr
\linetab{
    \exx\eng Classes are packed to the brim.
}
drastic & "dr\ae stIk & adj. & 激烈的; 剧烈的; 猛烈的\crr
\linetab{
    \exx\eng In such a situation, drastic measures are needed.
    \relative
    \tword{dramatic}{dr@"m\ae tIk}{戏剧的}
}
exhibiiton & ""Eks@"bIS@n & noun. & 展览; 展出\crr
\linetab{
    \relative
    \tword{exhibit}{Ig"zIbIt}{展览; 展出; 证明(verb. noun.)}
}
autonomy & O"tAn@mi & noun. & 自治; 自主权; 自治权\crr
\linetab{
    \exx\eng There are minority autonomy areas in China.
}
mug & m2g & noun.\newline verb. & (有柄的)大杯\newline 对...行凶抢劫\crr
\linetab{
    \exx\eng Many people won't go out alone at night because they're afraid of being 
    mugged.
}
accustome & @"k2st@m & verb. & 使习惯\crr
\linetab{
    \exx\eng I have accustomed myself to working for long hours.
}
crane & kren & noun.\newline verb. & 起重机; 鹤\newline 探头; 迟疑\crr
\linetab{
    \exx\eng She craned her neck to get better view.
}
hydrogen & "haIdr@dZEn & noun. & 氢\crr
\linetab{
    \relative
    \tword{oxygen}{"AksIdZ@n}{氧}
    \tword{nitrogen}{"naItr@dZ@n}{氮}
    \tword{silicon}{"sIlIk@n}{硅}
    \tword{carbon}{"kArb@n}{碳}
}
mushroom & "m2S"rum & noun.\newline verb. & 蘑菇; 快速成长的事物\newline 迅速成长; 迅速增加\crr
\linetab{
    \exx\eng New stadiums and gyms mushroomed all over the area.
}
vitamin & "vaIt@mIn & noun. & 维生素; 维他命\crr
proceed & proU"sid & verb. & 进行; 继续; 继续进行\crr
\linetab{
    \exx\eng Subscribers can customize the information they want to 
    receive and proceed directly to a company's Web site.
}
tray & tre & noun. & 托盘; 浅盘\crr
\linetab{
    \exx\eng He put the toast on the tray.
}
museum & mju"zi@m & noun. & 博物馆\crr
spotlight & "spAtlaIt & noun.\newline verb. & 聚光灯; 公众注意的中心\newline 聚光灯照明; 使突出醒目\crr
\linetab{
    \exx\eng Alber's case has returned to the spotlight in the past
    month because he is no longer a convicted man.
}
federal & "fEd@r@l & adj. & 联邦的; 联邦制的\crr
\linetab{
    \exx\eng A few premiers are suspicious of any federal-provincial deal-making.
}
affection & @"fEks@n & noun. & 钟爱; 情感\crr
\linetab{
    \exx\eng Every mother has affection for her children.
}
brittle & "brItl & adj. & 硬但易碎的; 脆弱的; 尖利的\crr
\linetab{
    \exx\eng The orchestra was brittle in tone.
    \relative
    \tword{baffle}{"b\ae f@l}{使受挫折; 使困惑; 使迷惑(verb. 隔板; 挡板; 迷惑(noun.))}
    \tword{crispy}{"krIspi}{脆的; 干冷的; 易碎的; 新鲜的; 精神爽快的}
    \tword{crust}{kr2st}{面包皮; 外壳; 硬外皮; 地壳(verb. noun.)}
}
anguish & "\ae NgwIS & noun. & 苦闷; 痛苦\crr
\linetab{
    \exx\eng Physical disability causes mental anguish.\newline
    \eng Her mental anguish was beyond words.
}
pour & pOr & verb. & 倒; 倾倒; 蜂拥而来\crr
\linetab{
    \exx\eng we must pour out a large stream of essential
    words, unhampered by stops, or quilifying adjectives, or finite 
    verb.
    \relative
    \tphrase{pour out}{倒下}
    \tphrase{pour away}{倒掉}
    \tphrase{pour into}{倒进}
}
ingredient & In"gridi@nt & noun. & 成分; 配料; 要素; 因素\crr
\linetab{
    \exx\eng The essential ingredient for success.
}
dissolve & dI"zAlv & verb. & 溶解; 解散; 散去; 失控\crr
\linetab{
    \exx\eng Smile can dissolve apathy and pass warmth.
    \relative
    \tword{absolve}{@b"zAlv}{赦免; 无罪; 开脱}
}
inflict & In"flIkt & verb. & 惩罚; 把...强加给\crr
\linetab{
    \exx\eng Don't inflict damage on any person.
}
extinguish & Ik"stINgwIS & verb. & 熄灭; 扑灭\crr
\linetab{
    \exx\eng Please extinguish your cigarettes.\newline
    \eng An uninformed citizenry will extinguish the precious embers of 
    medical progress.
}
fiscal & "fIsk@l & adj. & 财政的; 国库的\crr
\linetab{
    \exx\eng Some local governments exploit loopholes and exempt 
    enterprises which are otherwise big contributors to fiscal revenue.
}
linen & "lIn@n & noun.\newline adj. & 亚麻布; 亚麻织品\newline 亚麻布制的; 亚麻色的\crr
chronic & "krAnIk & adj. & 长期的; 慢性的\crr
\linetab{
    \exx\eng Women are exposed to tend to be in more of a chronic or repeated
    nature.
}
empire & "Em"paI\rse & noun. & 帝国\crr
violet & "vaI@l@t & noun.\newline adj. & 紫罗兰\newline 紫罗兰色的\crr
pistol & "pIst@l & noun. & 手枪\crr
\linetab{
    \exx\eng The signal pistol went off with a bang.
}
shrewd & Srud & adj. & 精明的; 敏锐的; 机灵的\crr
\linetab{
    \exx\eng because of shrewd advertising and public health compaigns.
}
persecute & "p\textrhookrevepsilon sIkjut & verb. & 迫害; 烦扰\crr
\linetab{
    \exx\eng They persecute me with all kinds of questions.
}
dissipate & "dIs@pet & verb. & 驱散; 消散; 浪费; 挥霍\crr
\linetab{
    \exx\eng Don't dissipate your efforts.
}
disperse & dIs"p\textrhookrevepsilon s & verb. & 散开; 驱逐; 散播\crr
sarcastic & sAr"k\ae stIk & adj. & 讽刺的; 嘲讽的; 挖苦的\crr
\linetab{
    \relative
    \tword{sarcasm}{"sArk\ae s@m}{讽刺; 挖苦}
    \tword{satirize}{""s\ae t@"raIz}{讽刺; 挖苦(verb.)}
    \tword{satire}{"s\ae taI@r}{讽刺; 讽刺文学; 讽刺作品}
    \tword{ironic}{aI"rAnIk}{讽刺的}
}
ascend &  @"sEnd & verb. & 上升; 升高; 登高\crr
\linetab{
    \exx\eng The rocket ascended into the sky until it disappeared.
}
ascertain & \ae s\rse"ten & verb. & 查明; 弄清; 确定\crr
\linetab{
    \exx\eng We must ascertain the murderer of the case.
}
stuff & st2f & noun.\newline verb. & 东西; 原料\newline 塞; 填充\crr
\linetab{
    \exx\eng Don't stuff the sack too full.
}
\end{engvc}

\begin{engvc}[18-9-29]
underlie & "2nd\rse"laI & verb. & 构成...的基础(或起因)\crr
\linetab{
    \exx\eng The most important forces behind the massive M\&A wave are the 
    same that underlie the globalization process.
}
depict & dI"pIkt & verb. & 描述; 描绘\crr
\linetab{
    \exx\eng After all, what is the one modern form of expression almost
    completely dedicated to depicting happiness?
}
tropic & "trApIk & noun.\newline adj. & 回归线; 热带\newline 热带的\crr
\linetab{
    \exx\eng tropic rainforest climate.
}
cord & kOrd & noun. & 细绳; 绳索\crr
\linetab{
    \exx\eng I wear a safety cord at all times.
}
cotton & "kAtn & noun. & 棉; 棉花; 棉布\crr
neck & nEk & noun. & 脖子\crr
\linetab{
\index{rtzc@{人体组成}|hyperpage}
    \twocol{
        \tword{head}{hEd}{头部}
        \tword{throat}{TroUt}{喉咙}
        \tword{chest}{tSEst}{胸口}
        \tword{nipple}{"nIp@l}{乳头}
        \tword{navel}{"nev@l}{肚脐}
        \tword{pit}{pIt}{胸口}
        \tword{abdomen}{"\ae bd@m@n}{腹部}
        \tword{thigh}{TaI}{大腿}
        \tword{back}{b\ae k}{背}
        \tword{waist}{west}{腰}
        \tword{shoulder}{"SoUld\rse}{肩膀}
        \tword{skull}{sk2l}{颅骨; 头盖骨}
    }{
        \tword{hip}{hIp}{臀部}
        \tword{buttock}{"b2t@k}{屁股}
        \tword{collarbone}{"kAl@rboUn}{锁骨}
        \tword{rib}{rIb}{肋骨}
        \tword{backbone}{"b\ae kboUn}{脊柱}
        \tphrase{private parts}{阴部}
        \tphrase{armpit hair}{腋毛}
        \tphrase{shoulder joint}{肩关节}
        \tphrase{shoulder blade}{肩胛骨}
        \tphrase{breastbone}{胸骨}
        \tphrase{elbow joint}{肘关节}
    }
}
nod & nAd & verb.\newline noun. & 点头; 打盹\newline 点头\crr
\linetab{
    \exx\eng As boards scrutinize succession plans in response to 
    shareholders pressure, executives who don't get the nod also may with to.
}
pant & p\ae nt & noun.\newline verb. & 裤子; 短裤\newline 喘息\crr
rifle & "raIf@l & noun.\newline verb. & 步枪; 来福枪\newline 快速搜寻\crr
\linetab{
    \exx\eng The killer did rifle his wallet and steal \$200.
}
demoralization & dI""mOr@laI"zeSn & noun. & 道德败坏; 士气消沉\crr
\linetab{
    \exx\eng The professor criticized the demoralization of the public in his book.
}
uncharted & ""2n"tSArtId & adj. & 无人涉足的; 未知的\crr
\linetab{
    \exx\eng Surely, we are in uncharted territory, right?
}
luggage & "l2gIdZ & noun. & 行李\crr
tall & tOl & adj. & 高的\crr
improbable & Im"prAb@bl & adj. & 不大可能的\crr
\linetab{
    \exx\eng Once you've ruled out the impossible, whatever remains, however improbable, must be true.
}
chassis & "S\ae si & noun. & 底盘; 起落架\crr
calibration & ""k\ae l@"breS@n & noun. & 校准; 标准化; 刻度; 标度\crr
bound & baUnd & noun.\newline adj.\newline verb. & 跳跃; 界限; 限制\newline 必定的; 受约束的\newline 有义务的\newline 跳; 跃; 限制\crr
\linetab{
    \exx\eng Part of the proboem is that justice are not bound by an ethics code.
}
daunt & dOnt & verb. & 使气馁; 使胆怯; 吓到\crr
\linetab{
    \exx\eng She was a brave woman but she felt daunted by teh task ahead.
}
descendant & dI"sEnd@nt & noun. & 后裔; 子孙; 后代\crr
\linetab{
    \exx\eng But however amazed our descendants may be at how far 
    from Utopia we were, they will look just like us.
}
cue & kju & verb.\newline noun. & 给提示\newline 提示; 信号; 暗号\crr
\linetab{
    \exx\eng That was the cue of outbreak of war.
}
breed & brid & verb.\newline noun. & 繁殖; 孕育; 引起\newline 品种; 血统\crr
\linetab{
    \exx\eng Downshifting has, ironically, even breed a new area of 
    what might be termed anti-consumerism.
}
browse & braUse & noun.\newline verb. & 浏览; 吃草\newline 浏览; 随意观看; 吃草\crr
prudent & "prudnt & adj. & 谨慎的; 慎重的; 精明的\crr
\linetab{
    \exx\eng With the risks obvious and growing, a prudent people 
    would take out an insurance policy now.
}
sneak & snik & verb.\newline adj.\newline noun. & 溜; 偷偷地做\newline 突然的; 出其不意的\newline 鬼鬼祟祟地人; 偷偷摸摸\crr
\linetab{
    \exx\eng I sneak a look at his book.\newline 
    \eng undercover investigators were able to sneak 
    weapons both fake and real past airport security nearly every time 
    they tried.
}
sober & "soUb\rse & adj.\newline verb. & 清醒地; 持重地\newline 使清醒; 使变得持重\crr
\linetab{
    \exx\eng A sober sided classical music critic.
}
blast & bl\ae st & verb.\newline noun. & 爆破\newline 冲击破; 巨响\crr
\linetab{
    \exx\eng He gave a blast on his trumpet.
}
threshold & "TreShoUld & noun. & 门槛; 门口; 起始点\crr
\linetab{
    \exx\eng They treaty will be the threshold of lasting peace.
}
marine & m@"rin & adj.\newline noun. & 海的; 与海有关地\newline 水兵; 舰队; 海运业\crr
smog & smAg & noun. & 烟雾\crr
\linetab{
    \exx\eng There is often smog in the big cities.
}
inertia & I"n\rse S@ & noun. & 惯性; 惰性\crr
\linetab{
    \exx\eng inertia carried the plane onto the ground.
    \relative
    \tword{inert}{I"n\rse t}{不活泼的; 迟钝的; 懒惰的}
}
maiden & "medn & noun.\newline adj. & 少女; 处女; 未婚女子\newline 初次的\crr
\linetab{
    \exx\eng The prince fell in love with a fair young maiden.
}
zeal & zil & noun. & 热情; 热忱\crr
\linetab{
    \exx\eng What motivated him was his zeal for "fundamental fairness".
}
scramble & "sk\ae mb@l & noun.\newline verb. & 攀登; 爬; 争夺; 混乱\newline 攀登; 爬; 混杂; 争抢\crr
\linetab{
    \exx\eng They scramble for the best seats.
}
glacier & "gleS@r & noun. & 冰川; 冰河\crr
\linetab{
    \exx\eng The gorge was formed by a glacier.
}
stereotype & "stEri@""taIp & noun. & 固定模式; 刻板印象\crr
evacuate & I"v\ae kju""et & verb. & 撤离; 疏散; 撤出\crr
\linetab{
    \exx\eng All people would evacuate the area.
}
freight & fret & noun.\newline verb. & 货运; 货物; 运费\newline  运送\crr
\linetab{
    \exx\eng We freight goods to all parts of teh USA.
}
curtain & "k\textrhookrevepsilon tn & noun. & 帷幕; 窗帘\crr
circulation & ""s\rse kj@"leSn & noun. & 循环; 流通; 发行量\crr
\linetab{
    \exx\eng In general circulation dailies.
}
malpractice & m\ae l"pr\ae ktIs & noun. & 玩忽职守; 治疗失当; 营私舞弊\crr
\end{engvc}